### 2020-11-08 examples/task1/Paper/conference_101719.tex
Uploaded examples and data for task 1

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{float}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Sensors Lab Conference}

\author{\IEEEauthorblockN{1\textsuperscript{st} Gabriele Paris}
\IEEEauthorblockA{\textit{Physic department} \\
\textit{Universiteit Antwerpen}\\
Antwerp, Belgium \\
gabriele.paris@student.uantwerpen.be}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
To write
\end{abstract}

\begin{IEEEkeywords}
6TiSCH, Contiki-NG, Energest, Zolertia
\end{IEEEkeywords}

\section{Introduction}
To write

\section{Analysing the 6TiSCH energy consumption}
\label{section:task1}
In the first analysis, we compared the energy consumption during a certain time period of the entire 6TiSCH stack to when only enabling the TSCH MAC layer (without link-layer security) after network convergence.\\
For both analyses, we report on the consumption of the root and the leaf node separately.\\
Following we remark differences in energy consumption between the root and the leaf node.

\subsection{Only TSCH MAC layer}
The basic setup for the following analysis is a root (coordinator) node that sends packets to a leaf node at a rate of 1 packet of 4 bytes per second.\\
Note that the root node has no event routine related to data reception. In the same way, the leaf node has no code which permits data transmission.\\
Both nodes are configured to measure the energy consumption by the Energest\footnote{https://github.com/contiki-ng/contiki-ng/wiki/Documentation:-Energest} module available in Contiki-ng\footnote{https://github.com/contiki-ng}.
The energy consumption is measured referring to the following formula:
\begin{equation}
	E_{tot}=\sum_{c \in comp}^{N_{c}}E_{c}=\sum_{c \in comp}^{N_{c}}I_c  \cdot V_{cc} \cdot t
\end{equation}
Where $V_{cc}$ is the supply voltage, fixed as a constant at the value $3.3V$.\\
And the single current consumption is obtained from the table \ref{tab:CurrentConsumption}\cite{inproceedings}.\\
\begin{table}[htbp]
	\begin{center}
		\begin{tabular}{ccc}
			\hline
			\textbf{State}    & \textbf{\begin{tabular}[c]{@{}c@{}}CC2538\\ datasheet\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Device\\ profiling\end{tabular}} \\ \hline
			\textbf{CPU}      & 20 mA                                                               & 15.35mA                                                             \\
			\textbf{LPM}      & 0.6 mA                                                              & 9.59 mA                                                             \\
			\textbf{Deep LPM} & 0.0013 mA                                                           & 2.58 mA                                                             \\
			\textbf{LISTEN}   & 24 mA                                                               & 28.32 mA                                                            \\
			\textbf{Rx}       & 27 mA                                                               & 30.14 mA                                                            \\
			\textbf{Tx}       & 34 mA                                                               & 31.12 mA                                                            \\ \hline
		\end{tabular}
	\end{center}
	\caption{Current draw for the TX and RX states using the CSMA
		protocol and the current drawn for TX and RX time slots using TSCH as MAC
		protocol, both when using the CC2538 radio.\cite{inproceedings}}
	\label{tab:CurrentConsumption}
\end{table}
To perform the first test only the TSCH MAC layer is enabled the rest of the stack is unused, including the security link-layer.\\
Physically speaking in this first test there is no need to measure the energy consumption variation given the distance, therefore the physical setup of the experiment consists of two Zolertia  Remote RevB boards placed at a fixed distance of approximately 10 cm.\\
At first, we have measured the energy consumption relative to the leaf node, which is only listening for data.
In figure \ref{fig:RXConsumptionTime} is possible to see the energy consumption during a period of around 27 minutes.
\begin{figure}[]
	\centering
	\includegraphics[width=.5\textwidth,keepaspectratio]{RXConsumptionTime.png}
	\caption{Zolertia leaf node energy consumption over time.}
	\label{fig:RXConsumptionTime}
\end{figure}
What is possible to notice is that most of the energy is used in deep sleep mode.\\
Then leaf node in this configuration requires only to listen, is therefore understandable that the majority of the time is spent in the lowest energy configuration, hence is important to notice that as referenced in table \ref{tab:CurrentConsumption} the deep state mode is the less energy consuming component, the board is prone to switch in this state as soon as possible to save battery.\\
In figure \ref{fig:RXConsumptionComponent} is shown the average energy consumption per component.\\
\begin{figure}[]
	\centering
	\includegraphics[width=.5\textwidth,keepaspectratio]{RXConsumptionComponent.png}
	\caption{Zolertia leaf node average energy consumption per component.}
	\label{fig:RXConsumptionComponent}
\end{figure}
Then we have performed the same experiment regarding the root coordinator node, in the same configuration for the leaf node we have measured the energy consumption over time \ref{fig:TXConsumptionTime} and per component \ref{fig:TXConsumptionComponent}.
\begin{figure}[H]
	\centering
	\includegraphics[width=.5\textwidth,keepaspectratio]{TXConsumptionTime.png}
	\caption{Zolertia root node energy consumption over time.}
	\label{fig:TXConsumptionTime}
\end{figure}
The first thing that is possible to notice is that the energy consumption of the transmitter continues to rise, due to the program on the root node itself, that as explained in the section \ref{section:task1} is required to send data to the leaf node.\\
As before analyzing the breakdown of the energy consumption shows us that the state of deep sleep is the favorite for the component.
\begin{figure}[]
	\centering
	\includegraphics[width=.5\textwidth,keepaspectratio]{TXConsumptionComponent.png}
	\caption{Zolertia root node average energy consumption per component.}
	\label{fig:TXConsumptionComponent}
\end{figure}
What is interesting to notice is the conspicuous increase of energy consumption in the root node in comparison to the leaf node, in the table \ref{tab:nodeEnergyComparison1} have been reported a comparison between the two nodes average energy consumption per component.
\begin{table}[H]
	\begin{center}
		\begin{tabular}{cccccc}
			\hline
			\textbf{Board} & \textbf{CPU} & \textbf{LPM} & \textbf{Deep} & \textbf{Tx} & \textbf{Rx} \\ \hline
			\textbf{Leaf}  & 8,738 mJ        & 7,337 mJ       & 81,697 mJ       & 11,430 mJ     & 22,326 mJ     \\
			\textbf{Root}  & 3,503 mJ       & 17,716 mJ      & 81,553 mJ       & 30,352 mJ     & 48,792 mJ     \\ \hline
		\end{tabular}
	\end{center}
	\caption{Energy consumption per component per node on average.}
	\label{tab:nodeEnergyComparison1}
\end{table}
As the last measurement, the boards have been programmed to run the same code, this receives and sends messages with an interval of around 8 seconds.\\
The boards have been running for a half an hour, the total consumption has been recorded and shown in table \ref{tab:RXTXConsumptionComponent}.\\
\begin{table}[H]
	\begin{center}
		\begin{tabular}{cccccc}
			\hline
			\textbf{Board}         & \textbf{CPU} & \textbf{LPM} & \textbf{Deep} & \textbf{Tx} & \textbf{Rx} \\ \hline
			\textbf{Leaf} & 2127 mJ      & 68768 mJ     & 18858 mJ      & 227471 mJ   & 220308 mJ   \\
			\textbf{Root} & 2127 mJ      & 68009 mJ     & 18662 mJ      & 225109 mJ   & 217921 mj   \\ \hline
		\end{tabular}
	\end{center}
	\caption{Root and leaf node running the same program, power comparison per component.}
	\label{tab:RXTXConsumptionComponent}
\end{table}
\subsection{Full stack}
The next experiment is as cited in the section \ref{section:task1} introduction related to the energy consumption once the full 6TiSCH stack has been enabled (except for the security layer).\\
The setup of this experiment is similar to the previous one.
Two boards 10cm apart from each other are running the same source code.\\
In this scenario, we have a coordinator node and a leaf node. No messages are exchanged between the two if not for standard 6TiSCH service messages.\\
As before is reported the time cumulative energy consumption regarding leaf and root node. 
\begin{figure}[H]
	\centering
	\includegraphics[width=.5\textwidth,keepaspectratio]{RootConsumptionTime.png}
	\caption{Zolertia root node energy consumption over timem full 6TiSCH stack.}
	\label{fig:RootConsumptionTime}
\end{figure}
\begin{figure}[H]
	\centering
	\includegraphics[width=.5\textwidth,keepaspectratio]{LeafConsumptionTime.png}
	\caption{Zolertia leaf node energy consumption over timem full 6TiSCH stack.}
	\label{fig:RootConsumptionTime}
\end{figure}
After a time analysis we provide a breakdown of the single components energy consumption.
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.5\textwidth,keepaspectratio]{RootConsumptionComponent.png}
	\caption{Zolertia root node average energy consumption per component.}
	\label{fig:RootConsumptionComponent}
\end{figure}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.5\textwidth,keepaspectratio]{LeafConsumptionComponent.png}
	\caption{Zolertia leaf node average energy consumption per component.}
	\label{fig:LeafConsumptionComponent}
\end{figure}
The plotted data is available at the table \ref{tab:nodeEnergyComparison2}.
\begin{table}[H]
	\begin{center}
		\begin{tabular}{cccccc}
			\hline
			\textbf{Board} & \textbf{CPU} & \textbf{LPM} & \textbf{Deep} & \textbf{Tx} & \textbf{Rx} \\ \hline
			\textbf{Leaf}  & 4,739 mJ       & 313,51 mJ      & 85,145 mJ       & 2,135 mJ      & 80,812 mJ     \\
			\textbf{Root}  & 4,417 mJ       & 313,708 mJ     & 85,145 mJ       & 0 mJ          & 81,106 mJ     \\ \hline
		\end{tabular}
	\end{center}
	\caption{Energy consumption per component per node on average.}
	\label{tab:nodeEnergyComparison2}
\end{table}
Note that the 0 energy consumption on transmission is not due to absence of transmission on the root node, but by the fact that very few packets are transmitted hence the number is too small to be reported.
\subsection{Conclusions}
In the previous subsections, we have tested the energy consumption per component at first by only using the TSCH MAC layer, and then by enabling the full 6TiSCH stack.\\
The following table reports the total energy consumption of leaf and root note in the two scenarios.
\begin{table}[H]
	\begin{center}
		\begin{tabular}{cccl}
			\cline{1-3}
			\textbf{Board}      & \textbf{Leaf} & \textbf{Root} & \textbf{}         \\ \cline{1-3}
			\textbf{Mac only}   & 131,518 mJ      & 181,916 mJ       &                   \\
			\textbf{Full stack} & 486,341 mJ      & 484,376 mJ      &                   \\ \hline
			\textbf{}           & 269,79\%      & 166,26\%      & \textbf{Increase} \\ \hline
		\end{tabular}
	\end{center}
	\caption{Total average energy consumption of leaf and root note in the two scenarios.}
	\label{tab:scenarios1Table}
\end{table}

As it is possible to see from the table \ref{tab:scenarios1Table} the energy consumption of the two nodes following the adding of the full stack increase drastically, this is normal and predictable by the fact that adding more layers on top of the single MAC add more computational requirements to the system, so a major time spent in less energy-saving states.

\begin{thebibliography}{00}
\bibitem{inproceedings} Sabovic, Adnan \& Delgado, Carmen \& Bauwens, Jan \& De Poorter, Eli \& Famaey, Jeroen. (2019). Accurate Online Energy Consumption Estimation of IoT Devices Using Energest. 363-373. 10.1007/978-3-030-33506-9\_32. 
\end{thebibliography}

\end{document}

### 2020-11-08 examples/nullnet/recieve.c

@@ -52,11 +52,11 @@
 #define LOG_LEVEL LOG_LEVEL_INFO
 
 /* Configuration */
-#define SEND_INTERVAL (8 * CLOCK_SECOND)
+#define SEND_INTERVAL (0.1 * CLOCK_SECOND)
 
 #if MAC_CONF_WITH_TSCH
 #include "net/mac/tsch/tsch.h"
-static linkaddr_t coordinator_addr =  {{ 0x00,0x12,0x4b,0x00,0x19,0x32,0xe1,0x69 }};
+static linkaddr_t coordinator_addr =  {{ 0x00,0x12,0x4b,0x00,0x19,0x32,0xe3,0x5d }};
 #endif /* MAC_CONF_WITH_TSCH */
 
 
@@ -72,10 +72,6 @@ const float wc_LISTEN =  0.02832 * vcc * 1000;
 const float wc_Rx =  0.03014 * vcc * 1000;
 const float wc_Tx =  0.03112 * vcc * 1000;
 
-static inline unsigned long to_seconds(uint64_t time)
-{
-  return (unsigned long)(time / ENERGEST_SECOND);
-}
 
 
 /*---------------------------------------------------------------------------*/
@@ -87,18 +83,57 @@ void input_callback(const void *data, uint16_t len,
   if(len == sizeof(unsigned)) {
     unsigned count;
     memcpy(&count, data, sizeof(count));
-    LOG_INFO("<--- Received %u from ", count);
-    LOG_INFO_LLADDR(src);
-    LOG_INFO_("\n");
+    //LOG_INFO("<--- Received %u from ", count);
+    //LOG_INFO_LLADDR(src);
+    //LOG_INFO_("\n");
   }
 }
 /*---------------------------------------------------------------------------*/
 PROCESS_THREAD(nullnet_example_process, ev, data)
 {
-  static struct etimer periodic_timer;
-  static unsigned count = 0;
+  static struct etimer timer;
 
   PROCESS_BEGIN();
+
+#if MAC_CONF_WITH_TSCH
+  tsch_set_coordinator(linkaddr_cmp(&coordinator_addr, &linkaddr_node_addr));
+#endif /* MAC_CONF_WITH_TSCH */
+
+
+  nullnet_set_input_callback(input_callback);
+
+  etimer_set(&timer, CLOCK_SECOND * 10);
+
+  while(1) {
[…]

### 2020-11-08 examples/nullnet/txrx.c

@@ -52,11 +52,11 @@
 #define LOG_LEVEL LOG_LEVEL_INFO
 
 /* Configuration */
-#define SEND_INTERVAL (8 * CLOCK_SECOND)
+#define SEND_INTERVAL (0.1 * CLOCK_SECOND)
 
 #if MAC_CONF_WITH_TSCH
 #include "net/mac/tsch/tsch.h"
-static linkaddr_t coordinator_addr =  {{ 0x00,0x12,0x4b,0x00,0x19,0x32,0xe1,0x69 }};
+static linkaddr_t coordinator_addr =  {{ 0x00,0x12,0x4b,0x00,0x19,0x32,0xe3,0x5d }};
 #endif /* MAC_CONF_WITH_TSCH */
 
 
@@ -72,10 +72,6 @@ const float wc_LISTEN =  0.02832 * vcc * 1000;
 const float wc_Rx =  0.03014 * vcc * 1000;
 const float wc_Tx =  0.03112 * vcc * 1000;
 
-static inline unsigned long to_seconds(uint64_t time)
-{
-  return (unsigned long)(time / ENERGEST_SECOND);
-}
 
 
 /*---------------------------------------------------------------------------*/
@@ -87,18 +83,50 @@ void input_callback(const void *data, uint16_t len,
   if(len == sizeof(unsigned)) {
     unsigned count;
     memcpy(&count, data, sizeof(count));
-    LOG_INFO("<--- Received %u from ", count);
-    LOG_INFO_LLADDR(src);
-    LOG_INFO_("\n");
+    //LOG_INFO("<--- Received %u from ", count);
+    //LOG_INFO_LLADDR(src);
+    //LOG_INFO_("\n");
   }
 }
 /*---------------------------------------------------------------------------*/
 PROCESS_THREAD(nullnet_example_process, ev, data)
 {
-  static struct etimer periodic_timer;
-  static unsigned count = 0;
 
   PROCESS_BEGIN();
+
+#if MAC_CONF_WITH_TSCH
+  tsch_set_coordinator(linkaddr_cmp(&coordinator_addr, &linkaddr_node_addr));
+#endif /* MAC_CONF_WITH_TSCH */
+
+
+  nullnet_set_input_callback(input_callback);
+
+  while(1) {
+  }
+
+  PROCESS_END();
+}
+
+
+/*---------------------------------------------------------------------------*/
[…]

### 2020-11-08 examples/task1/nullnet/nullnet-unicast.c

@@ -32,7 +32,7 @@
 
 /**
  * \file
- *         NullNet broadcast example
+ *         NullNet unicast example
  * \author
 *         Simon Duquennoy <simon.duquennoy@ri.se>
  *
@@ -41,10 +41,9 @@
 #include "contiki.h"
 #include "net/netstack.h"
 #include "net/nullnet/nullnet.h"
+
 #include <string.h>
 #include <stdio.h> /* For printf() */
-
-#include "sys/energest.h"
 
 /* Log configuration */
 #include "sys/log.h"
@@ -53,33 +52,17 @@
 
 /* Configuration */
 #define SEND_INTERVAL (8 * CLOCK_SECOND)
+static linkaddr_t dest_addr =         {{ 0x01, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 }};
 
 #if MAC_CONF_WITH_TSCH
 #include "net/mac/tsch/tsch.h"
-static linkaddr_t coordinator_addr =  {{ 0x00,0x12,0x4b,0x00,0x19,0x32,0xe1,0x69 }};
+static linkaddr_t coordinator_addr =  {{ 0x01, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 }};
 #endif /* MAC_CONF_WITH_TSCH */
 
-
-
-/* All eneergy consumptions are in mW, data from:
-   Accurate Online Energy Consumption Estimation of IoT Devices Using Energest
-*/
-const float vcc = 3.3;
-const float wc_CPU =  0.01535 * vcc * 1000;
-const float wc_LPM =  0.00959 * vcc * 1000;
-const float wc_deep_LPM = 0.00258 * vcc * 1000;
-const float wc_LISTEN =  0.02832 * vcc * 1000;
-const float wc_Rx =  0.03014 * vcc * 1000;
-const float wc_Tx =  0.03112 * vcc * 1000;
-
-static inline unsigned long to_seconds(uint64_t time)
-{
-  return (unsigned long)(time / ENERGEST_SECOND);
-}
-
-
 /*---------------------------------------------------------------------------*/
-PROCESS(nullnet_example_process, "NullNet broadcast example");
+PROCESS(nullnet_example_process, "NullNet unicast example");
+AUTOSTART_PROCESSES(&nullnet_example_process);
+
[…]

### 2020-11-08 examples/task1/nullnet/send.c

@@ -52,11 +52,11 @@
 #define LOG_LEVEL LOG_LEVEL_INFO
 
 /* Configuration */
-#define SEND_INTERVAL (8 * CLOCK_SECOND)
+#define SEND_INTERVAL (0.1 * CLOCK_SECOND)
 
 #if MAC_CONF_WITH_TSCH
 #include "net/mac/tsch/tsch.h"
-static linkaddr_t coordinator_addr =  {{ 0x00,0x12,0x4b,0x00,0x19,0x32,0xe1,0x69 }};
+static linkaddr_t coordinator_addr =  {{ 0x00,0x12,0x4b,0x00,0x19,0x32,0xe3,0x5d }};
 #endif /* MAC_CONF_WITH_TSCH */
 
 
@@ -72,40 +72,18 @@ const float wc_LISTEN =  0.02832 * vcc * 1000;
 const float wc_Rx =  0.03014 * vcc * 1000;
 const float wc_Tx =  0.03112 * vcc * 1000;
 
-static inline unsigned long to_seconds(uint64_t time)
-{
-  return (unsigned long)(time / ENERGEST_SECOND);
-}
 
 
 /*---------------------------------------------------------------------------*/
 PROCESS(nullnet_example_process, "NullNet broadcast example");
 /*---------------------------------------------------------------------------*/
-void input_callback(const void *data, uint16_t len,
-  const linkaddr_t *src, const linkaddr_t *dest)
-{
-  if(len == sizeof(unsigned)) {
-    unsigned count;
-    memcpy(&count, data, sizeof(count));
-    LOG_INFO("<--- Received %u from ", count);
-    LOG_INFO_LLADDR(src);
-    LOG_INFO_("\n");
-  }
-}
-/*---------------------------------------------------------------------------*/
+
 PROCESS_THREAD(nullnet_example_process, ev, data)
 {
   static struct etimer periodic_timer;
   static unsigned count = 0;
 
   PROCESS_BEGIN();
-
-  energest_init();
-  ENERGEST_ON(ENERGEST_TYPE_CPU);
-  ENERGEST_ON(ENERGEST_TYPE_LPM);
-  ENERGEST_ON(ENERGEST_TYPE_DEEP_LPM);
-  ENERGEST_ON(ENERGEST_TYPE_TRANSMIT);
-  ENERGEST_ON(ENERGEST_TYPE_LISTEN);
 
 #if MAC_CONF_WITH_TSCH
[…]

### 2020-11-08 Paper/conference_101719.tex
Submission state of the repository.

--- 2020-11-08 examples/task1/Paper/conference_101719.tex
@@
 \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
+%\IEEEoverridecommandlockouts
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+%\usepackage{algorithmic}
 \usepackage{graphicx}
@@
 \usepackage{float}
+\usepackage{biblatex}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Gabriele Paris}
+\author{\IEEEauthorblockN{Gabriele Paris}
 \IEEEauthorblockA{\textit{Physic department} \\
-\textit{Universiteit Antwerpen}\\
+\textit{University of Antwerp}\\
 Antwerp, Belgium \\
@@
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+% Cut out 3rd author block as Miroslav is not contributing.
+\IEEEauthorblockN{Pieter Hendriks}
+\IEEEauthorblockA{\textit{Dept computer science} \\
+\textit{University of Antwerp}\\
+Antwerp, Belgium \\
+pieter.hendriks@student.uantwerpen.be}
 }
@@
 \begin{abstract}
-To write
+In this study, we assess the performance of TSCH using the Contiki-NG operating system on Zolertia RE-mote (Rev.
+B) nodes.
+We'll show that, in two node networks, the leaf node consumes more power than the root node.
+Further, we'll assess the performance of the TSCH mode over various distances.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-6TiSCH, Contiki-NG, Energest, Zolertia
+6TiSCH, 6TSCH, Contiki-NG, Energest, IEEE 802.15.4, Power Consumption, Range, Time Slotted Channel Hopping, TiSCH, TSCH, Zolertia
 \end{IEEEkeywords}
@@
 \section{Introduction}
-To write
+This paper serves as an initial look at the performance of TSCH on the Contiki-NG operating system.
+Specifically, we're going to look at the energy consumption by the TSCH network stack vs the 6TiSCH network stack.
+We'll also analyze the TSCH joining process.
+Finally, we'll see how much impact the distance between node has on the network.
+
+\section{Related Work}
+\subsection{Throughput Analysis} \cite{ThroughputEvaluation} In this paper, an analysis of the throughput performance of TSCH networks is made.
+They show which parameters of the TSCH networks (node count, hop count, ...) influence the throughput metric in what way.
+Our research focuses on different performance characteristics of the TSCH implementation and can be useful alongside these results.
 
@@
 Where $V_{cc}$ is the supply voltage, fixed as a constant at the value $3.3V$.\\
-And the single current consumption is obtained from the table \ref{tab:CurrentConsumption}\cite{inproceedings}.\\
+And the single current consumption is obtained from the table \ref{tab:CurrentConsumption}\cite{EnergyConsumption}.\\
 \begin{table}[htbp]
@@
 		protocol and the current drawn for TX and RX time slots using TSCH as MAC
-		protocol, both when using the CC2538 radio.\cite{inproceedings}}
+		protocol, both when using the CC2538 radio.\cite{EnergyConsumption}}
 	\label{tab:CurrentConsumption}
@@
 
+%\section{Analysing the TSCH joining process}
+%\label{section:task2}
+% Miroslav not handing in, so no work here.
+
+\section{Analysing range capabilities}
+\label{section:task3}
+
+\subsection{Approach}
+
+In order to properly analyse the range capabilities, we must first define a test structure that will be repeated at each range.
+The test in this case is sending 120 packets (1 per second, 52 data bytes each) over a specified range (varying between 1 and 100 meters) so we can show the performance characteristics of TSCH as the distance between nodes varies.
+The data payload size was chosen out of convenience, as each packet carries metrics from the sender and they happened to be 52 bytes in size.
+Varying this packet size will result in different performance metrics and so must be addressed \ref{section:futurework}.
+
+Due to time constraints, combined with other obligations, the full scope of the experiments in this section has not yet been carried out.
+A brief comparison is made (showing the methodology) between nodes with 1 meter seperation and nodes with 5 meters seperation.
+Further work must be done to complete this analysis \ref{section:futurework}.
+
+As of now, though, we can show that the TSCH functionality is essentially unchanged when we're looking at 1 vs 5 meters seperation between the two nodes.
+The power requirements are within margin of error, there is no significant packet loss in either case.
+The longer distance has a slightly higher latency (potentially caused by more retransmissions, we'll need to look at this \ref{section:futurework}).
+
+For this analysis, we disabled the 6TiSCH stack (using only the TSCH mac layer) and ensured no security was enabled. No further changes to the Contiki-NG network stack were required.
+
+\subsection{Results}
+
+\subsubsection{1 meter separation}
+\label{section:1metersep}
+First, we'll compare the latencies.
+At 1 meter seperation, we found, on average, 9.29 timeslots delay between the enqueueing of the packet on the sender's side and the arrival on the receiver's side \ref{fig:latencies1m}.
+Presumably, a majority of this time is spent in the queue (or in re-transmissions), but this will be verified later \ref{section:futurework}.
+Over the distance of 1 meter, there is 100\% packet arrival rate.
+
+Regarding power use, then, we see that the leaf node consumes more power than the root node does.
+This is shown in \ref{fig:powerState1m}, combined with the current draw for each power state as described in \ref{tab:CurrentConsumption}.
+Overall, we find that the leaf node has used approximately 4.35 joules of energy whereas that value is only 2.58 joules for the root node.
+Since each packet carried a data payload of 52 bytes, we find the following power requirements: roughly 89 $\frac{mJ}{kbit}$ for the leaf node and  53 $\frac{mJ}{kbit}$ for the root node.
+
+\begin{figure}[]
+	\centering
+	\includegraphics[width=.5\textwidth,keepaspectratio]{1m_latencies.png}
+	\caption{Latencies for packets sent between two nodes at 1 meter seperation.}
+	\label{fig:latencies1m}
+\end{figure}
+\begin{figure}[]
+	\centering
+	\includegraphics[width=.5\textwidth,keepaspectratio]{5m_latencies.png}
+	\caption{Latencies for packets sent between two nodes at 5 meter seperation.}
+	\label{fig:latencies5m}
+\end{figure}
+
+\subsubsection{5 meters separation}
+
+When we increase the distance to 5 meters, not much changes.
+As the distance is still very small (and should be easily within range), this is to be expected.
+The packet delivery ratio is still at 100\%, latency is slightly increased to rougly 9.33 slots (but this could be within margin of error -  we should look at retransmission rates to verify \ref{section:futurework}).
+
+The energy consumption is essentially the same, they are definitely within margin of error for our current test setup and so will not be discussed further than they have been in \ref{section:1metersep}.
+
+\begin{figure}[]
+	\centering
+	\includegraphics[width=.5\textwidth,keepaspectratio]{1m_powerStates.png}
+	\caption{The time a node spends in each power state at 1 meter seperation.}
+	\label{fig:powerState1m}
+\end{figure}
+\begin{figure}[]
+	\centering
+	\includegraphics[width=.5\textwidth,keepaspectratio]{5m_powerStates.png}
+	\caption{The time a node spends in each power state at 5 meters seperation.}
+	\label{fig:powerState5m}
+\end{figure}
+
+%PACKET ARRIVAL RATE: 1.0
+%AVERAGE LATENCY: 9.291666666666666
+%LEAF ENERGY CONSUMPTION: 4.347331036560059 J
+%ROOT ENERGY CONSUMPTION: 2.577431278930664 J
+%Since each packet carried a data payload of 52 bytes, that's
+%	LEAF: 10.701122551532452 J/kbit
+%	ROOT: 6.344446225060096 J/kbit
+%PACKET ARRIVAL RATE: 1.0
+%AVERAGE LATENCY: 9.333333333333334
+%LEAF ENERGY CONSUMPTION: 4.345094247253417 J
+%ROOT ENERGY CONSUMPTION: 2.578182406585693 J
+%Since each packet carried a data payload of 52 bytes, that's
+%	LEAF: 10.695616608623796 J/kbit
+%	ROOT: 6.346295154672475 J/kbit
+
+\section{Future Work}
+
+\label{section:futurework}
+\begin{itemize}
+\item Analyze the TSCH joining process
+\item Perform the experiments as required for \ref{section:task3}
+\item Further discuss the current results in \ref{section:task3}
+\item Further analyze the found flaws in \ref{section:task3}
+\end{itemize}
+
 \begin{thebibliography}{00}
-\bibitem{inproceedings} Sabovic, Adnan \& Delgado, Carmen \& Bauwens, Jan \& De Poorter, Eli \& Famaey, Jeroen.
+\bibitem{EnergyConsumption} Sabovic, Adnan \& Delgado, Carmen \& Bauwens, Jan \& De Poorter, Eli \& Famaey, Jeroen.
 (2019).
@@
 10.1007/978-3-030-33506-9\_32.
+\bibitem{ThroughputEvaluation} Lee, S.
+B., Kim, E.
+J., \& Lim, Y.
+(2018).
+Contiki-NG-based IEEE 802.15.
+4 TSCH Throughput Evaluation.
+In Proceedings of the Korean Institute of Information and Commucation Sciences Conference (pp.
+577-578).
+The Korea Institute of Information and Commucation Engineering.
 \end{thebibliography}

### 2020-11-08 examples/task3/my_app.c

@@ -60,7 +60,7 @@
 
 /* Configuration */
 #define SEND_INTERVAL CLOCK_SECOND
-#define PACKET_SIZE 32 // in bytes, data section
+#define PACKET_SIZE 52 // in bytes, data section
 // Define the runtime, coordinator will run longer to allow attachment etc.
 // We start counting non-coord runtime from when attachment occurs.
 #if MYAPP_AS_COORDINATOR == 1
@@ -88,18 +88,30 @@ void input_callback(const void *data, uint16_t len,
 	// TODO: REMOVE ABOVE COMMENT, needs to work with length check somehow.
 		#if MYAPP_AS_COORDINATOR == 1
     unsigned count;
-
-    memcpy(&count, data, sizeof(count));
+		uint16_t currentOffset = 0;
+    memcpy(&count, data + currentOffset, sizeof(count)); currentOffset += sizeof(count);
 		uint64_t sentTime;
-		memcpy(&sentTime, data+sizeof(count), sizeof(sentTime));
+		memcpy(&sentTime, data + currentOffset, sizeof(sentTime)); currentOffset += sizeof(sentTime);
     LOG_INFO("<--- Received %u from ", count);
     LOG_INFO_LLADDR(src);
 		LOG_INFO_(" at time %"PRIu64", sent at time %"PRIu64" (latency is %"PRIu64")", tsch_get_network_uptime_ticks(), sentTime, tsch_get_network_uptime_ticks() - sentTime);
     LOG_INFO_("\n");
+		uint64_t senderPower[5] = {0, 0, 0, 0, 0};
+		memcpy(&(senderPower[0]), data + currentOffset, sizeof(uint64_t)); currentOffset += sizeof(uint64_t);
+		memcpy(&(senderPower[1]), data + currentOffset, sizeof(uint64_t)); currentOffset += sizeof(uint64_t);
+		memcpy(&(senderPower[2]), data + currentOffset, sizeof(uint64_t)); currentOffset += sizeof(uint64_t);
+		memcpy(&(senderPower[3]), data + currentOffset, sizeof(uint64_t)); currentOffset += sizeof(uint64_t);
+		memcpy(&(senderPower[4]), data + currentOffset, sizeof(uint64_t)); currentOffset += sizeof(uint64_t);
[…]

### 2020-11-28 Paper/Paper.tex
Added new part to paper and cleaned it

--- 2020-11-08 Paper/conference_101719.tex
@@
 \usepackage{float}
-\usepackage{biblatex}
+\usepackage{cite}
+\usepackage{url}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \author{\IEEEauthorblockN{Gabriele Paris}
-\IEEEauthorblockA{\textit{Physic department} \\
+\IEEEauthorblockA{\textit{Dept physic} \\
 \textit{University of Antwerp}\\
@@
 \section{Introduction}
+The IETF IPv6 over the TSCH mode of IEEE802.15.4e (6TiSCH) working group has standardized a set of protocols to enable low power industrial-grade IPv6 networks.
+6TiSCH proposes a protocol stack rooted in the Time Slotted Channel Hopping (TSCH) mode of the IEEE802.15.4-2015 standard, supports multi-hop topologies with the IPv6 Routing Protocol for Low-Power and Lossy Networks (RPL) routing protocol, and is IPv6-ready through 6LoWPAN\cite{6tischDef}.
+
+Contiki-NG is an operating system for resource-constrained devices in the Internet of Things.
+Contiki-NG contains an RFC-compliant, low-power IPv6 communication stack, enabling Internet connectivity.
+The system runs on a variety of platforms based on energy-efficient architectures such as the ARM Cortex-M3/M4 and the Texas Instruments MSP430.
+The code footprint is on the order of a 100 kB, and the memory usage can be configured to be as low as 10 kB.
+
 This paper serves as an initial look at the performance of TSCH on the Contiki-NG operating system.
@@
 In the first analysis, we compared the energy consumption during a certain time period of the entire 6TiSCH stack to when only enabling the TSCH MAC layer (without link-layer security) after network convergence.\\
+The full stack can be seen as in Figure \ref{fig:6tischStack}.
+
 For both analyses, we report on the consumption of the root and the leaf node separately.\\
-Following we remark differences in energy consumption between the root and the leaf node.
+Following we remark differences in energy consumption between the root and the leaf node in the two different scenarios.
 
-\subsection{Only TSCH MAC layer}
-The basic setup for the following analysis is a root (coordinator) node that sends packets to a leaf node at a rate of 1 packet of 4 bytes per second.\\
-Note that the root node has no event routine related to data reception. In the same way, the leaf node has no code which permits data transmission.\\
-Both nodes are configured to measure the energy consumption by the Energest\footnote{https://github.com/contiki-ng/contiki-ng/wiki/Documentation:-Energest} module available in Contiki-ng\footnote{https://github.com/contiki-ng}.
+The Time-Slotted Channel Hopping (TSCH) mode for medium access control (MAC) included in the standard IEEE 802.15.4 has been designed as the multichannel MAC protocol for Low-power and lossy networks (LLNs), a key component of the Internet of Things (IoT).
+Its ﬂexibility makes the TSCH mode a very promising candidate for the future of the MAC layer in LLNs.
+As such, its performance under different conditions must be assessed, so that accurate guidelines for its application can be drawn\cite{TSCHExperimentEval}.
+\begin{figure}[]
+	\centering
+	\includegraphics[width=.25\textwidth,keepaspectratio]{6TiSCH-Protocol-Stack.png}
+	\caption{6TiSCH Protocol Stack\cite{TimeCritical6tisch}.}
+	\label{fig:6tischStack}
+\end{figure}
+
+the physical setup of the experiment consists of two Zolertia  Remote RevB boards placed at a fixed distance of approximately 20 cm as shown in Figure \ref{fig:exp1Topology}.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=.35\textwidth,keepaspectratio]{exp1Topology.pdf}
+	\caption{Network topology for 6TiSCH energy consumption analysis.}
+	\label{fig:exp1Topology}
+\end{figure}
+The basic setup for the following analysis are a root (coordinator) node and a leaf node that exchange the same ammount of data packets.\\
+Both nodes are configured to measure the energy consumption by the Energest\footnote{https://github.com/contiki-ng/contiki-ng/wiki/Documentation:-Energest} module available in Contiki-ng\footnote{https://github.com/contiki-ng}.\\
+The Energest module can be used to implement lightweight, software-based energy estimation approach for resource-constrained IoT devices.
+By tracking the time various hardware states such as the radio is turned on, and by knowing the power consumption of the state, it is possible to estimate the energy consumption\cite{contiki-NGWiki}.\\
 The energy consumption is measured referring to the following formula:
 \begin{equation}
-	E_{tot}=\sum_{c \in comp}^{N_{c}}E_{c}=\sum_{c \in comp}^{N_{c}}I_c  \cdot V_{cc} \cdot t
+	E_{tot}=\sum_{c \in state}^{N_{s}}E_{s}=\sum_{s \in state}^{N_{s}}I_s  \cdot V_{cc} \cdot t
 \end{equation}
-Where $V_{cc}$ is the supply voltage, fixed as a constant at the value $3.3V$.\\
-And the single current consumption is obtained from the table \ref{tab:CurrentConsumption}\cite{EnergyConsumption}.\\
+Where $V_{cc}$ is the supply voltage, fixed as a constant at the value $3.3V$, $I_s$ is provided by the Table \ref{tab:CurrentConsumption} column \textit{Device profiling}\cite{EnergyConsumption}, and $t$ is measured using Energest.\\
+All measurements are performed in a span of 15 minutes each.
 \begin{table}[htbp]
@@
 	\end{center}
-	\caption{Current draw for the TX and RX states using the CSMA
-		protocol and the current drawn for TX and RX time slots using TSCH as MAC
-		protocol, both when using the CC2538 radio.\cite{EnergyConsumption}}
+	\caption{Comparison between values from the datasheet and N6705B DC Power Analyzer radio.\cite{EnergyConsumption}}
 	\label{tab:CurrentConsumption}
 \end{table}
-To perform the first test only the TSCH MAC layer is enabled the rest of the stack is unused, including the security link-layer.\\
-Physically speaking in this first test there is no need to measure the energy consumption variation given the distance, therefore the physical setup of the experiment consists of two Zolertia  Remote RevB boards placed at a fixed distance of approximately 10 cm.\\
-At first, we have measured the energy consumption relative to the leaf node, which is only listening for data.
-In figure \ref{fig:RXConsumptionTime} is possible to see the energy consumption during a period of around 27 minutes.
-\begin{figure}[]
+\subsection{Only TSCH MAC layer}
+In the first part of the experiment, we used only the stack till the MAC layer (TSCH) as shown in Figure \ref{fig:6tischStack}.\\
+We proceeded as explained in the setup to measure the energy consumption between leaf and root node.\\
+Results are reported in Table \ref{tab:MACOnly}.
+\begin{table}[h]
 	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{RXConsumptionTime.png}
-	\caption{Zolertia leaf node energy consumption over time.}
-	\label{fig:RXConsumptionTime}
-\end{figure}
-What is possible to notice is that most of the energy is used in deep sleep mode.\\
-Then leaf node in this configuration requires only to listen, is therefore understandable that the majority of the time is spent in the lowest energy configuration, hence is important to notice that as referenced in table \ref{tab:CurrentConsumption} the deep state mode is the less energy consuming component, the board is prone to switch in this state as soon as possible to save battery.\\
-In figure \ref{fig:RXConsumptionComponent} is shown the average energy consumption per component.\\
-\begin{figure}[]
-	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{RXConsumptionComponent.png}
-	\caption{Zolertia leaf node average energy consumption per component.}
-	\label{fig:RXConsumptionComponent}
-\end{figure}
-Then we have performed the same experiment regarding the root coordinator node, in the same configuration for the leaf node we have measured the energy consumption over time \ref{fig:TXConsumptionTime} and per component \ref{fig:TXConsumptionComponent}.
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{TXConsumptionTime.png}
-	\caption{Zolertia root node energy consumption over time.}
-	\label{fig:TXConsumptionTime}
-\end{figure}
-The first thing that is possible to notice is that the energy consumption of the transmitter continues to rise, due to the program on the root node itself, that as explained in the section \ref{section:task1} is required to send data to the leaf node.\\
-As before analyzing the breakdown of the energy consumption shows us that the state of deep sleep is the favorite for the component.
-\begin{figure}[]
-	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{TXConsumptionComponent.png}
-	\caption{Zolertia root node average energy consumption per component.}
-	\label{fig:TXConsumptionComponent}
-\end{figure}
-What is interesting to notice is the conspicuous increase of energy consumption in the root node in comparison to the leaf node, in the table \ref{tab:nodeEnergyComparison1} have been reported a comparison between the two nodes average energy consumption per component.
-\begin{table}[H]
-	\begin{center}
-		\begin{tabular}{cccccc}
+	\begin{tabular}{llllll}
 		\hline
-			\textbf{Board} & \textbf{CPU} & \textbf{LPM} & \textbf{Deep} & \textbf{Tx} & \textbf{Rx} \\ \hline
-			\textbf{Leaf}  & 8,738 mJ        & 7,337 mJ       & 81,697 mJ       & 11,430 mJ     & 22,326 mJ     \\
-			\textbf{Root}  & 3,503 mJ       & 17,716 mJ      & 81,553 mJ       & 30,352 mJ     & 48,792 mJ     \\ \hline
+		\textbf{Node} & \multicolumn{1}{c}{\textbf{CPU}} & \multicolumn{1}{c}{\textbf{LPM}} & \multicolumn{1}{c}{\textbf{Deep}} & \multicolumn{1}{c}{\textbf{Tx}} & \multicolumn{1}{c}{\textbf{Rx}} \\ \hline
+		\textbf{Leaf} & 3.330 mJ                         & 314.385 mJ                       & 85.143 mJ                         & 1.132 mJ                        & 993.527 mJ                      \\
+		\textbf{Root} & 3.330 mJ                         & 314.385 mJ                       & 85.143 mJ                         & 1.132 mJ                        & 993.527 mJ                      \\ \hline
 	\end{tabular}
-	\end{center}
-	\caption{Energy consumption per component per node on average.}
-	\label{tab:nodeEnergyComparison1}
+	\caption{Average power consumption comparison between root and leaf node per state, TSCH MAC only.}
+	\label{tab:MACOnly}
 \end{table}
-As the last measurement, the boards have been programmed to run the same code, this receives and sends messages with an interval of around 8 seconds.\\
-The boards have been running for a half an hour, the total consumption has been recorded and shown in table \ref{tab:RXTXConsumptionComponent}.\\
-\begin{table}[H]
-	\begin{center}
-		\begin{tabular}{cccccc}
-			\hline
-			\textbf{Board}         & \textbf{CPU} & \textbf{LPM} & \textbf{Deep} & \textbf{Tx} & \textbf{Rx} \\ \hline
-			\textbf{Leaf} & 2127 mJ      & 68768 mJ     & 18858 mJ      & 227471 mJ   & 220308 mJ   \\
-			\textbf{Root} & 2127 mJ      & 68009 mJ     & 18662 mJ      & 225109 mJ   & 217921 mj   \\ \hline
-		\end{tabular}
-	\end{center}
-	\caption{Root and leaf node running the same program, power comparison per component.}
-	\label{tab:RXTXConsumptionComponent}
-\end{table}
+What we can see is that data from root and leaf nodes show no variation, and the energy consumed from both of them is the same.
 \subsection{Full stack}
 The next experiment is as cited in the section \ref{section:task1} introduction related to the energy consumption once the full 6TiSCH stack has been enabled (except for the security layer).\\
-The setup of this experiment is similar to the previous one.
-Two boards 10cm apart from each other are running the same source code.\\
-In this scenario, we have a coordinator node and a leaf node. No messages are exchanged between the two if not for standard 6TiSCH service messages.\\
-As before is reported the time cumulative energy consumption regarding leaf and root node. 
-\begin{figure}[H]
+The setup of this experiment is the same to the previous one.
+Two boards 10cm apart from each other (\ref{fig:exp1Topology}) are running the same source code.\\
+In this scenario, we have a coordinator node and a leaf node.\\
+No messages are exchanged between the two if not for standard 6TiSCH service messages.\\
+We proceeded as explained in the setup to measure the energy consumption between leaf and root node.\\
+Results are reported in Table \ref{tab:FullStack}.
+\begin{table}[h]
 	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{RootConsumptionTime.png}
-	\caption{Zolertia root node energy consumption over timem full 6TiSCH stack.}
-	\label{fig:RootConsumptionTime}
-\end{figure}
-\begin{figure}[H]
+	\begin{tabular}{llllll}
+		\hline
+		\textbf{Node} &
+		\multicolumn{1}{c}{\textbf{CPU}} &
+		\multicolumn{1}{c}{\textbf{LPM}} &
+		\multicolumn{1}{c}{\textbf{Deep}} &
+		\multicolumn{1}{c}{\textbf{Tx}} &
+		\multicolumn{1}{c}{\textbf{Rx}} \\ \hline
+		\textbf{Leaf} &
+		5.00 mJ &
+		313.341 mJ &
+		85.143 mJ &
+		80.121 mJ &
+		98.362 mJ \\
+		\textbf{Root} &
+		3.890 mJ &
+		310.560 mJ &
+		84.209 mJ &
+		0 mJ &
+		33.879 mJ \\ \hline
+	\end{tabular}
+	\caption{Average power consumption per state between root and leaf node, full 6TiSCH  stack.}
+	\label{tab:FullStack}
+\end{table}
+\subsection{Final comparison}
+As a final comparison, we compared the total energy usage between root and leaf nodes in the two configurations.
+What we measured has been reported as Table \ref{tab:exp1Comparison}.
+\begin{table}[h]
 	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{LeafConsumptionTime.png}
-	\caption{Zolertia leaf node energy consumption over timem full 6TiSCH stack.}
-	\label{fig:RootConsumptionTime}
-\end{figure}
-After a time analysis we provide a breakdown of the single components energy consumption.
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{RootConsumptionComponent.png}
-	\caption{Zolertia root node average energy consumption per component.}
-	\label{fig:RootConsumptionComponent}
-\end{figure}
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{LeafConsumptionComponent.png}
-	\caption{Zolertia leaf node average energy consumption per component.}
-	\label{fig:LeafConsumptionComponent}
-\end{figure}
-The plotted data is available at the table \ref{tab:nodeEnergyComparison2}.
-\begin{table}[H]
-	\begin{center}
-		\begin{tabular}{cccccc}
+	\begin{tabular}{cll}
 		\hline
-			\textbf{Board} & \textbf{CPU} & \textbf{LPM} & \textbf{Deep} & \textbf{Tx} & \textbf{Rx} \\ \hline
-			\textbf{Leaf}  & 4,739 mJ       & 313,51 mJ      & 85,145 mJ       & 2,135 mJ      & 80,812 mJ     \\
-			\textbf{Root}  & 4,417 mJ       & 313,708 mJ     & 85,145 mJ       & 0 mJ          & 81,106 mJ     \\ \hline
+		\textbf{Node} & \multicolumn{1}{c}{\textbf{MAC only}} & \multicolumn{1}{c}{\textbf{Full stack}} \\ \hline
+		\textbf{Leaf} & 1.398 J                                & 0.582 J                                  \\
+		\textbf{Root} & 1.398 J                                & 0.433 J                                  \\ \hline
 	\end{tabular}
-	\end{center}
-	\caption{Energy consumption per component per node on average.}
-	\label{tab:nodeEnergyComparison2}
+	\caption{Energy comparison between leaf and root node in MAC only and full stack configurations.}
+	\label{tab:exp1Comparison}
 \end{table}
-Note that the 0 energy consumption on transmission is not due to absence of transmission on the root node, but by the fact that very few packets are transmitted hence the number is too small to be reported.
-\subsection{Conclusions}
-In the previous subsections, we have tested the energy consumption per component at first by only using the TSCH MAC layer, and then by enabling the full 6TiSCH stack.\\
-The following table reports the total energy consumption of leaf and root note in the two scenarios.
-\begin{table}[H]
-	\begin{center}
-		\begin{tabular}{cccl}
-			\cline{1-3}
-			\textbf{Board}      & \textbf{Leaf} & \textbf{Root} & \textbf{}         \\ \cline{1-3}
-			\textbf{Mac only}   & 131,518 mJ      & 181,916 mJ       &                   \\
-			\textbf{Full stack} & 486,341 mJ      & 484,376 mJ      &                   \\ \hline
-			\textbf{}           & 269,79\%      & 166,26\%      & \textbf{Increase} \\ \hline
-		\end{tabular}
-	\end{center}
-	\caption{Total average energy consumption of leaf and root note in the two scenarios.}
-	\label{tab:scenarios1Table}
-\end{table}
-
-As it is possible to see from the table \ref{tab:scenarios1Table} the energy consumption of the two nodes following the adding of the full stack increase drastically, this is normal and predictable by the fact that adding more layers on top of the single MAC add more computational requirements to the system, so a major time spent in less energy-saving states.
 
@@
 % Miroslav not handing in, so no work here.
+%
+%			¯\_( ͡° ͜ʖ ͡°)_/¯
+%
 
@@
 
-\begin{figure}[]
-	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{1m_latencies.png}
-	\caption{Latencies for packets sent between two nodes at 1 meter seperation.}
-	\label{fig:latencies1m}
-\end{figure}
-\begin{figure}[]
-	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{5m_latencies.png}
-	\caption{Latencies for packets sent between two nodes at 5 meter seperation.}
-	\label{fig:latencies5m}
-\end{figure}
+%\begin{figure}[]
+%	\centering
+%	\includegraphics[width=.5\textwidth,keepaspectratio]{1m_latencies.png}
+%	\caption{Latencies for packets sent between two nodes at 1 meter seperation.}
+%	\label{fig:latencies1m}
+%\end{figure}
+%\begin{figure}[]
+%	\centering
+%	\includegraphics[width=.5\textwidth,keepaspectratio]{5m_latencies.png}
+%	\caption{Latencies for packets sent between two nodes at 5 meter seperation.}
+%	\label{fig:latencies5m}
+%\end{figure}
 
@@
 
-\begin{figure}[]
-	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{1m_powerStates.png}
-	\caption{The time a node spends in each power state at 1 meter seperation.}
-	\label{fig:powerState1m}
-\end{figure}
-\begin{figure}[]
-	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{5m_powerStates.png}
-	\caption{The time a node spends in each power state at 5 meters seperation.}
-	\label{fig:powerState5m}
-\end{figure}
+%\begin{figure}[]
+%	\centering
+%	\includegraphics[width=.5\textwidth,keepaspectratio]{1m_powerStates.png}
+%	\caption{The time a node spends in each power state at 1 meter seperation.}
+%	\label{fig:powerState1m}
+%\end{figure}
+%\begin{figure}[]
+%	\centering
+%	\includegraphics[width=.5\textwidth,keepaspectratio]{5m_powerStates.png}
+%	\caption{The time a node spends in each power state at 5 meters seperation.}
+%	\label{fig:powerState5m}
+%\end{figure}
 
@@
 \begin{thebibliography}{00}
+\bibitem{contiki-NGWiki} Adam Dunkels, \url {https://github.com/contiki-ng/contiki-ng/wiki}
+\bibitem{6tischDef} X.
+Vilajosana, T.
+Watteyne, T.
+Chang, M.
+Vučinić, S.
+Duquennoy and P.
+Thubert, "IETF 6TiSCH: A Tutorial," in IEEE Communications Surveys \& Tutorials, vol.
+22, no.
+1, pp.
+595-615, Firstquarter 2020, doi: 10.1109/COMST.2019.2939407.
+\bibitem{TimeCritical6tisch} Karaagac, Abdulkadir \& Haxhibeqiri, Jetmir \& Moerman, Ingrid \& Hoebeke, Jeroen.
+(2018).
+Time-critical communication in 6TiSCH networks.
+161-166.
+10.1109/WCNCW.2018.8368987.
 \bibitem{EnergyConsumption} Sabovic, Adnan \& Delgado, Carmen \& Bauwens, Jan \& De Poorter, Eli \& Famaey, Jeroen.
@@
 The Korea Institute of Information and Commucation Engineering.
+\bibitem{TSCHExperimentEval} García Algora, Carlos \& Alfonso Reguera, Vitalio. (2018). Experimental evaluation of IEEE 802.15.4 TSCH on a 6TiSCH network. 39. 70-78. 
 \end{thebibliography}

### 2020-12-05 Paper/Paper.tex
Paper

@@
 \begin{IEEEkeywords}
-6TiSCH, 6TSCH, Contiki-NG, Energest, IEEE 802.15.4, Power Consumption, Range, Time Slotted Channel Hopping, TiSCH, TSCH, Zolertia
+6TiSCH, Contiki-NG, Energest, IEEE 802.15.4, Power Consumption, Range, Time Slotted Channel Hopping, TiSCH, TSCH, Zolertia
 \end{IEEEkeywords}
@@
 
+The hardware in use are Zolertia RE-Mote boards, designed jointly with universities and industry partners in RERUM European project, to ease the development of private and secure applications for IoT and Smart City applications.\\
+The RE-Mote packs several onboard resources, like an RTC, external WDT, Micro-SD, RF switch, and a Shutdown mode to reduce its power consumption down to 150nA\cite{contiki-NGWiki}.
+
 \section{Related Work}
-\subsection{Throughput Analysis} \cite{ThroughputEvaluation} In this paper, an analysis of the throughput performance of TSCH networks is made.
+\subsection{Accurate energy consumption using Energest}
+In section \ref{section:task1} of this paper, we focus on the analysis of the energy consumption between leaf and root node.
+This analysis can be done by knowing different parameters like current, tension, and time.\\
+tension is always $3.3V$, current instead should be correctly provided in the board datasheet, previous works have shown that real current consumption values are different from the datasheet provided ones\cite{EnergyConsumption}, in this paper, we are going to use such current measurements to determine the energy consumption.
+\subsection{Throughput Analysis} In this paper, an analysis of the throughput performance of TSCH networks is made.
 They show which parameters of the TSCH networks (node count, hop count, ...) influence the throughput metric in what way.
-Our research focuses on different performance characteristics of the TSCH implementation and can be useful alongside these results.
+Our research focuses on different performance characteristics of the TSCH implementation and can be useful alongside these results\cite{ThroughputEvaluation}.
 
@@
 \begin{equation}
-	E_{tot}=\sum_{c \in state}^{N_{s}}E_{s}=\sum_{s \in state}^{N_{s}}I_s  \cdot V_{cc} \cdot t
+	E_{tot}=\sum_{s \in state}^{N_{s}}E_{s}=\sum_{s \in state}^{N_{s}}I_s  \cdot V_{cc} \cdot t
 \end{equation}
@@
 \subsection{Only TSCH MAC layer}
-In the first part of the experiment, we used only the stack till the MAC layer (TSCH) as shown in Figure \ref{fig:6tischStack}.\\
+In the first part of the experiment, we used only the stack till the MAC layer (TSCH) as shown in Figure \ref{fig:6tischStack}.
+In TSCH networks, every node follows a time-synchronized schedule.
+This schedule instructs every node about exactly what to do and avoids wasting valuable energy.
+The TSCH schedule is divided into time slots.
+The duration of a time slot is typically 10 ms or 15 ms and sufficient to transmit a packet of the maximum size of 127 bytes, immediately followed by an optional acknowledgment frame indicating that the packet was successfully received.
+Multiple time slots are grouped into a slot frame, and the size of a slot frame defines the width of the schedule.
+These slot frames repeat continuously over time.
+TSCH also allows one to use multiple frequencies, leading to a two-dimensional matrix of cells.
+The number of available frequencies actually determines the height of the schedule\cite{AccurateEnergyTSCH}.
+
 We proceeded as explained in the setup to measure the energy consumption between leaf and root node.\\
@@
 \end{table}
-What we can see is that data from root and leaf nodes show no variation, and the energy consumed from both of them is the same.
+What we can see is that data from root and leaf nodes show no variation, and the energy consumed from both of them is the same.\\
+In a TSCH network The root needs to control the way the network is formed, including how new nodes join and how already joined nodes advertise the presence of the network, this is all encoded in the TSCH RFC\footnote{https://tools.ietf.org/html/rfc7554}.\\
+The root node during network convergence needs to:
+\begin{itemize}
+	\item Define the Information Elements included in the Enhanced Beacons, advertising the presence of the network;
+	\item for a new node define rules to process and filter received EBs;
+	\item Define the joining procedure.  This might include a mechanism to assign a unique 16-bit address to a node and the management of initial keying material;
+	\item Define a mechanism to secure the joining process and the subsequent optional process of scheduling more communication cells.
+\end{itemize}
+After the network has been formed it must be mantained, this implies that the root node must:
+\begin{itemize}
+	\item Manage each node's time source neighbor;
+	\item Define a mechanism for a node to update the join priority it announces in its EB;
+	\item Schedule transmissions of EBs to advertise the presence of the network.
+\end{itemize}
+We can therefore say that, atleast for two node, the workload on the root is not enought to show a difference in energy consumption during the stated time spam.
 \subsection{Full stack}
@@
 \bibitem{TSCHExperimentEval} García Algora, Carlos \& Alfonso Reguera, Vitalio. (2018). Experimental evaluation of IEEE 802.15.4 TSCH on a 6TiSCH network. 39. 70-78.
+\bibitem{AccurateEnergyTSCH} Accurate Energy Consumption Modeling of IEEE 802.15.4e TSCH Using Dual-BandOpenMote Hardware
+Glenn Daneels, Esteban Municio, Bruno Van de Velde, Glenn Ergeerts, Maarten Weyn, Steven Latré, \& Jeroen Famaey
+
 \end{thebibliography}

### 2020-12-05 Paper/Paper.tex
Added text to the abstract

@@
 \begin{abstract}
-In this study, we assess the performance of TSCH using the Contiki-NG operating system on Zolertia RE-mote (Rev.
-B) nodes.
-We'll show that, in two node networks, the leaf node consumes more power than the root node.
-Further, we'll assess the performance of the TSCH mode over various distances.
+In this paper, we assess the energy performance of TSCH and 6TiSCH using the Contiki-NG operating system on Zolertia RE-mote (Rev. B) nodes.\\
+These boards are part of the IoT hardware family, and they allow for the creation of a network minimizing energy consumption.\\
+The paper is subdivided into three main sections: in the first one, we will compare the energy consumption of the leaf and root node (LLC) at first using up to the MAC TSCH layer, and then using the full stack.\\
+In the second section, we will analyze the TSCH joining process and relative energy consumption. Further, in the final section, we will assess the performance of the TSCH mode over various distances.
 \end{abstract}

### 2020-12-11 Paper/Paper.tex
Updated with recent work. Task3 mostly done now, only need to verify with bigger distances and higher power variance. Methodology should be mostly sound.

@@
 This paper serves as an initial look at the performance of TSCH on the Contiki-NG operating system.
-Specifically, we're going to look at the energy consumption by the TSCH network stack vs the 6TiSCH network stack.
-We'll also analyze the TSCH joining process.
-Finally, we'll see how much impact the distance between node has on the network.
+Specifically, we look at the energy consumption by the TSCH network stack vs the 6TiSCH network stack, we analyze the TSCH joining process, and we measure the impact node separation has on the network's performance and energy characteristics.
 
@@
 
-\subsection{Approach}
+\subsection{Configuration} 
+For the most part, the default configuration of Contiki-NG is used. Any non-default values we've used, as well as other important details, are discussed here.
+
+\subsubsection{Network topology}
+We study a two-node TSCH network.
+Both nodes are Zolertia RE-mote (Rev.
+B) boards.
+One will act as the TSCH coordinator, the other as a leaf node.
+In all tests performed in this section, the traffic originates at the leaf node (and is sent to the coordinator).
+
+The nodes always remain within line of sight, at equal heights.
+The only physical parameter being varied (other than those outside our control) is the distance between them.
+For our range analysis, we consider four distances: 1 meter, 3 meters, 5 meters and 10 meters.
+For each of these values, the transmit power (see section \ref{section:txpower}) is varied as well - all permutations are considered.
+
+\subsubsection{Traffic characteristics}
+The traffic is uniform, 1 packet is sent per second.
+The packets contain 64 bytes of data.
+This value is chosen because it is a nice, round number that is sufficiently large for a few measurements (depending on the application), while remaining small enough to be sent over the TSCH layer without fragmentation.
+
+\subsubsection{TX power}
+\label{section:txpower}
+The transmit power parameter controls the intensity of the signal transmission.
+A larger TX power value leads to increased energy consumption.
+The amount of extra energy consumed by varying this value is left outside the scope of this study.
+We study 3 values for this parameter, the default value (3 dBm), the maximal value (7 dBm) and a smaller value (-1 dBm).
+The TX power is kept the same between the two nodes at all times.
+
+\subsubsection{TSCH schedule}
+\label{section:tschschedule}
+
+We use a very simple schedule for our experiments.
+There is a single advertising-only cell at (0, 0) and a cell used to transmit our data packets at (1, 1).
+The (0, 0) cell is used for beacons, so that the leaf node can join the network.
+It is not used for any of our measurements.
+All data we collect is sent on the (1, 1) cell.
+That cell is configured as a transmit-only (to the coordinator) cell in the leaf node and a receive-only (from the leaf) cell in the coordinator node.
+This setup is illustrated in figure \ref{fig:tsch_schedule}.
+The red cell is the cell used for EBs, where the root node advertises.
+The blue cell is used for all data transmissions from the leaf to the root.
+Contiki-NG, by default, configures TSCH with 7 slots per slotframe and 4 channels.
+We have left these parameters unchanged.
+\begin{figure}[]
+	\centering
+	\includegraphics[width=.4\textwidth,keepaspectratio]{tsch_schedule.png}
+	\caption{TSCH Schedule as used in the range analysis experiments}
+	\label{fig:6tischStack}
+\end{figure}
+
+\subsubsection{Network stack}
+\label{section:netstack}
+
+For these experiments, most of the default Contiki-NG network stack has been disabled.
+We're interested in the performance of TSCH, so our experiments interact directly with the MAC layer.
+To facilitate this, Contiki-NG is built with the following Makefile variables set:
+
+\begin{itemize}
+\item MAKE_MAC=MAKE_MAC_TSCH
+\item MAKE_NET=MAKE_NET_NULLNET
+\item MAKE_ROUTING=MAKE_ROUTING_NULLROUTING
+\end{itemize}
+
+MAKE_MAC_TSCH tells the Make system to build the TSCH MAC layer, MAKE_NET_NULLNET essentially disables the network layer, MAKE_ROUTING_NULLROUTING does the same for routing functionality.
+
+\subsubsection{Preprocessor definitions}
+
+The following values are defined in the preprocessor (some through Makefile, others through header definitions) in order to configure the behavior we want. Each parameter is briefly explained below.
+
+\label{section:preprocessdef}
+\begin{itemize}
+\item $ENERGEST_CONF_ON=1$: Enable the energest package to allow analysis of power use. 
+\item $TSCH_SCHEDULE_CONF_WITH_6TISCH_MINIMAL=0$: Disable creation of a default TSCH schedule. Instead we create our own, as described in section \ref{section:tschschedule}.
+\item $LLSEC802154_CONF_ENABLED=0$: Disable Link Layer security.
+\item $TSCH_CONF_JOIN_SECURED_ONLY=0$: Allow TSCH to join unsecured networks.
+\item $TSCH_CONF_AUTOSTART=0$: Allow the program to start TSCH manually (using the NETSTACK_MAC.on() function), rather than starting it immediately when the node powers on.
+\end{itemize}
+
+\subsection{Experiments}
+
+Over the course of a minute, 60 packets are sent from the leaf node to the coordinator (root) node in each configuration.
+The configuration parameters being varied are the transmit power and the distance between the nodes, as discussed previously.
+
+The configurations are kept as close to identical as possible between various experimentation runs.
+The node positions at each distance were marked, to ensure they were positioned as reliably as possible.
+Between experiments where the tx power is changed, the tx power setting is the change in the code.
+
+A total of 12 runs were done - 3 different TX power values, tested at 4 different distances.
 
@@
 
-\subsubsection{1 meter separation}
-\label{section:1metersep}
-First, we'll compare the latencies.
-At 1 meter seperation, we found, on average, 9.29 timeslots delay between the enqueueing of the packet on the sender's side and the arrival on the receiver's side \ref{fig:latencies1m}.
-Presumably, a majority of this time is spent in the queue (or in re-transmissions), but this will be verified later \ref{section:futurework}.
-Over the distance of 1 meter, there is 100\% packet arrival rate.
+\begin{figure}[]
+	\centering
+	\includegraphics[width=\textwidth,keepaspectratio]{average_latencies.png}
+	\caption{The average packet latencies for each distance/power combination}
+	\label{fig:averagelatencies}
+\end{figure}
+\begin{figure}[]
+	\centering
+	\includegraphics[width=\textwidth,keepaspectratio]{transmission_reliability.png}
+	\caption{Overview of amount of transmission attempts are made on average to send a single packet}
+	\label{fig:txattempts}
+\end{figure}
 
-Regarding power use, then, we see that the leaf node consumes more power than the root node does.
-This is shown in \ref{fig:powerState1m}, combined with the current draw for each power state as described in \ref{tab:CurrentConsumption}.
-Overall, we find that the leaf node has used approximately 4.35 joules of energy whereas that value is only 2.58 joules for the root node.
-Since each packet carried a data payload of 52 bytes, we find the following power requirements: roughly 89 $\frac{mJ}{kbit}$ for the leaf node and  53 $\frac{mJ}{kbit}$ for the root node.
+In our current test scenario, there is no meaningful difference between the various power levels when it comes to transmission reliability.
+The amount of transmission attempts that must be made per packet are essentially identical (and almost equal to 1) for all tested scenario's.
 
-%\begin{figure}[]
-%	\centering
-%	\includegraphics[width=.5\textwidth,keepaspectratio]{1m_latencies.png}
-%	\caption{Latencies for packets sent between two nodes at 1 meter seperation.}
-%	\label{fig:latencies1m}
-%\end{figure}
-%\begin{figure}[]
-%	\centering
-%	\includegraphics[width=.5\textwidth,keepaspectratio]{5m_latencies.png}
-%	\caption{Latencies for packets sent between two nodes at 5 meter seperation.}
-%	\label{fig:latencies5m}
-%\end{figure}
+Another observation we can make, which is influenced by the transmission reliability, is the packet latency.
+In figure \ref{fig:averagelatencies}, the latencies are shown, averaged over the experiment run, per tested scenario.
 
-\subsubsection{5 meters separation}
+The latencies shown in figure \ref{fig:averagelatencies} are grouped very closely together, just over 80 milliseconds.
+Since the default TSCH slot length is 10 milliseconds, and the slot frame has 7 slots, it takes just over the duration of a slotframe for a packet to go from being queued in the leaf node to arriving at the root (give or take clock drift since the last TSCH time synchronization).
+This seems a little high, given the limited amount of traffic being generated.
 
-When we increase the distance to 5 meters, not much changes.
-As the distance is still very small (and should be easily within range), this is to be expected.
-The packet delivery ratio is still at 100\%, latency is slightly increased to rougly 9.33 slots (but this could be within margin of error -  we should look at retransmission rates to verify \ref{section:futurework}).
+\begin{figure}[]
+	\centering
+	\includegraphics[width=\textwidth,keepaspectratio]{powerstates_10m.png}
+	\caption{The power states for the nodes when 10 meters apart}
+	\label{fig:power10m}
+\end{figure}
+\begin{figure}[]
+	\centering
+	\includegraphics[width=\textwidth,keepaspectratio]{powerstates_1m.png}
+	\caption{The power states for the nodes when 1 meter apart}
+	\label{fig:power1m}
+\end{figure}
 
-The energy consumption is essentially the same, they are definitely within margin of error for our current test setup and so will not be discussed further than they have been in \ref{section:1metersep}.
+The power results, as the latency and delivery results, are incredibly similar. This is trivially clear when comparing figures \ref{fig:power1m} and \ref{fig:power10m} - they are nearly identical.
+
+Using the results from profiling the device (as in \ref{tab:CurrentConsumption}), and the Energest results we've obtained, we can compute the amount of power that is needed for each device.
+The leaf, overall, used approximately 3.4 J.
+The root used approximately 4.1 J.
+
+With a total data size of 360 kilobits (12 tests * 60 packets * 64 bytes per packet * 8 bits per byte / 1024 bits per kilobit), that corresponds to roughly 9.6 \frac{mJ}{kbit} for the leaf and 11.5 \frac{mJ}{kbit} for the root.
+
+\subsection{Conclusion}
+
+The tests we ran do not offer a clear insight to the performance of TSCH in various scenarios.
+The different scenarios appear too close together to distinguish meaningful differences.
+Due to the inherent noisiness of the wireless medium, the tests should be expanded to be able to clearly spot a pattern.
+The duration should be extended and the difference between the values under test should increase.
+This way, if there is a pattern, it is less likely that a difference in noise in the medium will cause the test results to be essentially indistinguishable.
+
+\section{Future Work}
+
+\subsubsection{varied packet size}
+In this study, we've only looked at the performance characteristics of the network at various distances for packets carrying 64 bytes of data payload.
+An interesting follow-up might be the analysis of how the results change when the packet size is varied as well.
+A sensor network doing less complex measurements could definitely get by with smaller packets, for example, which presumably makes transmitting and receiving them simpler (does allowing lower TX power for the same delivery performance).
+
+\subsubsection{individually varied TX power}
+We've only considered the case where TX power is varied on both nodes.
+A potentially interesting follow-up to this is to consider the impact varying the parameter on one of the nodes has.
+This would clarify if, in order to ensure satisfactory network performance, TX power must be increased for all nodes or only for some.
+Our results have shown that larger TX power results in fewer retransmission (at the cost of increased power use per transmission), but we've not studied the trade-off in more detail.
 
@@
 %	ROOT: 6.346295154672475 J/kbit
-
-\section{Future Work}
-
-\label{section:futurework}
-\begin{itemize}
-\item Analyze the TSCH joining process
-\item Perform the experiments as required for \ref{section:task3}
-\item Further discuss the current results in \ref{section:task3}
-\item Further analyze the found flaws in \ref{section:task3}
-\end{itemize}
 

### 2020-12-11 examples/task3/conf_my_app.h

@@ -16,31 +16,9 @@
 // Definitions taken from examples/6tisch/simple-node/project-conf.h
 /* IEEE802.15.4 PANID */
 #define IEEE802154_CONF_PANID 0xabcd
-/* Do not start TSCH at init, wait for NETSTACK_MAC.on() */
-#define TSCH_CONF_AUTOSTART 0
-/* 6TiSCH minimal schedule length.
- * Larger values result in less frequent active slots: reduces capacity and saves energy. */
-#define TSCH_SCHEDULE_CONF_DEFAULT_LENGTH 3
-// Do we need this? Also in 6tisch implementation thing, so moving it over just in case.
-/* USB serial takes space, free more space elsewhere */
-#define SICSLOWPAN_CONF_FRAG 0
-#define UIP_CONF_BUFFER_SIZE 160
-
-//Definitions taken from examples/6tisch/custom-schedule/project-conf.h
-/* Disable the 6TiSCH minimal schedule */
-// Now passed through Makefile to make it be the same throughout
-//#define TSCH_SCHEDULE_CONF_WITH_6TISCH_MINIMAL 0
-/* Size of the application-specific schedule; a number relatively prime to the hopseq length */
-#define APP_SLOTFRAME_SIZE 17
-
-
-// Definitions taken from examples/nullnet/nullnet-unicast.c
-// Send interval modified to 1 second, as per assignment.
 
 /* Put all cells on the same slotframe */
 #define APP_SLOTFRAME_HANDLE 1
-/* Put all unicast cells on the same timeslot (for demonstration purposes only) */
-#define APP_UNICAST_TIMESLOT 1
 
 // See https://github.com/contiki-ng/contiki-ng/wiki/Documentation:-TSCH-and-6TiSCH for relevant docs
 // Has configuration macros etc

### 2020-12-11 examples/task3/my_app.c

@@ -42,6 +42,7 @@
 #include "contiki.h"
 #include "net/netstack.h"
 #include "net/nullnet/nullnet.h"
+#include "os/net/routing/routing.h"
 #include <string.h>
 #include <stdio.h> /* For printf() */
 #include <stdlib.h> // malloc
@@ -65,11 +66,21 @@
 // Define the runtime, coordinator will run longer to allow attachment etc.
 // We start counting non-coord runtime from when attachment occurs.
 #if MYAPP_AS_COORDINATOR == 1
-#define RUNTIME CLOCK_SECOND * 120
+#define RUNTIME CLOCK_SECOND * 60
 static bool hasReceived = false;
 #elif MYAPP_AS_COORDINATOR == 0
 #define RUNTIME CLOCK_SECOND * 60
 #endif
+
+#if MYAPP_AS_COORDINATOR == 1
+#define SUFFIX "_coordinator"
+#else
+#define SUFFIX "_leaf"
+#endif
+
+// Vary between 0xFF, 0x00 and the default value (TBD)
+#define APP_TX_POWER 0xFF
+
 
 #define MYFILENAME "MYAPP_UNIVANTW_OUTPUTFILE"
 #define FILE_WRITE_ERROR "Error - output too long, probably. Possibly some other issue."
@@ -80,7 +91,8 @@ static struct etimer runtime_timer;
 // #if MAC_CONF_WITH_TSCH
 #if MYAPP_AS_COORDINATOR == 0
 static linkaddr_t coordinator_addr =  {{ 0x00,0x12,0x4b,0x00,0x19,0x32,0xe2,0x61 }};
-//static linkaddr_t sender_addr = {{ 0x00,0x12,0x4b,0x00,0x19,0x32,0xe4,0x89 }};
+#else
+static linkaddr_t sender_addr = {{ 0x00,0x12,0x4b,0x00,0x19,0x32,0xe4,0x89 }};
 #endif
 // #endif /* MAC_CONF_WITH_TSCH */
 static int filehandle = -1;
@@ -109,18 +121,18 @@ void input_callback(const void *data, uint16_t len,
 			hasReceived = true;
 			energest_init();
 			LOG_INFO("Received first packet - assuming network convergence, now resetting power info.\n");
-			struct tsch_slotframe* sf = tsch_schedule_get_slotframe_by_handle(0);
-			if (sf == 0) {
-				LOG_ERR("No tsch_slotframe with handle 0, this should be impossible.");
-			}
[…]

### 2020-12-11 examples/task3/plotting/data/data_10_1.py

@@ -1,0 +1,17 @@
+rxTimes = [5715, 5840, 5966, 6101, 6226, 6352, 6477, 6612, 6737, 6863, 6997, 7123, 7248, 7375, 7509, 7635, 7760, 7895, 8028, 8145, 8271, 8406, 8531, 8657, 8791, 8918, 9041, 9168, 9303, 9428, 9554, 9689, 9814, 9938, 10065, 10199, 10325, 10450, 10585, 10710, 10836, 10962, 11096, 11222, 11347, 11482, 11608, 11732, 11858, 11993, 12119, 12243, 12379, 12504, 12629, 12756, 12890, 13015, 13150, 13276]
+cpu_time_coordinator = 32173
+cpu_sleep_time_coordinator = 176498
+cpu_deepsleep_time_coordinator = 1772385
+radio_rx_time_coordinator = 2221
+radio_tx_time_coordinator = 141647
+slotTime = 10000
+slotTicks = 328
+ticksPerSecond = 128
+numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1]
+scheduleTimes = [5703, 5829, 5955, 6090, 6215, 6341, 6467, 6600, 6726, 6852, 6987, 7112, 7238, 7364, 7497, 7623, 7749, 7884, 8009, 8135, 8260, 8394, 8520, 8645, 8781, 8906, 9032, 9157, 9292, 9416, 9543, 9678, 9803, 9929, 10054, 10188, 10313, 10440, 10574, 10700, 10826, 10951, 11085, 11210, 11337, 11471, 11596, 11722, 11848, 11981, 12107, 12233, 12368, 12494, 12620, 12745, 12879, 13004, 13130, 13265]
+cpu_time_leaf = 94839
+cpu_sleep_time_leaf = 95483
+cpu_deepsleep_time_leaf = 1775620
+radio_rx_time_leaf = 5796
+radio_tx_time_leaf = 73326
+rtimerTicksPerSecond = 32768

### 2020-12-11 examples/task3/plotting/data/data_10_3.py

@@ -1,0 +1,17 @@
+rxTimes = [2180, 2299, 2423, 2558, 2683, 2809, 2935, 3069, 3196, 3320, 3455, 3580, 3706, 3831, 3966, 4092, 4217, 4351, 4477, 4603, 4728, 4862, 4988, 5115, 5249, 5374, 5501, 5625, 5760, 5885, 6011, 6145, 6271, 6397, 6522, 6657, 6782, 6908, 7043, 7168, 7293, 7419, 7553, 7680, 7805, 7939, 8065, 8190, 8316, 8450, 8576, 8701, 8835, 8962, 9087, 9213, 9347, 9474, 9598, 9733]
+cpu_time_coordinator = 32815
+cpu_sleep_time_coordinator = 177060
+cpu_deepsleep_time_coordinator = 1785781
+radio_rx_time_coordinator = 2320
+radio_tx_time_coordinator = 142636
+slotTime = 10000
+slotTicks = 328
+ticksPerSecond = 128
+numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
+scheduleTimes = [2160, 2286, 2413, 2546, 2673, 2798, 2925, 3059, 3184, 3310, 3443, 3570, 3695, 3821, 3956, 4081, 4207, 4340, 4467, 4592, 4718, 4852, 4978, 5103, 5237, 5364, 5490, 5616, 5749, 5875, 6000, 6134, 6260, 6386, 6513, 6646, 6772, 6897, 7031, 7157, 7283, 7409, 7544, 7667, 7794, 7928, 8054, 8180, 8306, 8440, 8564, 8691, 8824, 8951, 9077, 9203, 9337, 9462, 9588, 9721]
+cpu_time_leaf = 94125
+cpu_sleep_time_leaf = 95249
+cpu_deepsleep_time_leaf = 1776568
+radio_rx_time_leaf = 5980
+radio_tx_time_leaf = 73459
+rtimerTicksPerSecond = 32768

### 2020-12-11 examples/task3/plotting/data/data_10_7.py

@@ -1,0 +1,17 @@
+rxTimes = [27078, 27204, 27330, 27455, 27590, 27715, 27840, 27975, 28093, 28235, 28353, 28487, 28613, 28738, 28872, 28998, 29123, 29249, 29383, 29510, 29634, 29777, 29896, 30029, 30147, 30280, 30407, 30530, 30666, 30792, 30917, 31044, 31177, 31303, 31427, 31563, 31688, 31814, 31940, 32074, 32200, 32324, 32460, 32585, 32711, 32835, 32971, 33097, 33222, 33357, 33482, 33608, 33733, 33868, 33993, 34119, 34253, 34379, 34506, 34631]
+cpu_time_coordinator = 32571
+cpu_sleep_time_coordinator = 176629
+cpu_deepsleep_time_coordinator = 1781201
+radio_rx_time_coordinator = 2287
+radio_tx_time_coordinator = 142435
+slotTime = 10000
+slotTicks = 328
+ticksPerSecond = 128
+numtx = [1, 1, 2, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 2, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
+scheduleTimes = [27066, 27192, 27318, 27445, 27579, 27704, 27830, 27964, 28089, 28216, 28341, 28476, 28602, 28728, 28861, 28986, 29113, 29238, 29373, 29498, 29624, 29758, 29883, 30010, 30135, 30270, 30395, 30521, 30654, 30780, 30907, 31032, 31167, 31291, 31418, 31551, 31677, 31802, 31929, 32064, 32189, 32315, 32448, 32575, 32700, 32827, 32960, 33086, 33211, 33345, 33472, 33597, 33723, 33856, 33983, 34108, 34243, 34368, 34494, 34620]
+cpu_time_leaf = 95366
+cpu_sleep_time_leaf = 95188
+cpu_deepsleep_time_leaf = 1775754
+radio_rx_time_leaf = 6164
+radio_tx_time_leaf = 73732
+rtimerTicksPerSecond = 32768

### 2020-12-11 examples/task3/plotting/data/data_1_1.py

@@ -1,0 +1,17 @@
+slotTime = 10000
+slotTicks = 328
+ticksPerSecond = 128
+numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
+scheduleTimes = [3815, 3937, 4072, 4197, 4322, 4457, 4582, 4708, 4834, 4969, 5093, 5219, 5355, 5479, 5606, 5732, 5865, 5990, 6117, 6250, 6376, 6503, 6629, 6763, 6887, 7014, 7148, 7273, 7398, 7526, 7659, 7784, 7910, 8044, 8171, 8295, 8422, 8555, 8681, 8808, 8941, 9067, 9192, 9319, 9453, 9578, 9704, 9838, 9963, 10089, 10216, 10350, 10475, 10600, 10736, 10860, 10987, 11112, 11247, 11372]
+cpu_time_leaf = 102404
+cpu_sleep_time_leaf = 101753
+cpu_deepsleep_time_leaf = 1760840
+radio_rx_time_leaf = 5612
+radio_tx_time_leaf = 73188
+rtimerTicksPerSecond = 32768
+rxTimes = [3831, 3949, 4083, 4208, 4334, 4468, 4595, 4719, 4845, 4979, 5105, 5231, 5365, 5491, 5616, 5742, 5876, 6002, 6127, 6262, 6389, 6513, 6639, 6773, 6899, 7024, 7159, 7285, 7410, 7536, 7670, 7796, 7921, 8046, 8181, 8307, 8432, 8567, 8693, 8818, 8953, 9078, 9204, 9329, 9464, 9589, 9715, 9849, 9975, 10101, 10227, 10361, 10486, 10612, 10747, 10872, 10997, 11123, 11258, 11383]
+cpu_time_coordinator = 32414
+cpu_sleep_time_coordinator = 176347
+cpu_deepsleep_time_coordinator = 1776825
+radio_rx_time_coordinator = 2188
+radio_tx_time_coordinator = 141754

### 2020-12-11 examples/task3/plotting/data/data_1_3.py

@@ -1,0 +1,17 @@
+slotTime = 10000
+slotTicks = 328
+ticksPerSecond = 128
+numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
+scheduleTimes = [28520, 28646, 28772, 28907, 29031, 29158, 29282, 29417, 29543, 29669, 29802, 29928, 30055, 30179, 30314, 30440, 30566, 30700, 30825, 30951, 31076, 31210, 31337, 31463, 31597, 31722, 31848, 31974, 32107, 32234, 32359, 32494, 32619, 32745, 32870, 33004, 33131, 33256, 33391, 33515, 33642, 33767, 33901, 34028, 34153, 34288, 34412, 34538, 34663, 34798, 34925, 35050, 35184, 35309, 35436, 35560, 35695, 35821, 35947, 36082]
+cpu_time_leaf = 94837
+cpu_sleep_time_leaf = 94819
+cpu_deepsleep_time_leaf = 1776285
+radio_rx_time_leaf = 5703
+radio_tx_time_leaf = 73332
+rtimerTicksPerSecond = 32768
+rxTimes = [28531, 28657, 28783, 28917, 29043, 29168, 29294, 29428, 29554, 29679, 29814, 29939, 30066, 30191, 30325, 30450, 30575, 30711, 30836, 30962, 31096, 31223, 31348, 31473, 31608, 31733, 31860, 31985, 32119, 32244, 32370, 32505, 32630, 32755, 32881, 33016, 33141, 33268, 33401, 33528, 33653, 33778, 33913, 34038, 34164, 34298, 34433, 34549, 34676, 34810, 34935, 35061, 35194, 35321, 35446, 35572, 35706, 35832, 35958, 36092]
+cpu_time_coordinator = 32835
+cpu_sleep_time_coordinator = 175609
+cpu_deepsleep_time_coordinator = 1781958
+radio_rx_time_coordinator = 2188
+radio_tx_time_coordinator = 142022

### 2020-12-11 examples/task3/plotting/data/data_1_7.py

@@ -1,0 +1,17 @@
+slotTime = 10000
+slotTicks = 328
+ticksPerSecond = 128
+numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
+scheduleTimes = [7036, 7166, 7292, 7416, 7552, 7677, 7803, 7930, 8062, 8189, 8313, 8448, 8574, 8701, 8826, 8959, 9086, 9210, 9346, 9471, 9597, 9723, 9856, 9982, 10107, 10242, 10368, 10494, 10620, 10753, 10879, 11004, 11138, 11265, 11391, 11517, 11650, 11776, 11901, 12035, 12162, 12287, 12414, 12548, 12672, 12798, 12932, 13059, 13184, 13311, 13443, 13570, 13694, 13829, 13956, 14082, 14208, 14340, 14467, 14591]
+cpu_time_leaf = 94603
+cpu_sleep_time_leaf = 95378
+cpu_deepsleep_time_leaf = 1776654
+radio_rx_time_leaf = 5704
+radio_tx_time_leaf = 73209
+rtimerTicksPerSecond = 32768
+rxTimes = [7051, 7177, 7302, 7427, 7562, 7689, 7813, 7939, 8074, 8199, 8325, 8459, 8585, 8710, 8836, 8971, 9096, 9221, 9356, 9482, 9607, 9733, 9867, 9993, 10119, 10253, 10379, 10504, 10630, 10764, 10890, 11015, 11150, 11276, 11401, 11528, 11661, 11787, 11912, 12047, 12172, 12298, 12424, 12558, 12684, 12818, 12944, 13069, 13195, 13320, 13455, 13580, 13706, 13841, 13966, 14092, 14217, 14353, 14477, 14603]
+cpu_time_coordinator = 32079
+cpu_sleep_time_coordinator = 175604
+cpu_deepsleep_time_coordinator = 1773408
+radio_rx_time_coordinator = 2188
+radio_tx_time_coordinator = 141028

### 2020-12-11 examples/task3/plotting/data/data_3_1.py

@@ -1,0 +1,17 @@
+slotTime = 10000
+slotTicks = 328
+ticksPerSecond = 128
+numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
+scheduleTimes = [3495, 3623, 3748, 3876, 4009, 4135, 4260, 4394, 4520, 4645, 4773, 4906, 5032, 5157, 5291, 5417, 5542, 5669, 5803, 5929, 6054, 6188, 6314, 6439, 6566, 6700, 6824, 6951, 7085, 7212, 7336, 7463, 7597, 7722, 7848, 7981, 8108, 8233, 8360, 8494, 8618, 8745, 8879, 9005, 9129, 9257, 9391, 9515, 9642, 9775, 9902, 10026, 10154, 10287, 10412, 10537, 10672, 10799, 10924, 11051]
+cpu_time_leaf = 94703
+cpu_sleep_time_leaf = 95046
+cpu_deepsleep_time_leaf = 1776557
+radio_rx_time_leaf = 5703
+radio_tx_time_leaf = 73412
+rtimerTicksPerSecond = 32768
+rxTimes = [3518, 3634, 3760, 3886, 4020, 4145, 4271, 4405, 4531, 4657, 4782, 4917, 5042, 5169, 5302, 5428, 5553, 5679, 5814, 5940, 6066, 6199, 6325, 6450, 6576, 6710, 6836, 6962, 7096, 7223, 7347, 7473, 7607, 7734, 7859, 7993, 8119, 8244, 8370, 8505, 8631, 8756, 8890, 9016, 9141, 9267, 9401, 9528, 9652, 9787, 9912, 10038, 10163, 10298, 10424, 10549, 10684, 10801, 10935, 11060]
+cpu_time_coordinator = 32118
+cpu_sleep_time_coordinator = 178091
+cpu_deepsleep_time_coordinator = 1786834
+radio_rx_time_coordinator = 2188
+radio_tx_time_coordinator = 142753

### 2020-12-11 examples/task3/plotting/data/data_5_3.py

@@ -1,0 +1,17 @@
+rxTimes = [9302, 9428, 9554, 9680, 9814, 9940, 10065, 10191, 10325, 10450, 10576, 10710, 10836, 10962, 11087, 11222, 11347, 11474, 11607, 11733, 11858, 11984, 12119, 12244, 12370, 12504, 12630, 12756, 12881, 13015, 13141, 13267, 13401, 13527, 13652, 13779, 13912, 14039, 14163, 14298, 14424, 14548, 14675, 14809, 14935, 15060, 15195, 15321, 15446, 15572, 15706, 15833, 15957, 16092, 16217, 16343, 16468, 16603, 16729, 16854]
+cpu_time_coordinator = 32837
+cpu_sleep_time_coordinator = 177119
+cpu_deepsleep_time_coordinator = 1787330
+radio_rx_time_coordinator = 2188
+radio_tx_time_coordinator = 142713
+slotTime = 10000
+slotTicks = 328
+ticksPerSecond = 128
+numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
+scheduleTimes = [9288, 9416, 9543, 9669, 9802, 9929, 10053, 10181, 10313, 10440, 10565, 10699, 10825, 10951, 11078, 11211, 11337, 11462, 11596, 11722, 11847, 11974, 12107, 12234, 12359, 12493, 12619, 12744, 12871, 13005, 13130, 13256, 13390, 13516, 13641, 13768, 13901, 14027, 14153, 14286, 14413, 14539, 14665, 14798, 14924, 15050, 15183, 15310, 15434, 15562, 15695, 15821, 15947, 16080, 16207, 16331, 16459, 16591, 16718, 16844]
+cpu_time_leaf = 94181
+cpu_sleep_time_leaf = 95211
+cpu_deepsleep_time_leaf = 1777243
+radio_rx_time_leaf = 5612
+radio_tx_time_leaf = 73334
+rtimerTicksPerSecond = 32768

### 2020-12-11 examples/task3/plotting/data/data_5_7.py

@@ -1,0 +1,17 @@
+rxTimes = [14791, 14917, 15042, 15177, 15303, 15429, 15554, 15688, 15814, 15939, 16074, 16199, 16325, 16451, 16585, 16711, 16836, 16971, 17096, 17222, 17347, 17482, 17607, 17733, 17868, 17993, 18120, 18244, 18388, 18505, 18630, 18764, 18890, 19016, 19141, 19276, 19401, 19527, 19661, 19788, 19913, 20038, 20173, 20299, 20424, 20558, 20684, 20809, 20935, 21070, 21194, 21321, 21455, 21581, 21707, 21832, 21966, 22092, 22217, 22353]
+cpu_time_coordinator = 32420
+cpu_sleep_time_coordinator = 177551
+cpu_deepsleep_time_coordinator = 1791902
+radio_rx_time_coordinator = 2188
+radio_tx_time_coordinator = 143062
+slotTime = 10000
+slotTicks = 328
+ticksPerSecond = 128
+numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
+scheduleTimes = [14780, 14905, 15031, 15165, 15292, 15417, 15544, 15677, 15803, 15928, 16062, 16189, 16314, 16441, 16573, 16700, 16825, 16959, 17086, 17211, 17338, 17470, 17597, 17721, 17856, 17983, 18109, 18235, 18367, 18493, 18618, 18753, 18879, 19005, 19132, 19264, 19391, 19515, 19650, 19776, 19902, 20028, 20161, 20288, 20412, 20547, 20673, 20799, 20925, 21058, 21183, 21309, 21444, 21570, 21696, 21822, 21955, 22081, 22206, 22340]
+cpu_time_leaf = 95097
+cpu_sleep_time_leaf = 94994
+cpu_deepsleep_time_leaf = 1776649
+radio_rx_time_leaf = 5704
+radio_tx_time_leaf = 73197
+rtimerTicksPerSecond = 32768

### 2020-12-11 examples/task3/plotting/old/plot.py

@@ -1,0 +1,102 @@
+from matplotlib.pyplot import *
+import re
+
+if __name__ == "__main__":
+	startMarker = "[INFO: MyApp     ] Received first packet - assuming network convergence, now resetting power info."
+	packetMarker = "[INFO: MyApp     ] <--- Received"
+	filenames = ['out0.txt', 'out1.txt']
+	powerOrder = ['CPU', 'LPM', 'DEEPLPM','TX','RX','CPU', 'LPM', 'Deep','Tx','Rx','Total']
+	output_suffix = "0"
+	for filename in filenames:
+		index = None	
+		packetsArrived = []
+		powerOnTime = {}
+		latencies = []
+		with open(filename, 'r') as f:
+			started = False
+			nextPacket = True
+			currentRegex = 0
+			allLines = f.readlines()
+			for lineIndex in range(len(allLines)):
+				line = allLines[lineIndex][:-1] # Take line, cut off the new line at the end
+				if not started:
+					# Skip all lines preceding the first-packet-received
+					# As this marks the start of our network setup.
+					if line[:len(startMarker)] == startMarker:
+						started = True
+					continue
+				if nextPacket:
+					if line[:len(packetMarker)] == packetMarker:
+						nextPacket = False
+						index = -1
+						result = re.match(re.escape(packetMarker) + "\s(\d+)", line)
+						if (int(result[1]) > 120):
+							break
+						packetsArrived.append(int(result[1]))
+						# \w's in the below expression are slightly more lenient than we'd like (should be hexadecimal only), but close enough
+						result = re.match(re.escape(packetMarker) + "\s\d+\sfrom\s\w+\.\w+\.\w+\.\w+\sat\stime\s\d+,\ssent\sat\stime\s\d+\s\(latency\sis\s(\d+)", line)
+						latencies.append(int(result[1]))
+					continue
+
+				# From here is a repeating pattern, we can select pretty simply: 
+				if index == -1:
+					# Skip one intermediate line
+					index = 0
+					continue
+				result=re.search(powerOrder[index] + ":\s*(\d+)\sticks", line)
+
+
+				powerOnTime[powerOrder[index] + ("SEND" if index <= 4 else "RECV")] = int(result[1])
+				index += 1
+				if index == 11:
[…]

### 2020-12-11 examples/task3/plotting/plot.py

@@ -1,102 +1,138 @@
+import data.data_1_1 as d11
+import data.data_1_3 as d13
+import data.data_1_7 as d17
+import data.data_3_1 as d31
+import data.data_3_3 as d33
+import data.data_3_7 as d37
+import data.data_5_1 as d51
+import data.data_5_3 as d53
+import data.data_5_7 as d57
+import data.data_10_1 as d91
+import data.data_10_3 as d93
+import data.data_10_7 as d97
+
+
+
+dataSets = [d11, d13, d17, d31, d33, d37, d51, d53, d57, d91, d93, d97]
+dataSets1m = [d11, d13, d17]
+dataSets3m = [d31, d33, d37]
+dataSets5m = [d51, d53, d57]
+dataSets10m = [d91, d93, d97]
+dataSets1p = [d11, d31, d51, d91]
+dataSets3p = [d13, d33, d53, d93]
+dataSets7p = [d17, d37, d57, d97]
+
+powerSets = [dataSets1p, dataSets3p, dataSets7p]
+distanceSets = [dataSets1m, dataSets3m, dataSets5m, dataSets10m]
+distances = ["1m", "3m", "5m", "10m"]
+powers = ["-1dBm", "3dBm", "7dBm"]
+distancePowers=['1m, -1dBm', '1m, 3dBm', '1m, 7dBm', '3m, -1dBm', '3m, 3dBm', '3m, 7dBm', '5m, -1dBm', '5m, 3dBm', '5m, 7dBm', '10m, -1dBm', '10m, 3dBm', '10m, 7dBm']
+powerColors = ['ro-', 'go-', 'bo-']
+distanceColors = ['ro-', 'go-', 'bo-', 'mo-']
 from matplotlib.pyplot import *
-import re
-
-if __name__ == "__main__":
-	startMarker = "[INFO: MyApp     ] Received first packet - assuming network convergence, now resetting power info."
-	packetMarker = "[INFO: MyApp     ] <--- Received"
-	filenames = ['out0.txt', 'out1.txt']
-	powerOrder = ['CPU', 'LPM', 'DEEPLPM','TX','RX','CPU', 'LPM', 'Deep','Tx','Rx','Total']
-	output_suffix = "0"
-	for filename in filenames:
-		index = None	
-		packetsArrived = []
-		powerOnTime = {}
-		latencies = []
-		with open(filename, 'r') as f:
-			started = False
-			nextPacket = True
-			currentRegex = 0
[…]

### 2020-12-11 examples/task3/poc.c

@@ -1,0 +1,43 @@
+#include "contiki.h"
+#include "os/storage/cfs/cfs-coffee.h"
+#include "sys/log.h"
+#define LOG_MODULE "MyApp"
+#define LOG_LEVEL LOG_LEVEL_INFO
+
+PROCESS(poc, "Proof of concept");
+
+PROCESS_THREAD(poc, ev, data)
+{
+  static int filehandle = 0;
+  PROCESS_BEGIN();
+  filehandle = cfs_open("MYTESTFILEPIETERHENDRIKS", CFS_READ | CFS_WRITE);
+  char buffer[1024];
+  int ret;
+  ret = cfs_read(filehandle, buffer, 1024);
+  if (ret != 0 && ret != -1) 
+  {
+    cfs_close(filehandle);
+    cfs_remove("MYTESTFILEPIETERHENDRIKS");
+    filehandle = cfs_open("MYTESTFILEPIETERHENDRIKS", CFS_READ | CFS_WRITE);
+  }
+  if (ret != -1) 
+  {
+    buffer[ret] = '\0';
+    LOG_INFO("Ret = %i\n", ret);
+    LOG_INFO("Read string: %s\n", buffer);
+
+    for (int i = 0; i < 15; ++i) 
+    {
+      buffer[i] = 'a';
+    }
+
+    ret = cfs_write(filehandle, buffer, 15);
+    LOG_INFO("WRet = %i\n", ret);
+
+    cfs_close(filehandle);
+
+  }
+  
+  PROCESS_END();
+}
+AUTOSTART_PROCESSES(&poc);

### 2020-12-11 Paper/Paper.tex
Minor fixes to paper tex

@@
 	\label{fig:6tischStack}
-\end{figure}
+\end{figure}}
 
@@
 \begin{itemize}
-\item MAKE_MAC=MAKE_MAC_TSCH
-\item MAKE_NET=MAKE_NET_NULLNET
-\item MAKE_ROUTING=MAKE_ROUTING_NULLROUTING
+\item MAKE\_MAC=MAKE\_MAC\_TSCH
+\item MAKE\_NET=MAKE\_NET\_NULLNET
+\item MAKE\_ROUTING=MAKE\_ROUTING\_NULLROUTING
 \end{itemize}
 
-MAKE_MAC_TSCH tells the Make system to build the TSCH MAC layer, MAKE_NET_NULLNET essentially disables the network layer, MAKE_ROUTING_NULLROUTING does the same for routing functionality.
+MAKE\_MAC\_TSCH tells the Make system to build the TSCH MAC layer, MAKE\_NET\_NULLNET essentially disables the network layer, MAKE\_ROUTING\_NULLROUTING does the same for routing functionality.
 
@@
 \item $TSCH_CONF_JOIN_SECURED_ONLY=0$: Allow TSCH to join unsecured networks.
-\item $TSCH_CONF_AUTOSTART=0$: Allow the program to start TSCH manually (using the NETSTACK_MAC.on() function), rather than starting it immediately when the node powers on.
+\item $TSCH_CONF_AUTOSTART=0$: Allow the program to start TSCH manually (using the NETSTACK\_MAC.on() function), rather than starting it immediately when the node powers on.
 \end{itemize}
@@
 
-With a total data size of 360 kilobits (12 tests * 60 packets * 64 bytes per packet * 8 bits per byte / 1024 bits per kilobit), that corresponds to roughly 9.6 \frac{mJ}{kbit} for the leaf and 11.5 \frac{mJ}{kbit} for the root.
+With a total data size of 360 kilobits (12 tests * 60 packets * 64 bytes per packet * 8 bits per byte / 1024 bits per kilobit), that corresponds to roughly $9.6 \frac{mJ}{kbit}$ for the leaf and $11.5 \frac{mJ}{kbit}$ for the root.
 
@@
 Our results have shown that larger TX power results in fewer retransmission (at the cost of increased power use per transmission), but we've not studied the trade-off in more detail.
-
-%\begin{figure}[]
-%	\centering
-%	\includegraphics[width=.5\textwidth,keepaspectratio]{1m_powerStates.png}
-%	\caption{The time a node spends in each power state at 1 meter seperation.}
-%	\label{fig:powerState1m}
-%\end{figure}
-%\begin{figure}[]
-%	\centering
-%	\includegraphics[width=.5\textwidth,keepaspectratio]{5m_powerStates.png}
-%	\caption{The time a node spends in each power state at 5 meters seperation.}
-%	\label{fig:powerState5m}
-%\end{figure}
-
-%PACKET ARRIVAL RATE: 1.0
-%AVERAGE LATENCY: 9.291666666666666
-%LEAF ENERGY CONSUMPTION: 4.347331036560059 J
-%ROOT ENERGY CONSUMPTION: 2.577431278930664 J
-%Since each packet carried a data payload of 52 bytes, that's
-%	LEAF: 10.701122551532452 J/kbit
-%	ROOT: 6.344446225060096 J/kbit
-%PACKET ARRIVAL RATE: 1.0
-%AVERAGE LATENCY: 9.333333333333334
-%LEAF ENERGY CONSUMPTION: 4.345094247253417 J
-%ROOT ENERGY CONSUMPTION: 2.578182406585693 J
-%Since each packet carried a data payload of 52 bytes, that's
-%	LEAF: 10.695616608623796 J/kbit
-%	ROOT: 6.346295154672475 J/kbit
 

### 2020-12-11 Paper/Paper.tex

--- 2020-12-11 Paper/Paper.tex
@@
 As such, its performance under different conditions must be assessed, so that accurate guidelines for its application can be drawn\cite{TSCHExperimentEval}.
-\begin{figure}[]
-	\centering
-	\includegraphics[width=.25\textwidth,keepaspectratio]{6TiSCH-Protocol-Stack.png}
-	\caption{6TiSCH Protocol Stack\cite{TimeCritical6tisch}.}
-	\label{fig:6tischStack}
-\end{figure}
+%\begin{figure}[]
+%	\centering
+%	\includegraphics[width=.25\textwidth,keepaspectratio]{6TiSCH-Protocol-Stack.png}
+%	\caption{6TiSCH Protocol Stack\cite{TimeCritical6tisch}.}
+%	\label{fig:6tischStack}
+%\end{figure}
 

### 2021-01-20 Paper/Paper.tex
Solved image problem
Last commit before second submission
Updated part of the corrections

--- 2020-12-11 Paper/Paper.tex
@@
 These boards are part of the IoT hardware family, and they allow for the creation of a network minimizing energy consumption.\\
-The paper is subdivided into three main sections: in the first one, we will compare the energy consumption of the leaf and root node (LLC) at first using up to the MAC TSCH layer, and then using the full stack.\\
-In the second section, we will analyze the TSCH joining process and relative energy consumption. Further, in the final section, we will assess the performance of the TSCH mode over various distances.
+We perform different experiments aiming to evaluate various parameters such as energy consumption or latency of the boards in a two nodes network.\\
+Different measurements are performed on the boards under different conditions such as only the MAC layer enabled compared full-stack, during the joining process, and at various distances.
+For each experiment, we report and explain how the introduced variations in the network affect the measured values.
 \end{abstract}
@@
 The IETF IPv6 over the TSCH mode of IEEE802.15.4e (6TiSCH) working group has standardized a set of protocols to enable low power industrial-grade IPv6 networks.
-6TiSCH proposes a protocol stack rooted in the Time Slotted Channel Hopping (TSCH) mode of the IEEE802.15.4-2015 standard, supports multi-hop topologies with the IPv6 Routing Protocol for Low-Power and Lossy Networks (RPL) routing protocol, and is IPv6-ready through 6LoWPAN\cite{6tischDef}.
+6TiSCH proposes a protocol stack rooted in the Time Slotted Channel Hopping (TSCH) mode of the IEEE802.15.4-2015 standard, a scheme aiming to guarantee network reliability by keeping nodes time-synchronised at the MAC layer.
+The latter is accomplished by scheduling, therefore nodes must remain time synchronised throughout the network deployment’s life-time.
+To this end, nodes periodically exchange Enhanced Beacon (EB) packets\cite{6tischDef}.
+It supports multi-hop topologies with the IPv6 Routing Protocol for Low-Power and Lossy Networks (RPL) routing protocol, and is IPv6-ready through 6LoWPAN\cite{6tischDef}.
 
@@
 The hardware in use are Zolertia RE-Mote boards, designed jointly with universities and industry partners in RERUM European project, to ease the development of private and secure applications for IoT and Smart City applications.\\
-The RE-Mote packs several onboard resources, like an RTC, external WDT, Micro-SD, RF switch, and a Shutdown mode to reduce its power consumption down to 150nA\cite{contiki-NGWiki}.
+The RE-Mote packs several onboard resources, like an accurate time keeper real time clock (RTC), external watchdog timer (WDT) to force an embedded microprocessor or microcontroller to reset in case of loop, Micro-SD, RF switch, and a Shutdown mode to reduce its power consumption down to 150nA\cite{contiki-NGWiki}.
+
+The paper is subdivided into three main sections: in the first one, we will compare the energy consumption of the leaf and root node (LLC) at first using up to the MAC TSCH layer, and then using the full stack.\\
+In the second section, we will analyze the TSCH joining process and relative energy consumption. Further, in the final section, we will assess the performance of the TSCH mode over various distances.
 
@@
 This analysis can be done by knowing different parameters like current, tension, and time.\\
-tension is always $3.3V$, current instead should be correctly provided in the board datasheet, previous works have shown that real current consumption values are different from the datasheet provided ones\cite{EnergyConsumption}, in this paper, we are going to use such current measurements to determine the energy consumption.
+tension is always fixed at $3.3V$ due to the power supply and voltage regulator on the board, current should instead be correctly provided in the board datasheet, previous works have shown that real current consumption values are different from the datasheet provided ones\cite{EnergyConsumption}.
+In this paper, we are going to use such current measurements to determine the energy consumption.
 \subsection{Throughput Analysis} In this paper, an analysis of the throughput performance of TSCH networks is made.
@@
 For both analyses, we report on the consumption of the root and the leaf node separately.\\
-Following we remark differences in energy consumption between the root and the leaf node in the two different scenarios.
-
-The Time-Slotted Channel Hopping (TSCH) mode for medium access control (MAC) included in the standard IEEE 802.15.4 has been designed as the multichannel MAC protocol for Low-power and lossy networks (LLNs), a key component of the Internet of Things (IoT).
+Following we remark differences in energy consumption between the root and the leaf node in the two different scenarios.\\
+The TSCH mode for medium access control (MAC) included in the standard IEEE 802.15.4 has been designed as the multichannel MAC protocol for Low-power and lossy networks (LLNs), a key component of the IoT.
 Its ﬂexibility makes the TSCH mode a very promising candidate for the future of the MAC layer in LLNs.
@@
 	\label{fig:6tischStack}
-\end{figure}}
+\end{figure}
 
-the physical setup of the experiment consists of two Zolertia  Remote RevB boards placed at a fixed distance of approximately 20 cm as shown in Figure \ref{fig:exp1Topology}.
+The physical setup of the experiment consists of two Zolertia  Remote RevB boards placed at a fixed distance of approximately 20 cm as shown in Figure \ref{fig:exp1Topology}.
+nothing stand between the two boards which are free to comunicate.
 \begin{figure}[H]
@@
 \end{equation}
-Where $V_{cc}$ is the supply voltage, fixed as a constant at the value $3.3V$, $I_s$ is provided by the Table \ref{tab:CurrentConsumption} column \textit{Device profiling}\cite{EnergyConsumption}, and $t$ is measured using Energest.\\
+Where $V_{cc}$ is the supply voltage, fixed as a constant at the value $3.3V$, $I_s$ is provided by the Table \ref{tab:CurrentConsumption} column \textit{Device profiling}\cite{EnergyConsumption} chosen because more accurate than the one provided by the CC2538 datasheet, and $t$ is measured using Energest.\\
 All measurements are performed in a span of 15 minutes each.
@@
 We proceeded as explained in the setup to measure the energy consumption between leaf and root node.\\
-Results are reported in Table \ref{tab:MACOnly}.
+Results, measured after network convergence are reported in Table \ref{tab:MACOnly}.
 \begin{table}[h]
@@
 \end{itemize}
-We can therefore say that, atleast for two node, the workload on the root is not enought to show a difference in energy consumption during the stated time spam.
+We can therefore say that, atleast for two node comunicating for such time, after network convergence, the workload on the root is not enought to show a difference in energy consumption during the stated time spam.
 \subsection{Full stack}
-The next experiment is as cited in the section \ref{section:task1} introduction related to the energy consumption once the full 6TiSCH stack has been enabled (except for the security layer).\\
+The next experiment is as cited in the section introduction related to the energy consumption once the full 6TiSCH stack has been enabled (except for the security layer).\\
 The setup of this experiment is the same to the previous one.
-Two boards 10cm apart from each other (\ref{fig:exp1Topology}) are running the same source code.\\
+Two boards 20cm apart from each other (\ref{fig:exp1Topology}) are running the same source code.
+
 In this scenario, we have a coordinator node and a leaf node.\\
@@
 	\caption{TSCH Schedule as used in the range analysis experiments}
-	\label{fig:6tischStack}
+	\label{fig:TSCHSchedule}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=\textwidth,keepaspectratio]{average_latencies.png}
+	\includegraphics[width=.5\textwidth,keepaspectratio]{average_latencies.png}
 	\caption{The average packet latencies for each distance/power combination}
@@
 	\centering
-	\includegraphics[width=\textwidth,keepaspectratio]{transmission_reliability.png}
+	\includegraphics[width=.5\textwidth,keepaspectratio]{transmission_reliability.png}
 	\caption{Overview of amount of transmission attempts are made on average to send a single packet}
@@
 	\centering
-	\includegraphics[width=\textwidth,keepaspectratio]{powerstates_10m.png}
+	\includegraphics[width=.5\textwidth,keepaspectratio]{powerstates_10m.png}
 	\caption{The power states for the nodes when 10 meters apart}
@@
 	\centering
-	\includegraphics[width=\textwidth,keepaspectratio]{powerstates_1m.png}
+	\includegraphics[width=.5\textwidth,keepaspectratio]{powerstates_1m.png}
 	\caption{The power states for the nodes when 1 meter apart}
@@
 Glenn Daneels, Esteban Municio, Bruno Van de Velde, Glenn Ergeerts, Maarten Weyn, Steven Latré, \& Jeroen Famaey
-
+\bibitem{TSCHDefinition}A.
+Mavromatis, G.
+Z.
+Papadopoulos, X.
+Fafoutis, A.
+Elsts, G.
+Oikonomou and T.
+Tryfonas, "Impact of Guard Time Length on IEEE 802.15.4e TSCH Energy Consumption," 2016 13th Annual IEEE International Conference on Sensing, Communication, and Networking (SECON), London, 2016, pp.
+1-3, doi: 10.1109/SAHCN.2016.7732997.
 \end{thebibliography}

### 2021-01-21 Paper/Paper.tex

@@
 That cell is configured as a transmit-only (to the coordinator) cell in the leaf node and a receive-only (from the leaf) cell in the coordinator node.
-This setup is illustrated in figure \ref{fig:tsch_schedule}.
+This setup is illustrated in figure \ref{fig:TSCHSchedule}.
 The red cell is the cell used for EBs, where the root node advertises.
@@
 The data payload size was chosen out of convenience, as each packet carries metrics from the sender and they happened to be 52 bytes in size.
-Varying this packet size will result in different performance metrics and so must be addressed \ref{section:futurework}.
+Varying this packet size will result in different performance metrics and so must be addressed, this is discussed in section \ref{section:futurework}.
 
@@
 A brief comparison is made (showing the methodology) between nodes with 1 meter seperation and nodes with 5 meters seperation.
-Further work must be done to complete this analysis \ref{section:futurework}.
+Further work must be done to complete this analysis, more informations at section \ref{section:futurework}.
 
@@
 \section{Future Work}
-
+\label{section:futurework}
 \subsubsection{varied packet size}
@@
 \begin{thebibliography}{00}
-\bibitem{contiki-NGWiki} Adam Dunkels, \url {https://github.com/contiki-ng/contiki-ng/wiki}
 \bibitem{6tischDef} X.
@@
 595-615, Firstquarter 2020, doi: 10.1109/COMST.2019.2939407.
-\bibitem{TimeCritical6tisch} Karaagac, Abdulkadir \& Haxhibeqiri, Jetmir \& Moerman, Ingrid \& Hoebeke, Jeroen.
-(2018).
-Time-critical communication in 6TiSCH networks.
-161-166.
-10.1109/WCNCW.2018.8368987.
+\bibitem{contiki-NGWiki} Adam Dunkels, \url {https://github.com/contiki-ng/contiki-ng/wiki}
 \bibitem{EnergyConsumption} Sabovic, Adnan \& Delgado, Carmen \& Bauwens, Jan \& De Poorter, Eli \& Famaey, Jeroen.
@@
 The Korea Institute of Information and Commucation Engineering.
+\bibitem{TimeCritical6tisch} Karaagac, Abdulkadir \& Haxhibeqiri, Jetmir \& Moerman, Ingrid \& Hoebeke, Jeroen.
+(2018).
+Time-critical communication in 6TiSCH networks.
+161-166.
+10.1109/WCNCW.2018.8368987.
 \bibitem{TSCHExperimentEval} García Algora, Carlos \& Alfonso Reguera, Vitalio. (2018). Experimental evaluation of IEEE 802.15.4 TSCH on a 6TiSCH network. 39. 70-78.

### 2021-01-21 Paper/Paper.tex
Work on paper, mostly task3 for now

--- 2021-01-20 Paper/Paper.tex
@@
 \usepackage{float}
-\usepackage{cite}
 \usepackage{url}
+\usepackage{biblatex}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+\newcommand{\figref}[1]{Figure~\ref{#1}} 
+\newcommand{\secref}[1]{Section~\ref{#1}}
+\newcommand{\tabref}[1]{Table~\ref{#1}}
+
+% Fix some overfull hboxes
+\setlength{\tabcolsep}{4pt}
+
+% Allow linebreaks at underscores
+\renewcommand\_{\textunderscore\allowbreak}
+
+\bibliography{Paper}
 \begin{document}
 
-\title{Sensors Lab Conference}
+\title{TSCH: A look at reliability and energy requirements}
 
@@
 \and
-% Cut out 3rd author block as Miroslav is not contributing.
 \IEEEauthorblockN{Pieter Hendriks}
@@
 \begin{IEEEkeywords}
-6TiSCH, Contiki-NG, Energest, IEEE 802.15.4, Power Consumption, Range, Time Slotted Channel Hopping, TiSCH, TSCH, Zolertia
+6TiSCH, Contiki-NG, Energest, IEEE 802.15.4, Power Consumption, Range, Time Slotted Channel Hopping, 6TiSCH, TSCH, Zolertia
 \end{IEEEkeywords}
@@
 
-This paper serves as an initial look at the performance of TSCH on the Contiki-NG operating system.
-Specifically, we look at the energy consumption by the TSCH network stack vs the 6TiSCH network stack, we analyze the TSCH joining process, and we measure the impact node separation has on the network's performance and energy characteristics.
+This paper serves as an initial look at the performance of TSCH on the Contiki-NG operating system. We study the following cases:
+\begin{itemize}
+\item Energy consumption of TSCH network stack vs 6TiSCH network stack
+\item Time taken for and energy used during node association with an established TSCH network
+\item Measure the impact of distance between nodes on energy use and network reliability
+\end{itemize}
 
@@
 \subsection{Accurate energy consumption using Energest}
-In section \ref{section:task1} of this paper, we focus on the analysis of the energy consumption between leaf and root node.
-This analysis can be done by knowing different parameters like current, tension, and time.\\
-tension is always fixed at $3.3V$ due to the power supply and voltage regulator on the board, current should instead be correctly provided in the board datasheet, previous works have shown that real current consumption values are different from the datasheet provided ones\cite{EnergyConsumption}.
+In \secref{section:task1} of this paper, we focus on the analysis of the energy consumption between leaf and root node.
+This analysis can be done by knowing different parameters like current, voltage, and time.
+Voltage is always fixed at $3.3V$ due to the power supply and voltage regulator on the board, current should instead be correctly provided in the board datasheet, previous works have shown that real current consumption values are different from the datasheet provided ones\cite{EnergyConsumption}.
 In this paper, we are going to use such current measurements to determine the energy consumption.
-\subsection{Throughput Analysis} In this paper, an analysis of the throughput performance of TSCH networks is made.
-They show which parameters of the TSCH networks (node count, hop count, ...) influence the throughput metric in what way.
-Our research focuses on different performance characteristics of the TSCH implementation and can be useful alongside these results\cite{ThroughputEvaluation}.
+\subsection{Throughput Analysis} S.
+Lee et al present an analysis of the throughput performance of TSCH networks.
+They show which parameters of the TSCH networks (node count, hop count) influence the throughput metric in what way.
+They concluded that throughput capability of the network increases as the node count increases.
+The throughput capability drops when the hop count increases.
+Our research focuses on different performance characteristics of the TSCH implementation (energy efficiency rather than throughput), while varying different variables and can be useful alongside these results\cite{ThroughputEvaluation}.
+\subsection{Join Process Performance} D.
+De Guglielmo et al analyse the time it takes for nodes to associate with an existing TSCH network.
+Their work focuses on the time taken for nodes to associate to the network and finds that the amount of channels in the hopping sequence is the most important factor\cite{JoinProcess}.
+Our research additionally considers the energy states nodes are in during the join process.
 
@@
 \label{section:task1}
-In the first analysis, we compared the energy consumption during a certain time period of the entire 6TiSCH stack to when only enabling the TSCH MAC layer (without link-layer security) after network convergence.\\
-The full stack can be seen as in Figure \ref{fig:6tischStack}.
 
-For both analyses, we report on the consumption of the root and the leaf node separately.\\
-Following we remark differences in energy consumption between the root and the leaf node in the two different scenarios.\\
+\subsection{Introduction} 
+\label{section:t1_intro}
+In the first analysis, we compared the energy consumption during a certain time period of the entire 6TiSCH stack to when only enabling the TSCH MAC layer (without link-layer security) after network convergence.
+The full stack can be seen as in \figref{fig:6tischStack}.
+
+For both analyses, we report on the consumption of the root and the leaf node separately.
+Following we remark differences in energy consumption between the root and the leaf node in the two different scenarios.
 The TSCH mode for medium access control (MAC) included in the standard IEEE 802.15.4 has been designed as the multichannel MAC protocol for Low-power and lossy networks (LLNs), a key component of the IoT.
@@
 As such, its performance under different conditions must be assessed, so that accurate guidelines for its application can be drawn\cite{TSCHExperimentEval}.
-\begin{figure}[]
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=.25\textwidth,keepaspectratio]{6TiSCH-Protocol-Stack.png}
+	\includegraphics[width=.25\textwidth,keepaspectratio]{figures/6TiSCH-Protocol-Stack.png}
 	\caption{6TiSCH Protocol Stack\cite{TimeCritical6tisch}.}
@@
 
-The physical setup of the experiment consists of two Zolertia  Remote RevB boards placed at a fixed distance of approximately 20 cm as shown in Figure \ref{fig:exp1Topology}.
-nothing stand between the two boards which are free to comunicate.
-\begin{figure}[H]
+the physical setup of the experiment consists of two Zolertia  Remote RevB boards placed at a fixed distance of approximately 20 cm as shown in \figref{fig:exp1Topology}.
+There is nothing between the boards hindering communication.
+
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=.35\textwidth,keepaspectratio]{exp1Topology.pdf}
+	\includegraphics[width=.35\textwidth,keepaspectratio]{figures/exp1Topology.pdf}
 	\caption{Network topology for 6TiSCH energy consumption analysis.}
@@
 \end{figure}
-The basic setup for the following analysis are a root (coordinator) node and a leaf node that exchange the same ammount of data packets.\\
-Both nodes are configured to measure the energy consumption by the Energest\footnote{https://github.com/contiki-ng/contiki-ng/wiki/Documentation:-Energest} module available in Contiki-ng\footnote{https://github.com/contiki-ng}.\\
+The basic setup for the following analysis is a root (coordinator) node and a leaf node that exchange the same amount of data packets.
+Both nodes are configured to measure the energy consumption by the Energest\footnote{https://github.com/contiki-ng/contiki-ng/wiki/Documentation:-Energest} module available in Contiki-ng\footnote{https://github.com/contiki-ng}.
 The Energest module can be used to implement lightweight, software-based energy estimation approach for resource-constrained IoT devices.
-By tracking the time various hardware states such as the radio is turned on, and by knowing the power consumption of the state, it is possible to estimate the energy consumption\cite{contiki-NGWiki}.\\
+By tracking the time various hardware states such as the radio is turned on, and by knowing the power consumption of the state, it is possible to estimate the energy consumption\cite{contiki-NGWiki}.
 The energy consumption is measured referring to the following formula:
@@
 \end{equation}
-Where $V_{cc}$ is the supply voltage, fixed as a constant at the value $3.3V$, $I_s$ is provided by the Table \ref{tab:CurrentConsumption} column \textit{Device profiling}\cite{EnergyConsumption} chosen because more accurate than the one provided by the CC2538 datasheet, and $t$ is measured using Energest.\\
+
+Where $V_{cc}$ is the supply voltage, fixed as a constant at the value $3.3V$, $I_s$ is provided by the Table \tabref{tab:CurrentConsumption} column \textit{Device profiling}\cite{EnergyConsumption} chosen because more accurate than the one provided by the CC2538 datasheet, and $t$ is measured using Energest.
+
 All measurements are performed in a span of 15 minutes each.
@@
 \subsection{Only TSCH MAC layer}
-In the first part of the experiment, we used only the stack till the MAC layer (TSCH) as shown in Figure \ref{fig:6tischStack}.
+In the first part of the experiment, we used only the stack till the MAC layer (TSCH) as shown in \figref{fig:6tischStack}.
 In TSCH networks, every node follows a time-synchronized schedule.
@@
 We proceeded as explained in the setup to measure the energy consumption between leaf and root node.\\
-Results, measured after network convergence are reported in Table \ref{tab:MACOnly}.
-\begin{table}[h]
+Results, measured after network convergence, are reported in \tabref{tab:MACOnly}.
+
+\begin{table}[htbp]
 	\centering
@@
 \subsection{Full stack}
-The next experiment is as cited in the section introduction related to the energy consumption once the full 6TiSCH stack has been enabled (except for the security layer).\\
+The next experiment is as cited in \secref{section:t1_intro} related to the energy consumption once the full 6TiSCH stack has been enabled (except for the security layer).\\
 The setup of this experiment is the same to the previous one.
@@
 We proceeded as explained in the setup to measure the energy consumption between leaf and root node.\\
-Results are reported in Table \ref{tab:FullStack}.
-\begin{table}[h]
+Results are reported in \tabref{tab:FullStack}.
+\begin{table}[htbp]
 	\centering
@@
 As a final comparison, we compared the total energy usage between root and leaf nodes in the two configurations.
-What we measured has been reported as Table \ref{tab:exp1Comparison}.
-\begin{table}[h]
+What we measured has been reported as \tabref{tab:exp1Comparison}.
+\begin{table}[htbp]
 	\centering
@@
 
+\section{Energy consumption during the TSCH join process}
+\label{section:task2}
 %\section{Analysing the TSCH joining process}
@@
 
-\section{Analysing range capabilities}
+\section{Impact of distance on energy consumption and network reliability}
 \label{section:task3}
+\subsection{Introduction}
+
+In this section, we look at the impact seperation between two nodes has on the energy use of the nodes and the reliability of the TSCH layer.
+We consider 4 distances and 3 TX power levels and evaluate the performance based on the device power states (recorded using Energest) and the delivery rate (recorded using necessary retransmission count on MAC layer).
 
@@
 One will act as the TSCH coordinator, the other as a leaf node.
-In all tests performed in this section, the traffic originates at the leaf node (and is sent to the coordinator).
+In all tests performed in this section, the traffic is sent from the leaf node to the root node.
 
-The nodes always remain within line of sight, at equal heights.
+The nodes always remain within line of sight, at equal heights (elevated 1 meter above the ground).
 The only physical parameter being varied (other than those outside our control) is the distance between them.
-For our range analysis, we consider four distances: 1 meter, 3 meters, 5 meters and 10 meters.
-For each of these values, the transmit power (see section \ref{section:txpower}) is varied as well - all permutations are considered.
-
-\subsubsection{Traffic characteristics}
-The traffic is uniform, 1 packet is sent per second.
-The packets contain 64 bytes of data.
-This value is chosen because it is a nice, round number that is sufficiently large for a few measurements (depending on the application), while remaining small enough to be sent over the TSCH layer without fragmentation.
+For our range analysis, we consider four distances: 1 meter, 10 meters, 50 meters and 100 meters.
+The node positions at each distance were marked, to ensure they were positioned as reliably as possible.
 
@@
 \label{section:txpower}
-The transmit power parameter controls the intensity of the signal transmission.
-A larger TX power value leads to increased energy consumption.
-The amount of extra energy consumed by varying this value is left outside the scope of this study.
-We study 3 values for this parameter, the default value (3 dBm), the maximal value (7 dBm) and a smaller value (-1 dBm).
-The TX power is kept the same between the two nodes at all times.
+
+For each distance in the experiment, we also consider the impact of the TX power parameter.
+This value sets the intensity of the signal transmission.
+A larger TX power value leads to increased energy consumption\cite{AccurateEnergyTSCH}.
+The amount of extra energy consumed by varying this value is left outside the scope of this study, because our study is limited to observing time spent in each energy state.
+The associated current draw for each energy state (used to compute final energy consumption values) is obtained through spec sheets or device profiling results (see \tabref{tab:CurrentConsumption}).
+We consider 3 distinct values for this parameter: 7 dBm, 0 dBm and -7 dBm.
+
+\subsubsection{Traffic characteristics}
+\label{section:trafficchar}
+The traffic is uniform, 1 packet is sent per second.
+The packets contain 64 bytes of data.
+The packet size was chosen because 64 bytes is sufficiently large to contain sensor measurement data while remaining small enough to be transmitted over the TSCH layer without fragmentation.
+Each experiment will send 60 packets so that we may average the performance for each parameter set over that data.
 
@@
 That cell is configured as a transmit-only (to the coordinator) cell in the leaf node and a receive-only (from the leaf) cell in the coordinator node.
-This setup is illustrated in figure \ref{fig:tsch_schedule}.
-The red cell is the cell used for EBs, where the root node advertises.
-The blue cell is used for all data transmissions from the leaf to the root.
-Contiki-NG, by default, configures TSCH with 7 slots per slotframe and 4 channels.
-We have left these parameters unchanged.
-\begin{figure}[]
+This setup is illustrated in \figref{fig:TSCHSchedule}.
+The size of the schedule is left as its default value, that is, 7 slots per frame, 4 channels.
+
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=.4\textwidth,keepaspectratio]{tsch_schedule.png}
+	\includegraphics[width=.4\textwidth,keepaspectratio]{figures/tsch_schedule.png}
 	\caption{TSCH Schedule as used in the range analysis experiments}
@@
 To facilitate this, Contiki-NG is built with the following Makefile variables set:
-
 \begin{itemize}
+{
+\small
 \item MAKE\_MAC=MAKE\_MAC\_TSCH
@@
 \item MAKE\_ROUTING=MAKE\_ROUTING\_NULLROUTING
+}
 \end{itemize}
 
-MAKE\_MAC\_TSCH tells the Make system to build the TSCH MAC layer, MAKE\_NET\_NULLNET essentially disables the network layer, MAKE\_ROUTING\_NULLROUTING does the same for routing functionality.
+MAKE\_MAC\_TSCH configures the build system to build the TSCH MAC layer.
+MAKE\_NET\_NULLNET and MAKE\_ROUTING\_NULLROUTING essentially disable their respective functionalities.
+Placeholder functions (no side-effects, always return success) are defined in Contiki-NG, but these are not used by our implementation.
 
@@
 \begin{itemize}
-\item $ENERGEST_CONF_ON=1$: Enable the energest package to allow analysis of power use. 
-\item $TSCH_SCHEDULE_CONF_WITH_6TISCH_MINIMAL=0$: Disable creation of a default TSCH schedule. Instead we create our own, as described in section \ref{section:tschschedule}.
-\item $LLSEC802154_CONF_ENABLED=0$: Disable Link Layer security.
-\item $TSCH_CONF_JOIN_SECURED_ONLY=0$: Allow TSCH to join unsecured networks.
-\item $TSCH_CONF_AUTOSTART=0$: Allow the program to start TSCH manually (using the NETSTACK\_MAC.on() function), rather than starting it immediately when the node powers on.
+{
+\small
+\item ENERGEST\_CONF\_ON=1\\ Enable the energest package to allow analysis of power use. 
+\item TSCH\_SCHEDULE\_CONF\_WITH\_6TISCH\_MINIMAL=0\\ Disable creation of a default TSCH schedule. Instead we create our own, as described in \secref{section:tschschedule}.
+\item LLSEC802154\_CONF\_ENABLED=0\\ Disable Link Layer security.
+\item TSCH\_CONF\_JOIN\_SECURED\_ONLY=0\\ Allow TSCH to join unsecured networks.
+}
 \end{itemize}
-
-\subsection{Experiments}
-
-Over the course of a minute, 60 packets are sent from the leaf node to the coordinator (root) node in each configuration.
-The configuration parameters being varied are the transmit power and the distance between the nodes, as discussed previously.
-
-The configurations are kept as close to identical as possible between various experimentation runs.
-The node positions at each distance were marked, to ensure they were positioned as reliably as possible.
-Between experiments where the tx power is changed, the tx power setting is the change in the code.
-
-A total of 12 runs were done - 3 different TX power values, tested at 4 different distances.
-
-In order to properly analyse the range capabilities, we must first define a test structure that will be repeated at each range.
-The test in this case is sending 120 packets (1 per second, 52 data bytes each) over a specified range (varying between 1 and 100 meters) so we can show the performance characteristics of TSCH as the distance between nodes varies.
-The data payload size was chosen out of convenience, as each packet carries metrics from the sender and they happened to be 52 bytes in size.
-Varying this packet size will result in different performance metrics and so must be addressed \ref{section:futurework}.
-
-Due to time constraints, combined with other obligations, the full scope of the experiments in this section has not yet been carried out.
-A brief comparison is made (showing the methodology) between nodes with 1 meter seperation and nodes with 5 meters seperation.
-Further work must be done to complete this analysis \ref{section:futurework}.
-
-As of now, though, we can show that the TSCH functionality is essentially unchanged when we're looking at 1 vs 5 meters seperation between the two nodes.
-The power requirements are within margin of error, there is no significant packet loss in either case.
-The longer distance has a slightly higher latency (potentially caused by more retransmissions, we'll need to look at this \ref{section:futurework}).
-
-For this analysis, we disabled the 6TiSCH stack (using only the TSCH mac layer) and ensured no security was enabled. No further changes to the Contiki-NG network stack were required.
 
@@
 
-\begin{figure}[]
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{average_latencies.png}
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/latencies.png}
 	\caption{The average packet latencies for each distance/power combination}
@@
 \end{figure}
-\begin{figure}[]
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{transmission_reliability.png}
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/transmission_reliability.png}
 	\caption{Overview of amount of transmission attempts are made on average to send a single packet}
@@
 Another observation we can make, which is influenced by the transmission reliability, is the packet latency.
-In figure \ref{fig:averagelatencies}, the latencies are shown, averaged over the experiment run, per tested scenario.
+In \figref{fig:averagelatencies}, the latencies are shown, averaged over the experiment run, per tested scenario.
 
-The latencies shown in figure \ref{fig:averagelatencies} are grouped very closely together, just over 80 milliseconds.
+The latencies shown in \figref{fig:averagelatencies} are grouped very closely together, just over 80 milliseconds.
 Since the default TSCH slot length is 10 milliseconds, and the slot frame has 7 slots, it takes just over the duration of a slotframe for a packet to go from being queued in the leaf node to arriving at the root (give or take clock drift since the last TSCH time synchronization).
@@
 
-\begin{figure}[]
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{powerstates_10m.png}
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/powerstates_10m.png}
 	\caption{The power states for the nodes when 10 meters apart}
@@
 \end{figure}
-\begin{figure}[]
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=.5\textwidth,keepaspectratio]{powerstates_1m.png}
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/powerstates_1m.png}
 	\caption{The power states for the nodes when 1 meter apart}
@@
 
-The power results, as the latency and delivery results, are incredibly similar. This is trivially clear when comparing figures \ref{fig:power1m} and \ref{fig:power10m} - they are nearly identical.
+The power results, as the latency and delivery results, are incredibly similar. This is trivially clear when comparing \figref{fig:power1m} and \figref{fig:power10m} - they are nearly identical.
 
-Using the results from profiling the device (as in \ref{tab:CurrentConsumption}), and the Energest results we've obtained, we can compute the amount of power that is needed for each device.
+Using the results from profiling the device (as in \tabref{tab:CurrentConsumption}), and the Energest results we've obtained, we can compute the amount of power that is needed for each device.
 The leaf, overall, used approximately 3.4 J.
@@
 \section{Future Work}
+\label{section:futurework}
 
-\subsubsection{varied packet size}
+\subsubsection{Varied packet size}
 In this study, we've only looked at the performance characteristics of the network at various distances for packets carrying 64 bytes of data payload.
 An interesting follow-up might be the analysis of how the results change when the packet size is varied as well.
-A sensor network doing less complex measurements could definitely get by with smaller packets, for example, which presumably makes transmitting and receiving them simpler (does allowing lower TX power for the same delivery performance).
+A sensor network doing less complex measurements could definitely get by with smaller packets, for example.
+Smaller packets lead to shorter transmission times.
+This may reduce the error rate during transmission and thus could potentially achieve the same reliability at a lower TX power.
 
-\subsubsection{individually varied TX power}
+\subsubsection{Individually varied TX power}
 We've only considered the case where TX power is varied on both nodes.
@@
 This would clarify if, in order to ensure satisfactory network performance, TX power must be increased for all nodes or only for some.
-Our results have shown that larger TX power results in fewer retransmission (at the cost of increased power use per transmission), but we've not studied the trade-off in more detail.
-
-\begin{thebibliography}{00}
-\bibitem{contiki-NGWiki} Adam Dunkels, \url {https://github.com/contiki-ng/contiki-ng/wiki}
-\bibitem{6tischDef} X.
-Vilajosana, T.
-Watteyne, T.
-Chang, M.
-Vučinić, S.
-Duquennoy and P.
-Thubert, "IETF 6TiSCH: A Tutorial," in IEEE Communications Surveys \& Tutorials, vol.
-22, no.
-1, pp.
-595-615, Firstquarter 2020, doi: 10.1109/COMST.2019.2939407.
-\bibitem{TimeCritical6tisch} Karaagac, Abdulkadir \& Haxhibeqiri, Jetmir \& Moerman, Ingrid \& Hoebeke, Jeroen.
-(2018).
-Time-critical communication in 6TiSCH networks.
-161-166.
-10.1109/WCNCW.2018.8368987.
-\bibitem{EnergyConsumption} Sabovic, Adnan \& Delgado, Carmen \& Bauwens, Jan \& De Poorter, Eli \& Famaey, Jeroen.
-(2019).
-Accurate Online Energy Consumption Estimation of IoT Devices Using Energest.
-363-373.
-10.1007/978-3-030-33506-9\_32.
-\bibitem{ThroughputEvaluation} Lee, S.
-B., Kim, E.
-J., \& Lim, Y.
-(2018).
-Contiki-NG-based IEEE 802.15.
-4 TSCH Throughput Evaluation.
-In Proceedings of the Korean Institute of Information and Commucation Sciences Conference (pp.
-577-578).
-The Korea Institute of Information and Commucation Engineering.
-\bibitem{TSCHExperimentEval} García Algora, Carlos \& Alfonso Reguera, Vitalio. (2018). Experimental evaluation of IEEE 802.15.4 TSCH on a 6TiSCH network. 39. 70-78.
-\bibitem{AccurateEnergyTSCH} Accurate Energy Consumption Modeling of IEEE 802.15.4e TSCH Using Dual-BandOpenMote Hardware
-Glenn Daneels, Esteban Municio, Bruno Van de Velde, Glenn Ergeerts, Maarten Weyn, Steven Latré, \& Jeroen Famaey
-\bibitem{TSCHDefinition}A.
-Mavromatis, G.
-Z.
-Papadopoulos, X.
-Fafoutis, A.
-Elsts, G.
-Oikonomou and T.
-Tryfonas, "Impact of Guard Time Length on IEEE 802.15.4e TSCH Energy Consumption," 2016 13th Annual IEEE International Conference on Sensing, Communication, and Networking (SECON), London, 2016, pp.
-1-3, doi: 10.1109/SAHCN.2016.7732997.
-\end{thebibliography}
+Our results have shown that larger TX power results in fewer retransmission (at the cost of increased power use per transmission\cite{AccurateEnergyTSCH}), but we've not studied the trade-off in more detail.
+It is conceivable to have the root node be connected to a power source, while other nodes are running on battery, for example.
+So an interesting study would be to only increase TX power on the root node and see if (and to what degree) that improves performance the reliability, since its energy consumption is less relevant.
 

### 2021-01-21 examples/task3/plotting/data.py

@@ -1,35 +1,0 @@
-
-class Data:
-  def __init__(self, rxTimes = [], txTimes = [], numTx = []):
-    self.rxTimes = rxTimes
-    self.txTimes = txTimes
-    self.numTx = numTx
-
-rxTimes_1m = [19300, 19420, 19548, 19674, 19805, 19931, 20058, 20189, 20315, 20443, 20574, 20700, 20827, 20958, 21084, 21211, 21342, 21468, 21595, 21727, 21853, 21979, 22111, 22237, 22364, 22495, 22621, 22748, 22880, 23006, 23132, 23264, 23390, 23517, 23649, 23774, 23901, 24033, 24159, 24286, 24417, 24544, 24670, 24802, 24928, 25054, 25186, 25313, 25439, 25570, 25697, 25823, 25955, 26082, 26207, 26339, 26466, 26592, 26724, 26850]
-numtx_1m = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
-scheduleTimes_1m = [19289, 19415, 19541, 19669, 19799, 19926, 20054, 20183, 20310, 20438, 20568, 20695, 20823, 20952, 21079, 21208, 21337, 21463, 21591, 21722, 21848, 21976, 22105, 22232, 22360, 22490, 22616, 22744, 22874, 23001, 23129, 23258, 23385, 23514, 23644, 23770, 23897, 24027, 24154, 24281, 24412, 24538, 24667, 24796, 24923, 25051, 25180, 25307, 25436, 25564, 25691, 25820, 25949, 26076, 26205, 26333, 26460, 26588, 26718, 26845]
-run1m = Data(rxTimes_1m, scheduleTimes_1m, numtx_1m)
-
[…]

### 2021-01-21 examples/task3/plotting/data/data100m.py

@@ -1,0 +1,44 @@
+def_numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 4, 1, 1, 1, 1, 1, 1, 1, 1, 2, 0, 2, 1, 2, 1, 5, 4, 6, 3, 1, 2, 1, 1, 3, 1, 4, 1]
+def_scheduleTimes = [20556, 20681, 20807, 20941, 21067, 21193, 21319, 21453, 21578, 21705, 21838, 21964, 22090, 22216, 22350, 22475, 22601, 22735, 22861, 22987, 23113, 23247, 23372, 23498, 23632, 23757, 23884, 24010, 24144, 24269, 24395, 24529, 24654, 24781, 24907, 25041, 25166, 25292, 25426, 25551, 25678, 25803, 25938, 26062, 26187, 26323, 26448, 26574, 26700, 26835, 26959, 27085, 27219, 27345, 27470, 27597, 27732, 27856, 27983, 28116]
+def_sendTimes = [20557, 20683, 20808, 20944, 21068, 21194, 21328, 21454, 21580, 21705, 21841, 21965, 22091, 22225, 22351, 22476, 22602, 22738, 22862, 22988, 23122, 23248, 23373, 23499, 23633, 23759, 23885, 24019, 24145, 24270, 24396, 24539, 24657, 24808, 24916, 25042, 25167, 25293, 25427, 25553, 25678, 25813, 25948, 0, 26199, 26324, 26460, 26575, 26746, 26862, 27007, 27104, 27221, 27356, 27472, 27607, 27750, 27858, 28010, 28118]
+def_cpu_time_leaf = 42101
+def_cpu_sleep_time_leaf = 108875
+def_cpu_deepsleep_time_leaf = 1820028
+def_radio_rx_time_leaf = 9984
+def_radio_tx_time_leaf = 75736
+high_numtx = [1, 3, 1, 2, 1, 3, 3, 2, 1, 5, 2, 2, 1, 1, 1, 1, 2, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 2, 2, 1, 1, 1, 1, 1, 1, 1, 3, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
[…]

### 2021-01-21 examples/task3/plotting/data/data10m.py

@@ -1,0 +1,44 @@
+def_numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 2, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
+def_scheduleTimes = [152, 277, 404, 537, 663, 789, 915, 1050, 1173, 1300, 1433, 1560, 1686, 1812, 1946, 2071, 2197, 2330, 2457, 2583, 2709, 2843, 2968, 3093, 3227, 3354, 3480, 3607, 3740, 3865, 3990, 4124, 4250, 4377, 4503, 4637, 4762, 4887, 5021, 5147, 5274, 5400, 5534, 5659, 5784, 5919, 6044, 6170, 6296, 6431, 6555, 6681, 6815, 6941, 7068, 7194, 7328, 7452, 7578, 7711]
+def_sendTimes = [153, 279, 404, 540, 665, 790, 925, 1050, 1176, 1301, 1436, 1561, 1687, 1821, 1948, 2073, 2198, 2333, 2458, 2584, 2718, 2844, 2969, 3095, 3230, 3355, 3481, 3615, 3741, 3866, 3992, 4126, 4252, 4388, 4512, 4638, 4763, 4889, 5023, 5149, 5274, 5409, 5535, 5660, 5795, 5920, 6056, 6180, 6306, 6431, 6557, 6683, 6817, 6944, 7068, 7203, 7328, 7454, 7579, 7714]
+def_cpu_time_leaf = 44656
+def_cpu_sleep_time_leaf = 103719
+def_cpu_deepsleep_time_leaf = 1823782
+def_radio_rx_time_leaf = 6916
+def_radio_tx_time_leaf = 73812
+high_numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
[…]

### 2021-01-21 examples/task3/plotting/data/data1m.py

@@ -1,0 +1,47 @@
+def_numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
+def_scheduleTimes = [152, 277, 403, 537, 663, 789, 915, 1050, 1174, 1300, 1434, 1560, 1686, 1812, 1946, 2072, 2197, 2331, 2457, 2583, 2709, 2843, 2968, 3093, 3228, 3354, 3480, 3606, 3739, 3866, 3990, 4124, 4250, 4377, 4503, 4637, 4762, 4887, 5022, 5147, 5274, 5399, 5534, 5659, 5784, 5919, 6044, 6171, 6296, 6431, 6555, 6681, 6816, 6941, 7068, 7193, 7328, 7452, 7578, 7712]
+def_sendTimes = [153, 279, 405, 539, 664, 790, 925, 1050, 1176, 1301, 1436, 1561, 1687, 1821, 1947, 2074, 2198, 2333, 2458, 2584, 2718, 2844, 2969, 3095, 3230, 3355, 3481, 3615, 3741, 3866, 3992, 4126, 4252, 4378, 4512, 4638, 4763, 4890, 5023, 5149, 5274, 5409, 5535, 5660, 5786, 5920, 6046, 6171, 6306, 6431, 6558, 6683, 6817, 6943, 7068, 7203, 7328, 7454, 7580, 7714]
+def_cpu_time_leaf = 43873
+def_cpu_sleep_time_leaf = 103663
+def_cpu_deepsleep_time_leaf = 1824620
+def_radio_rx_time_leaf = 6448
+def_radio_tx_time_leaf = 73636
+
+def_cpu_time_coordinator = 30376
+def_cpu_sleep_time_coordinator = 177505
+def_cpu_deepsleep_time_coordinator = 1764756
+def_radio_rx_time_coordinator = 2169
+def_radio_tx_time_coordinator = 141482
+
[…]

### 2021-01-21 examples/task3/plotting/data/data50m.py

@@ -1,0 +1,46 @@
+def_numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 3, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 8, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1]
+def_scheduleTimes = [24959, 25086, 25211, 25346, 25470, 25596, 25731, 25856, 25983, 26108, 26242, 26367, 26493, 26627, 26753, 26880, 27005, 27140, 27264, 27390, 27524, 27650, 27775, 27902, 28037, 28161, 28287, 28421, 28547, 28673, 28799, 28933, 29058, 29184, 29319, 29444, 29570, 29696, 29830, 29955, 30080, 30216, 30341, 30467, 30592, 30726, 30852, 30978, 31112, 31237, 31364, 31490, 31623, 31749, 31874, 32009, 32134, 32261, 32385, 32520]
+def_sendTimes = [24962, 25086, 25221, 25346, 25472, 25598, 25732, 25858, 25983, 26128, 26252, 26369, 26494, 26629, 26755, 26880, 27015, 27140, 27266, 27391, 27526, 27661, 27777, 27912, 28037, 28182, 28288, 28423, 28548, 28674, 28808, 28934, 29060, 29185, 29320, 29445, 29571, 29705, 29831, 29956, 30092, 30217, 30342, 30531, 30593, 30728, 30853, 30979, 31113, 31239, 31365, 31499, 31625, 31750, 31876, 32010, 32136, 32271, 32388, 32521]
+def_cpu_time_leaf = 41330
+def_cpu_sleep_time_leaf = 106127
+def_cpu_deepsleep_time_leaf = 1822710
+def_radio_rx_time_leaf = 7800
+def_radio_tx_time_leaf = 74542
+
+high_numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
[…]

### 2021-01-21 examples/task3/plotting/data/data_10_1.py

@@ -1,17 +1,0 @@
-rxTimes = [5715, 5840, 5966, 6101, 6226, 6352, 6477, 6612, 6737, 6863, 6997, 7123, 7248, 7375, 7509, 7635, 7760, 7895, 8028, 8145, 8271, 8406, 8531, 8657, 8791, 8918, 9041, 9168, 9303, 9428, 9554, 9689, 9814, 9938, 10065, 10199, 10325, 10450, 10585, 10710, 10836, 10962, 11096, 11222, 11347, 11482, 11608, 11732, 11858, 11993, 12119, 12243, 12379, 12504, 12629, 12756, 12890, 13015, 13150, 13276]
-cpu_time_coordinator = 32173
-cpu_sleep_time_coordinator = 176498
-cpu_deepsleep_time_coordinator = 1772385
-radio_rx_time_coordinator = 2221
-radio_tx_time_coordinator = 141647
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1]
-scheduleTimes = [5703, 5829, 5955, 6090, 6215, 6341, 6467, 6600, 6726, 6852, 6987, 7112, 7238, 7364, 7497, 7623, 7749, 7884, 8009, 8135, 8260, 8394, 8520, 8645, 8781, 8906, 9032, 9157, 9292, 9416, 9543, 9678, 9803, 9929, 10054, 10188, 10313, 10440, 10574, 10700, 10826, 10951, 11085, 11210, 11337, 11471, 11596, 11722, 11848, 11981, 12107, 12233, 12368, 12494, 12620, 12745, 12879, 13004, 13130, 13265]
-cpu_time_leaf = 94839
-cpu_sleep_time_leaf = 95483
-cpu_deepsleep_time_leaf = 1775620
-radio_rx_time_leaf = 5796
-radio_tx_time_leaf = 73326
-rtimerTicksPerSecond = 32768

### 2021-01-21 examples/task3/plotting/data/data_10_3.py

@@ -1,17 +1,0 @@
-rxTimes = [2180, 2299, 2423, 2558, 2683, 2809, 2935, 3069, 3196, 3320, 3455, 3580, 3706, 3831, 3966, 4092, 4217, 4351, 4477, 4603, 4728, 4862, 4988, 5115, 5249, 5374, 5501, 5625, 5760, 5885, 6011, 6145, 6271, 6397, 6522, 6657, 6782, 6908, 7043, 7168, 7293, 7419, 7553, 7680, 7805, 7939, 8065, 8190, 8316, 8450, 8576, 8701, 8835, 8962, 9087, 9213, 9347, 9474, 9598, 9733]
-cpu_time_coordinator = 32815
-cpu_sleep_time_coordinator = 177060
-cpu_deepsleep_time_coordinator = 1785781
-radio_rx_time_coordinator = 2320
-radio_tx_time_coordinator = 142636
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
-scheduleTimes = [2160, 2286, 2413, 2546, 2673, 2798, 2925, 3059, 3184, 3310, 3443, 3570, 3695, 3821, 3956, 4081, 4207, 4340, 4467, 4592, 4718, 4852, 4978, 5103, 5237, 5364, 5490, 5616, 5749, 5875, 6000, 6134, 6260, 6386, 6513, 6646, 6772, 6897, 7031, 7157, 7283, 7409, 7544, 7667, 7794, 7928, 8054, 8180, 8306, 8440, 8564, 8691, 8824, 8951, 9077, 9203, 9337, 9462, 9588, 9721]
-cpu_time_leaf = 94125
-cpu_sleep_time_leaf = 95249
-cpu_deepsleep_time_leaf = 1776568
-radio_rx_time_leaf = 5980
-radio_tx_time_leaf = 73459
-rtimerTicksPerSecond = 32768

### 2021-01-21 examples/task3/plotting/data/data_10_7.py

@@ -1,17 +1,0 @@
-rxTimes = [27078, 27204, 27330, 27455, 27590, 27715, 27840, 27975, 28093, 28235, 28353, 28487, 28613, 28738, 28872, 28998, 29123, 29249, 29383, 29510, 29634, 29777, 29896, 30029, 30147, 30280, 30407, 30530, 30666, 30792, 30917, 31044, 31177, 31303, 31427, 31563, 31688, 31814, 31940, 32074, 32200, 32324, 32460, 32585, 32711, 32835, 32971, 33097, 33222, 33357, 33482, 33608, 33733, 33868, 33993, 34119, 34253, 34379, 34506, 34631]
-cpu_time_coordinator = 32571
-cpu_sleep_time_coordinator = 176629
-cpu_deepsleep_time_coordinator = 1781201
-radio_rx_time_coordinator = 2287
-radio_tx_time_coordinator = 142435
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 2, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 2, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
-scheduleTimes = [27066, 27192, 27318, 27445, 27579, 27704, 27830, 27964, 28089, 28216, 28341, 28476, 28602, 28728, 28861, 28986, 29113, 29238, 29373, 29498, 29624, 29758, 29883, 30010, 30135, 30270, 30395, 30521, 30654, 30780, 30907, 31032, 31167, 31291, 31418, 31551, 31677, 31802, 31929, 32064, 32189, 32315, 32448, 32575, 32700, 32827, 32960, 33086, 33211, 33345, 33472, 33597, 33723, 33856, 33983, 34108, 34243, 34368, 34494, 34620]
-cpu_time_leaf = 95366
-cpu_sleep_time_leaf = 95188
-cpu_deepsleep_time_leaf = 1775754
-radio_rx_time_leaf = 6164
-radio_tx_time_leaf = 73732
-rtimerTicksPerSecond = 32768

### 2021-01-21 examples/task3/plotting/data/data_1_1.py

@@ -1,17 +1,0 @@
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
-scheduleTimes = [3815, 3937, 4072, 4197, 4322, 4457, 4582, 4708, 4834, 4969, 5093, 5219, 5355, 5479, 5606, 5732, 5865, 5990, 6117, 6250, 6376, 6503, 6629, 6763, 6887, 7014, 7148, 7273, 7398, 7526, 7659, 7784, 7910, 8044, 8171, 8295, 8422, 8555, 8681, 8808, 8941, 9067, 9192, 9319, 9453, 9578, 9704, 9838, 9963, 10089, 10216, 10350, 10475, 10600, 10736, 10860, 10987, 11112, 11247, 11372]
-cpu_time_leaf = 102404
-cpu_sleep_time_leaf = 101753
-cpu_deepsleep_time_leaf = 1760840
-radio_rx_time_leaf = 5612
-radio_tx_time_leaf = 73188
-rtimerTicksPerSecond = 32768
-rxTimes = [3831, 3949, 4083, 4208, 4334, 4468, 4595, 4719, 4845, 4979, 5105, 5231, 5365, 5491, 5616, 5742, 5876, 6002, 6127, 6262, 6389, 6513, 6639, 6773, 6899, 7024, 7159, 7285, 7410, 7536, 7670, 7796, 7921, 8046, 8181, 8307, 8432, 8567, 8693, 8818, 8953, 9078, 9204, 9329, 9464, 9589, 9715, 9849, 9975, 10101, 10227, 10361, 10486, 10612, 10747, 10872, 10997, 11123, 11258, 11383]
-cpu_time_coordinator = 32414
-cpu_sleep_time_coordinator = 176347
-cpu_deepsleep_time_coordinator = 1776825
-radio_rx_time_coordinator = 2188
-radio_tx_time_coordinator = 141754

### 2021-01-21 examples/task3/plotting/data/data_1_3.py

@@ -1,17 +1,0 @@
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
-scheduleTimes = [28520, 28646, 28772, 28907, 29031, 29158, 29282, 29417, 29543, 29669, 29802, 29928, 30055, 30179, 30314, 30440, 30566, 30700, 30825, 30951, 31076, 31210, 31337, 31463, 31597, 31722, 31848, 31974, 32107, 32234, 32359, 32494, 32619, 32745, 32870, 33004, 33131, 33256, 33391, 33515, 33642, 33767, 33901, 34028, 34153, 34288, 34412, 34538, 34663, 34798, 34925, 35050, 35184, 35309, 35436, 35560, 35695, 35821, 35947, 36082]
-cpu_time_leaf = 94837
-cpu_sleep_time_leaf = 94819
-cpu_deepsleep_time_leaf = 1776285
-radio_rx_time_leaf = 5703
-radio_tx_time_leaf = 73332
-rtimerTicksPerSecond = 32768
-rxTimes = [28531, 28657, 28783, 28917, 29043, 29168, 29294, 29428, 29554, 29679, 29814, 29939, 30066, 30191, 30325, 30450, 30575, 30711, 30836, 30962, 31096, 31223, 31348, 31473, 31608, 31733, 31860, 31985, 32119, 32244, 32370, 32505, 32630, 32755, 32881, 33016, 33141, 33268, 33401, 33528, 33653, 33778, 33913, 34038, 34164, 34298, 34433, 34549, 34676, 34810, 34935, 35061, 35194, 35321, 35446, 35572, 35706, 35832, 35958, 36092]
-cpu_time_coordinator = 32835
-cpu_sleep_time_coordinator = 175609
-cpu_deepsleep_time_coordinator = 1781958
-radio_rx_time_coordinator = 2188
-radio_tx_time_coordinator = 142022

### 2021-01-21 examples/task3/plotting/data/data_1_7.py

@@ -1,17 +1,0 @@
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
-scheduleTimes = [7036, 7166, 7292, 7416, 7552, 7677, 7803, 7930, 8062, 8189, 8313, 8448, 8574, 8701, 8826, 8959, 9086, 9210, 9346, 9471, 9597, 9723, 9856, 9982, 10107, 10242, 10368, 10494, 10620, 10753, 10879, 11004, 11138, 11265, 11391, 11517, 11650, 11776, 11901, 12035, 12162, 12287, 12414, 12548, 12672, 12798, 12932, 13059, 13184, 13311, 13443, 13570, 13694, 13829, 13956, 14082, 14208, 14340, 14467, 14591]
-cpu_time_leaf = 94603
-cpu_sleep_time_leaf = 95378
-cpu_deepsleep_time_leaf = 1776654
-radio_rx_time_leaf = 5704
-radio_tx_time_leaf = 73209
-rtimerTicksPerSecond = 32768
-rxTimes = [7051, 7177, 7302, 7427, 7562, 7689, 7813, 7939, 8074, 8199, 8325, 8459, 8585, 8710, 8836, 8971, 9096, 9221, 9356, 9482, 9607, 9733, 9867, 9993, 10119, 10253, 10379, 10504, 10630, 10764, 10890, 11015, 11150, 11276, 11401, 11528, 11661, 11787, 11912, 12047, 12172, 12298, 12424, 12558, 12684, 12818, 12944, 13069, 13195, 13320, 13455, 13580, 13706, 13841, 13966, 14092, 14217, 14353, 14477, 14603]
-cpu_time_coordinator = 32079
-cpu_sleep_time_coordinator = 175604
-cpu_deepsleep_time_coordinator = 1773408
-radio_rx_time_coordinator = 2188
-radio_tx_time_coordinator = 141028

### 2021-01-21 examples/task3/plotting/data/data_3_1.py

@@ -1,17 +1,0 @@
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
-scheduleTimes = [3495, 3623, 3748, 3876, 4009, 4135, 4260, 4394, 4520, 4645, 4773, 4906, 5032, 5157, 5291, 5417, 5542, 5669, 5803, 5929, 6054, 6188, 6314, 6439, 6566, 6700, 6824, 6951, 7085, 7212, 7336, 7463, 7597, 7722, 7848, 7981, 8108, 8233, 8360, 8494, 8618, 8745, 8879, 9005, 9129, 9257, 9391, 9515, 9642, 9775, 9902, 10026, 10154, 10287, 10412, 10537, 10672, 10799, 10924, 11051]
-cpu_time_leaf = 94703
-cpu_sleep_time_leaf = 95046
-cpu_deepsleep_time_leaf = 1776557
-radio_rx_time_leaf = 5703
-radio_tx_time_leaf = 73412
-rtimerTicksPerSecond = 32768
-rxTimes = [3518, 3634, 3760, 3886, 4020, 4145, 4271, 4405, 4531, 4657, 4782, 4917, 5042, 5169, 5302, 5428, 5553, 5679, 5814, 5940, 6066, 6199, 6325, 6450, 6576, 6710, 6836, 6962, 7096, 7223, 7347, 7473, 7607, 7734, 7859, 7993, 8119, 8244, 8370, 8505, 8631, 8756, 8890, 9016, 9141, 9267, 9401, 9528, 9652, 9787, 9912, 10038, 10163, 10298, 10424, 10549, 10684, 10801, 10935, 11060]
-cpu_time_coordinator = 32118
-cpu_sleep_time_coordinator = 178091
-cpu_deepsleep_time_coordinator = 1786834
-radio_rx_time_coordinator = 2188
-radio_tx_time_coordinator = 142753

### 2021-01-21 examples/task3/plotting/data/data_3_3.py

@@ -1,20 +1,0 @@
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-rxTimes = [3411, 3528, 3661, 3788, 3911, 4047, 4172, 4298, 4423, 4558, 4683, 4809, 4944, 5070, 5195, 5320, 5455, 5580, 5705, 5841, 5966, 6092, 6217, 6352, 6477, 6602, 6737, 6863, 6989, 7114, 7249, 7374, 7499, 7634, 7760, 7885, 8011, 8145, 8271, 8396, 8531, 8658, 8782, 8909, 9042, 9168, 9293, 9428, 9555, 9679, 9805, 9939, 10065, 10190, 10325, 10450, 10576, 10702, 10836, 10962]
-cpu_time_coordinator = 31935
-cpu_sleep_time_coordinator = 176057
-cpu_deepsleep_time_coordinator = 1775286
-radio_rx_time_coordinator = 2188
-radio_tx_time_coordinator = 141483
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
-scheduleTimes = [3394, 3517, 3651, 3776, 3902, 4035, 4161, 4286, 4414, 4547, 4673, 4797, 4932, 5059, 5183, 5311, 5445, 5570, 5695, 5829, 5955, 6080, 6208, 6341, 6467, 6592, 6726, 6852, 6978, 7104, 7238, 7364, 7489, 7623, 7749, 7874, 8001, 8135, 8260, 8386, 8520, 8646, 8771, 8898, 9032, 9157, 9283, 9416, 9543, 9668, 9795, 9929, 10054, 10180, 10313, 10440, 10566, 10692, 10826, 10951]
-cpu_time_leaf = 94542
-cpu_sleep_time_leaf = 94824
-cpu_deepsleep_time_leaf = 1775632
-radio_rx_time_leaf = 5611
-radio_tx_time_leaf = 73035
-rtimerTicksPerSecond = 32768

### 2021-01-21 examples/task3/plotting/data/data_3_7.py

@@ -1,17 +1,0 @@
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 2, 1, 1]
-scheduleTimes = [12511, 12636, 12763, 12896, 13023, 13148, 13275, 13409, 13534, 13660, 13793, 13920, 14045, 14171, 14305, 14430, 14556, 14690, 14817, 14942, 15069, 15202, 15328, 15453, 15587, 15713, 15839, 15966, 16099, 16224, 16350, 16484, 16610, 16736, 16862, 16996, 17121, 17247, 17381, 17506, 17633, 17759, 17893, 18018, 18144, 18278, 18404, 18530, 18656, 18790, 18915, 19040, 19174, 19301, 19427, 19553, 19686, 19812, 19937, 20071]
-cpu_time_leaf = 94471
-cpu_sleep_time_leaf = 94956
-cpu_deepsleep_time_leaf = 1776515
-radio_rx_time_leaf = 5888
-radio_tx_time_leaf = 73320
-rtimerTicksPerSecond = 32768
-rxTimes = [12523, 12648, 12774, 12908, 13033, 13159, 13284, 13419, 13545, 13670, 13805, 13930, 14057, 14181, 14315, 14441, 14567, 14701, 14827, 14953, 15077, 15213, 15339, 15464, 15598, 15724, 15850, 15974, 16110, 16235, 16361, 16495, 16621, 16746, 16872, 17007, 17132, 17258, 17401, 17518, 17643, 17768, 17903, 18030, 18155, 18288, 18415, 18540, 18665, 18800, 18927, 19051, 19186, 19312, 19437, 19563, 19697, 19823, 19948, 20082]
-cpu_time_coordinator = 32611
-cpu_sleep_time_coordinator = 177001
-cpu_deepsleep_time_coordinator = 1789969
-radio_rx_time_coordinator = 2188
-radio_tx_time_coordinator = 142708

### 2021-01-21 examples/task3/plotting/data/data_5_1.py

@@ -1,17 +1,0 @@
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
-scheduleTimes = [1970, 2099, 2224, 2350, 2484, 2609, 2735, 2862, 2995, 3121, 3247, 3380, 3506, 3633, 3759, 3892, 4018, 4143, 4277, 4403, 4529, 4656, 4789, 4915, 5041, 5174, 5300, 5426, 5553, 5685, 5812, 5938, 6071, 6197, 6322, 6450, 6582, 6709, 6834, 6968, 7093, 7220, 7347, 7479, 7606, 7730, 7865, 7990, 8117, 8243, 8376, 8503, 8628, 8762, 8887, 9014, 9140, 9273, 9400, 9524]
-cpu_time_leaf = 94205
-cpu_sleep_time_leaf = 95034
-cpu_deepsleep_time_leaf = 1777397
-radio_rx_time_leaf = 5795
-radio_tx_time_leaf = 73286
-rtimerTicksPerSecond = 32768
-rxTimes = [1984, 2109, 2235, 2361, 2504, 2622, 2746, 2872, 3006, 3132, 3257, 3392, 3518, 3644, 3770, 3903, 4038, 4155, 4298, 4415, 4541, 4665, 4800, 4926, 5052, 5186, 5311, 5437, 5562, 5697, 5823, 5948, 6083, 6208, 6334, 6459, 6594, 6719, 6845, 6979, 7105, 7231, 7356, 7491, 7616, 7743, 7876, 8002, 8127, 8253, 8388, 8513, 8639, 8773, 8899, 9024, 9150, 9284, 9411, 9536]
-cpu_time_coordinator = 31746
-cpu_sleep_time_coordinator = 174207
-cpu_deepsleep_time_coordinator = 1767955
-radio_rx_time_coordinator = 2188
-radio_tx_time_coordinator = 140739

### 2021-01-21 examples/task3/plotting/data/data_5_3.py

@@ -1,17 +1,0 @@
-rxTimes = [9302, 9428, 9554, 9680, 9814, 9940, 10065, 10191, 10325, 10450, 10576, 10710, 10836, 10962, 11087, 11222, 11347, 11474, 11607, 11733, 11858, 11984, 12119, 12244, 12370, 12504, 12630, 12756, 12881, 13015, 13141, 13267, 13401, 13527, 13652, 13779, 13912, 14039, 14163, 14298, 14424, 14548, 14675, 14809, 14935, 15060, 15195, 15321, 15446, 15572, 15706, 15833, 15957, 16092, 16217, 16343, 16468, 16603, 16729, 16854]
-cpu_time_coordinator = 32837
-cpu_sleep_time_coordinator = 177119
-cpu_deepsleep_time_coordinator = 1787330
-radio_rx_time_coordinator = 2188
-radio_tx_time_coordinator = 142713
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
-scheduleTimes = [9288, 9416, 9543, 9669, 9802, 9929, 10053, 10181, 10313, 10440, 10565, 10699, 10825, 10951, 11078, 11211, 11337, 11462, 11596, 11722, 11847, 11974, 12107, 12234, 12359, 12493, 12619, 12744, 12871, 13005, 13130, 13256, 13390, 13516, 13641, 13768, 13901, 14027, 14153, 14286, 14413, 14539, 14665, 14798, 14924, 15050, 15183, 15310, 15434, 15562, 15695, 15821, 15947, 16080, 16207, 16331, 16459, 16591, 16718, 16844]
-cpu_time_leaf = 94181
-cpu_sleep_time_leaf = 95211
-cpu_deepsleep_time_leaf = 1777243
-radio_rx_time_leaf = 5612
-radio_tx_time_leaf = 73334
-rtimerTicksPerSecond = 32768

### 2021-01-21 examples/task3/plotting/data/data_5_7.py

@@ -1,17 +1,0 @@
-rxTimes = [14791, 14917, 15042, 15177, 15303, 15429, 15554, 15688, 15814, 15939, 16074, 16199, 16325, 16451, 16585, 16711, 16836, 16971, 17096, 17222, 17347, 17482, 17607, 17733, 17868, 17993, 18120, 18244, 18388, 18505, 18630, 18764, 18890, 19016, 19141, 19276, 19401, 19527, 19661, 19788, 19913, 20038, 20173, 20299, 20424, 20558, 20684, 20809, 20935, 21070, 21194, 21321, 21455, 21581, 21707, 21832, 21966, 22092, 22217, 22353]
-cpu_time_coordinator = 32420
-cpu_sleep_time_coordinator = 177551
-cpu_deepsleep_time_coordinator = 1791902
-radio_rx_time_coordinator = 2188
-radio_tx_time_coordinator = 143062
-slotTime = 10000
-slotTicks = 328
-ticksPerSecond = 128
-numtx = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]
-scheduleTimes = [14780, 14905, 15031, 15165, 15292, 15417, 15544, 15677, 15803, 15928, 16062, 16189, 16314, 16441, 16573, 16700, 16825, 16959, 17086, 17211, 17338, 17470, 17597, 17721, 17856, 17983, 18109, 18235, 18367, 18493, 18618, 18753, 18879, 19005, 19132, 19264, 19391, 19515, 19650, 19776, 19902, 20028, 20161, 20288, 20412, 20547, 20673, 20799, 20925, 21058, 21183, 21309, 21444, 21570, 21696, 21822, 21955, 22081, 22206, 22340]
-cpu_time_leaf = 95097
-cpu_sleep_time_leaf = 94994
-cpu_deepsleep_time_leaf = 1776649
-radio_rx_time_leaf = 5704
-radio_tx_time_leaf = 73197
-rtimerTicksPerSecond = 32768

### 2021-01-21 examples/task3/plotting/old/plot.py

@@ -1,102 +1,0 @@
-from matplotlib.pyplot import *
-import re
-
-if __name__ == "__main__":
-	startMarker = "[INFO: MyApp     ] Received first packet - assuming network convergence, now resetting power info."
-	packetMarker = "[INFO: MyApp     ] <--- Received"
-	filenames = ['out0.txt', 'out1.txt']
-	powerOrder = ['CPU', 'LPM', 'DEEPLPM','TX','RX','CPU', 'LPM', 'Deep','Tx','Rx','Total']
-	output_suffix = "0"
-	for filename in filenames:
-		index = None	
-		packetsArrived = []
-		powerOnTime = {}
-		latencies = []
-		with open(filename, 'r') as f:
-			started = False
-			nextPacket = True
-			currentRegex = 0
-			allLines = f.readlines()
-			for lineIndex in range(len(allLines)):
-				line = allLines[lineIndex][:-1] # Take line, cut off the new line at the end
-				if not started:
-					# Skip all lines preceding the first-packet-received
-					# As this marks the start of our network setup.
-					if line[:len(startMarker)] == startMarker:
-						started = True
-					continue
-				if nextPacket:
-					if line[:len(packetMarker)] == packetMarker:
-						nextPacket = False
-						index = -1
-						result = re.match(re.escape(packetMarker) + "\s(\d+)", line)
-						if (int(result[1]) > 120):
-							break
-						packetsArrived.append(int(result[1]))
-						# \w's in the below expression are slightly more lenient than we'd like (should be hexadecimal only), but close enough
-						result = re.match(re.escape(packetMarker) + "\s\d+\sfrom\s\w+\.\w+\.\w+\.\w+\sat\stime\s\d+,\ssent\sat\stime\s\d+\s\(latency\sis\s(\d+)", line)
-						latencies.append(int(result[1]))
-					continue
-
-				# From here is a repeating pattern, we can select pretty simply: 
-				if index == -1:
-					# Skip one intermediate line
-					index = 0
-					continue
-				result=re.search(powerOrder[index] + ":\s*(\d+)\sticks", line)
-
-
-				powerOnTime[powerOrder[index] + ("SEND" if index <= 4 else "RECV")] = int(result[1])
-				index += 1
-				if index == 11:
[…]

### 2021-01-21 examples/task3/plotting/plot.py

@@ -1,138 +1,168 @@
-import data.data_1_1 as d11
-import data.data_1_3 as d13
-import data.data_1_7 as d17
-import data.data_3_1 as d31
-import data.data_3_3 as d33
-import data.data_3_7 as d37
-import data.data_5_1 as d51
-import data.data_5_3 as d53
-import data.data_5_7 as d57
-import data.data_10_1 as d91
-import data.data_10_3 as d93
-import data.data_10_7 as d97
 
-
-
-dataSets = [d11, d13, d17, d31, d33, d37, d51, d53, d57, d91, d93, d97]
-dataSets1m = [d11, d13, d17]
-dataSets3m = [d31, d33, d37]
-dataSets5m = [d51, d53, d57]
-dataSets10m = [d91, d93, d97]
-dataSets1p = [d11, d31, d51, d91]
-dataSets3p = [d13, d33, d53, d93]
-dataSets7p = [d17, d37, d57, d97]
-
-powerSets = [dataSets1p, dataSets3p, dataSets7p]
-distanceSets = [dataSets1m, dataSets3m, dataSets5m, dataSets10m]
-distances = ["1m", "3m", "5m", "10m"]
-powers = ["-1dBm", "3dBm", "7dBm"]
-distancePowers=['1m, -1dBm', '1m, 3dBm', '1m, 7dBm', '3m, -1dBm', '3m, 3dBm', '3m, 7dBm', '5m, -1dBm', '5m, 3dBm', '5m, 7dBm', '10m, -1dBm', '10m, 3dBm', '10m, 7dBm']
-powerColors = ['ro-', 'go-', 'bo-']
-distanceColors = ['ro-', 'go-', 'bo-', 'mo-']
+from data import data1m, data10m, data100m, data50m 
 from matplotlib.pyplot import *
-output_suffix = ".png"
+from statistics import mean
 
+ioff()
 
-# Plot average transmission attempts per packet
-# Show per powerlevel
-# So for distances 1, 3, 5, 10 
+distances = ["1m", "10m", "50m", "100m"]
+powers = {"low_": "-7 dBm", "def_": "0 dBm", "high_": "7 dBm"}
+powerlist = ["-7 dBm", "0 dBm", "7 dBm"]
+prefixes = ["low_", "def_", "high_"]
 
-figure()
+modules = [data1m, data10m, data50m, data100m]
+
+# Retransmissions Figure
+fig = figure()
 title("Transmission reliability per power level")
[…]

### 2021-01-21 Paper/Paper.tex
report so far

@@
 \usepackage{url}
+\usepackage{multirow}
 \usepackage{biblatex}
@@
 \label{section:task2}
-%\section{Analysing the TSCH joining process}
-%\label{section:task2}
-% Miroslav not handing in, so no work here.
-%
-%			¯\_( ͡° ͜ʖ ͡°)_/¯
-%
+
+\subsection{Disclaimer}
+
+An oversight during the initial experiments for this section caused all the data to be invalid.
+Since command line defines (set in the Makefile) are used to set the behaviour for the TSCH layer, a recompile of the files setting the configured values is required for them to take effect.
+Since those files are not changed in between compilations, the Make build system does not automatically re-compile them when the Makefile changes.
+During our initial experiment set, these were the only changes made in between runs of the software.
+
+Initial dataset considered
 
@@
 
+\figref{fig:distance} shows a satellite image of where the measurements were taken.
+In this image, white and red dots were added marking the locations.
+The white dot is the location the static root node was placed.
+Then each red dot marks one of the locations that the leaf was placed in to perform our testing.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/distance}
+	\caption{Satellite image of the location the measurements were made}
+	\label{fig:distance}
+\end{figure}
+
 \subsubsection{TX power}
@@
 The amount of extra energy consumed by varying this value is left outside the scope of this study, because our study is limited to observing time spent in each energy state.
+We do have access to the required hardware to accurately determine how much power the device is drawing in any given energy state.
 The associated current draw for each energy state (used to compute final energy consumption values) is obtained through spec sheets or device profiling results (see \tabref{tab:CurrentConsumption}).
@@
 	\centering
-	\includegraphics[width=.4\textwidth,keepaspectratio]{figures/tsch_schedule.png}
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/tsch_schedule.png}
 	\caption{TSCH Schedule as used in the range analysis experiments}
@@
 
+\subsubsection{Network reliability}
+The PHY delivery ratio for packets is somewhat interchangeable for all TX powers at low distances.
+This is clear from \figref{fig:txattempts}.
+At higher distances, though, it becomes clear that the lower TX power struggles significantly more than the high TX power.
+In fact, while the TX power set to 7 dBm at 100 meters manages to deliver 100\% of packets, the -7 dBm TX power setting fails to do so.
+At 50m, it failed to deliver 2 out of 60 packets.
+At 100 meters, that shot up to 19/60.
+It is clear, then, that for two nodes that are separated by 100 meters, a TX power setting of -7 dBm is woefully insufficient.
+
 \begin{figure}[htbp]
 	\centering
-	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/latencies.png}
-	\caption{The average packet latencies for each distance/power combination}
-	\label{fig:averagelatencies}
-\end{figure}
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/transmission_reliability.png}
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/retransmissions}
 	\caption{Overview of amount of transmission attempts are made on average to send a single packet}
@@
 
-In our current test scenario, there is no meaningful difference between the various power levels when it comes to transmission reliability.
-The amount of transmission attempts that must be made per packet are essentially identical (and almost equal to 1) for all tested scenario's.
-
-Another observation we can make, which is influenced by the transmission reliability, is the packet latency.
-In \figref{fig:averagelatencies}, the latencies are shown, averaged over the experiment run, per tested scenario.
-
-The latencies shown in \figref{fig:averagelatencies} are grouped very closely together, just over 80 milliseconds.
-Since the default TSCH slot length is 10 milliseconds, and the slot frame has 7 slots, it takes just over the duration of a slotframe for a packet to go from being queued in the leaf node to arriving at the root (give or take clock drift since the last TSCH time synchronization).
-This seems a little high, given the limited amount of traffic being generated.
+This is also clearly visible in the packet latencies, as seen in \figref{fig:averagelatencies}.
+Clearly, as distance increases, so does the experienced packet latency.
+It is important to note that \figref{fig:averagelatencies} does not account for packets that did not arrive - it simply leaves them out of the calculation.
+This was done because no meaningful latency can be ascribed to a packet that did not arrive correctly.
+It clearly shows that as the distance increases and/or TX power decreases, the latency increases.
+The degree to which that happens, though, is underrepresented due to this fact.
 
@@
 	\centering
-	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/powerstates_10m.png}
-	\caption{The power states for the nodes when 10 meters apart}
-	\label{fig:power10m}
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/latencies}
+	\caption{The average packet latencies for each distance/power combination}
+	\label{fig:averagelatencies}
+\end{figure}
+
+\subsubsection{Energy use}
+
+\figref{fig:leaf_allstates} shows what percentage of time the leaf node spends in each power state in each of the experiments.
+The energy states are remarkably similar in all cases.
+The power states at 100m, -7 dBm are slightly offset from the rest of them.
+Presumably, because of the extra necessary re-transmissions, both the CPU and the radio are not able to sleep, or deep sleep, quite as often as they otherwise would.
+With the difference being so small, though, it is clear that the code we wrote has minimal impact on the device power states.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/leaf_allstates}
+	\caption{Power states for the leaf node, over all experiment setups}
+	\label{fig:leaf_allstates}
+\end{figure}
+
+In \figref{fig:leaf_radiostates} we zoom in on the radio power states (RX and TX).
+Here it is clear that the large distance, low TX power configuration uses relatively more radio time than the others, both RX and TX.
+That both increase seems intuitively correct, as retransmissions being necessary would require additional radio awake time.
+It is interesting that the RX time seems to increase relatively more than the TX time.
+This could be explained by the fact that when a node receives the ACK for a packet it has sent, it no longer needs to listen, allowing it to shut down the radio sooner.
+When the transmission fails, the radio has to be on for a longer period of time, causing a larger discrepancy.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/leaf_rx_tx}
+	\caption{Power states for the leaf node, zoomed in on radio states only}
+	\label{fig:leaf_radiostates}
+\end{figure}
+
+We also look at the root node's power results, in \figref{fig:root_allstates} and \figref{fig:root_radiostates}.
+These are even more similar than the leaf node's are, nearly identical in all cases.
+This is expected, though.
+The root application we are using does not, itself, transmit data.
+Rather, it only records its own energy state information when data is received from the leaf node.
+A very large majority of the time, the root application is simply sleeping.
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/root_allstates}
+	\caption{Power states for the leaf node, over all experiment setups}
+	\label{fig:root_allstates}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/powerstates_1m.png}
-	\caption{The power states for the nodes when 1 meter apart}
-	\label{fig:power1m}
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/root_rx_tx}
+	\caption{Power states for the leaf node, zoomed in on radio states only}
+	\label{fig:root_radiostates}
 \end{figure}
 
-The power results, as the latency and delivery results, are incredibly similar. This is trivially clear when comparing \figref{fig:power1m} and \figref{fig:power10m} - they are nearly identical.
+We use the values obtained through device profiling in \tabref{tab:CurrentConsumption} to estimate the node power use.
+This computation does not take into account the impact of the varied TX power parameter.
+As discussed in \secref{section:txpower}, it is not feasible for us to correctly assess power use while taking that parameter into account.
 
-Using the results from profiling the device (as in \tabref{tab:CurrentConsumption}), and the Energest results we've obtained, we can compute the amount of power that is needed for each device.
-The leaf, overall, used approximately 3.4 J.
-The root used approximately 4.1 J.
+In order to maintain clarity despite this restriction, we keep separate counts for the power used by the radio and the power used by the processor.
+It is thus important to note that for all figures in \tabref{tab:t3_powerresults}, the radio power use results are not quite as accurate as they could be.
+Both -7 dBm and 0 dBm values are higher than they should be (-7 dBm more so than 0 dBm), while 7 dBm's stated values are lower than they should be (the source of our data (\cite{EnergyConsumption}) does not mention changing the TX power, so presumably it was left at its default value of 3 dBm).
 
-With a total data size of 360 kilobits (12 tests * 60 packets * 64 bytes per packet * 8 bits per byte / 1024 bits per kilobit), that corresponds to roughly $9.6 \frac{mJ}{kbit}$ for the leaf and $11.5 \frac{mJ}{kbit}$ for the root.
+It is clear that, for the most part, the power use is close to identical for every considered scenario.
+As the distance increases, a slight increase in radio power use can be seen in all cases.
+More so in the low TX power cases.
+Given the results seen in \figref{fig:leaf_radiostates} and \figref{fig:root_radiostates}, that is to be expected.
+
+Each experiment transmitted 30720 bits (64 bytes * 60 packets * 8 bits per byte).
+Using that fact, we can compute the amount of energy per kilobit that was transmitted or received (for leaf and root, respectively).
+These numbers can be found in \tabref{tab:t3_powerperkilobit}.
 
@@
 
-The tests we ran do not offer a clear insight to the performance of TSCH in various scenarios.
-The different scenarios appear too close together to distinguish meaningful differences.
-Due to the inherent noisiness of the wireless medium, the tests should be expanded to be able to clearly spot a pattern.
-The duration should be extended and the difference between the values under test should increase.
-This way, if there is a pattern, it is less likely that a difference in noise in the medium will cause the test results to be essentially indistinguishable.
+The software we implemented barely influenced the power state the device was in.
+CPU-wise, this matches our expectations.
+Our program is written such that there is minimal computation required and most of the time our process sleeps, waiting for events to occur.
+In the case of the radio, the power use increases when more packets need to be sent.
+In our use-case, that is the case when retransmissions occur.
+If no retransmissions occur, the data sent is always the same.
+
+We've found that the TSCH layer manages good reliability over a distance of 100m, if the TX power parameter is set high enough.
+For a lower value for the TX power parameter, performance is lacklustre.
+Clearly there is a balance to be found between adequate performance and impact on the battery life.
+A TX power parameter that is set unnecessarily high will impact the battery life of a node simply by requiring more power per transmission, whereas a lower value will require more power because retransmissions are more likely.
+For any given distance, and environment noise level, the
 
@@
 
+\printbibliography
+
+\onecolumn
+
+\begin{table}[htbp]
+\noindent\makebox[\textwidth]{
+\begin{tabular}{c|c|c|c|c|c|c|c}
+\multicolumn{2}{c}{\multirow{2}{*}{}} & \multicolumn{2}{c}{-7 dBm} & \multicolumn{2}{c}{0 dBm} & \multicolumn{2}{c}{7 dBm} \\ \cline{3-8}
+\multicolumn{2}{c}{}                  & cpu          & radio       & cpu         & radio       & cpu         & radio       \\ \hline
+1 meter                       & root  & 0.2050 J     & 0.1367 J    & 0.2051 J    & 0.1364 J    & 0.2048 J    & 0.1363 J    \\ \cline{2-8}
+                              & leaf  & 0.1936 J     & 0.0760 J    & 0.1946 J    & 0.0759 J    & 0.1939 J    & 0.0759 J    \\ \hline
+\multirow{2}{*}{10 meters}    & root  & 0.2053 J     & 0.1371 J    & 0.2060 J    & 0.1378 J    & 0.2048 J    & 0.1365 J    \\ \cline{2-8}
+                              & leaf  & 0.1942 J     & 0.0770 J    & 0.1949 J    & 0.0765 J    & 0.1942 J    & 0.0759 J    \\ \hline
+\multirow{2}{*}{50 meters}    & root  & 0.2054 J     & 0.1372 J    & 0.2063 J    & 0.1376 J    & 0.2053 J    & 0.1365 J    \\ \cline{2-8}
+                              & leaf  & 0.1963 J     & 0.0829 J    & 0.1939 J    & 0.0780 J    & 0.1940 J    & 0.0758 J    \\ \hline
+\multirow{2}{*}{100 meters}   & root  & 0.2065 J     & 0.1382 J    & 0.2060 J    & 0.1382 J    & 0.2052 J    & 0.1373 J    \\ \cline{2-8}
+                              & leaf  & 0.2001 J     & 0.1015 J    & 0.1949 J    & 0.0811 J    & 0.1940 J    & 0.0791 J
+
+\end{tabular} 
+}
+\label{tab:t3_powerresults}
+\caption{Power use for leaf and root nodes in all experiment setups}
+\end{table}
+
+\begin{table}[htbp]
+\noindent\makebox[\textwidth]{
+\begin{tabular}{c|c|c|c|c|c|c|c}
+\multicolumn{2}{c}{\multirow{2}{*}{}} & \multicolumn{2}{c}{-7 dBm} & \multicolumn{2}{c}{0 dBm} & \multicolumn{2}{c}{7 dBm} \\[3pt] \cline{3-8}
+\multicolumn{2}{c}{}                  & cpu          & radio       & cpu         & radio       & cpu         & radio       \\[3pt] \hline
+1 meter                       & root  & 6.833 $\frac{mJ}{kbit}$ & 4.557 $\frac{mJ}{kbit}$ & 6.837 $\frac{mJ}{kbit}$ & 4.547 $\frac{mJ}{kbit}$ & 6.827 $\frac{mJ}{kbit}$ & 4.543 $\frac{mJ}{kbit}$ \\[3pt] \cline{2-8}
+                              & leaf  & 6.453 $\frac{mJ}{kbit}$ & 2.53 $\frac{mJ}{kbit}$ & 6.487$\frac{mJ}{kbit}$ & 2.53 $\frac{mJ}{kbit}$ & 6.463 $\frac{mJ}{kbit}$ & 2.53 $\frac{mJ}{kbit}$ \\[3pt] \hline
+\multirow{2}{*}{10 meters}    & root  & 6.843 $\frac{mJ}{kbit}$ & 4.570 $\frac{mJ}{kbit}$ & 6.867 $\frac{mJ}{kbit}$ & 4.593 $\frac{mJ}{kbit}$ & 6.827 $\frac{mJ}{kbit}$ & 4.55 $\frac{mJ}{kbit}$ \\[3pt] \cline{2-8}
+                              & leaf  & 6.473 $\frac{mJ}{kbit}$ & 2.567 $\frac{mJ}{kbit}$ & 6.497 $\frac{mJ}{kbit}$ & 2.55 $\frac{mJ}{kbit}$ & 6.473 $\frac{mJ}{kbit}$ & 2.53 $\frac{mJ}{kbit}$ \\[3pt] \hline
+\multirow{2}{*}{50 meters}    & root  & 6.847 $\frac{mJ}{kbit}$ & 4.573 $\frac{mJ}{kbit}$ & 6.877 $\frac{mJ}{kbit}$ & 4.587 $\frac{mJ}{kbit}$ & 6.843 $\frac{mJ}{kbit}$ & 4.55 $\frac{mJ}{kbit}$ \\[3pt] \cline{2-8}
+                              & leaf  & 6.543 $\frac{mJ}{kbit}$ & 2.763 $\frac{mJ}{kbit}$ & 6.463 $\frac{mJ}{kbit}$ & 2.6 $\frac{mJ}{kbit}$ & 6.467 $\frac{mJ}{kbit}$ & 2.527 $\frac{mJ}{kbit}$ \\[3pt] \hline
+\multirow{2}{*}{100 meters}   & root  & 6.883 $\frac{mJ}{kbit}$ & 4.607 $\frac{mJ}{kbit}$ & 6.867 $\frac{mJ}{kbit}$ & 4.607 $\frac{mJ}{kbit}$ & 6.84 $\frac{mJ}{kbit}$ & 4.577 $\frac{mJ}{kbit}$ \\[3pt] \cline{2-8}
+                              & leaf  & 6.67 $\frac{mJ}{kbit}$ & 3.383 $\frac{mJ}{kbit}$ & 6.497 $\frac{mJ}{kbit}$ & 2.703 $\frac{mJ}{kbit}$ & 6.467 $\frac{mJ}{kbit}$ & 2.637 $\frac{mJ}{kbit}$
+\end{tabular}
+}
+\label{tab:t3_powerperkilobit}
+\caption{Power use for leaf and root nodes in all experiment setups}
+\end{table}
+\twocolumn
+
 \end{document}

### 2021-01-21 examples/task2/leaf.sh

@@ -3,6 +3,10 @@
 # Probably not as necessary now that we've removed the compile-time define method of distinguishing
 # But can't hurt, either.
 touch leaf_app.c
+# Also touch tsch files. We change behaviour with command-line defines, so these are important
+touch ../../os/net/mac/tsch/tsch.c
+touch ../../os/net/mac/tsch/tsch.h
+touch ../../os/net/mac/tsch/tsch-conf.h
 if [ -e /dev/ttyUSB1 ]; then
 	echo "Installing leaf onto port 1!"
 	make -j 20 leaf_app.upload PORT=/dev/ttyUSB1

### 2021-01-21 examples/task2/leaf_app.c

@@ -87,7 +87,9 @@ PROCESS_THREAD(leaf_app, ev, data)
 
 void send_callback(void *ptr, int status, int num_tx) {
 	uint8_t buffer;
-	memcpy(&buffer, ptr, 1);
+	char* p = (char*) ptr + 21;
+	// Ignore the header, get our value
+	memcpy(&buffer, p, 1);
 	if (status != 0) {
 		sendPacket();
 		LOG_WARN("Re-sent marker packet for index %u. Readings may not be reliable.\n", buffer);

### 2021-01-21 examples/task2/plotting/data/data_16/leaf_1.py

@@ -1,0 +1,530 @@
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 58505
+Link-layer address: 0012.4b00.1932.e489
+Zolertia RE-Mote revision B platform
+Leaf started with channel hopping sequence size: 1
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 502910
+seconds = 15
+cpu = 8089
+lpm = 493230
+deep = 1730
+tx = 38
+rx = 500719
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 462667
+seconds = 14
+cpu = 7692
+lpm = 453349
+deep = 1765
+tx = 38
+rx = 460436
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 412204
+seconds = 13
+cpu = 6870
+lpm = 403738
+deep = 1735
+tx = 38
+rx = 410005
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 405322
+seconds = 12
+cpu = 6763
+lpm = 396934
+deep = 1764
+tx = 38
+rx = 403093
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 464961
+seconds = 14
+cpu = 7696
+lpm = 455647
+deep = 1757
+tx = 38
+rx = 462737
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 414497
+seconds = 13
+cpu = 6924
+lpm = 405733
+deep = 1979
+tx = 38
+rx = 412092
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 439729
+seconds = 13
+cpu = 7266
+lpm = 430733
+deep = 1869
+tx = 38
+rx = 437395
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 522306
+seconds = 16
+cpu = 8591
+lpm = 512099
+deep = 1755
+tx = 38
+rx = 520084
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
[…]

### 2021-01-21 examples/task2/plotting/data/data_16/leaf_16.py

@@ -1,0 +1,319 @@
+cpu = 1864
+lpm = 17543
+deep = 425574
+tx = 85
+rx = 15262
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 57953
+Link-layer address: 0012.4b00.1932.e261
+Zolertia RE-Mote revision B platform
+cpu = 1904
+lpm = 16141
+deep = 394823
+tx = 85
+rx = 14165
+cpu = 4065
+lpm = 32460
+deep = 784633
+tx = 170
+rx = 28173
+cpu = 6538
+lpm = 49541
+deep = 1198599
+tx = 255
+rx = 43036
+cpu = 8969
+lpm = 68730
+deep = 1663258
+tx = 340
+rx = 59717
+cpu = 11305
+lpm = 85429
+deep = 2066272
+tx = 425
+rx = 74187
+cpu = 13817
+lpm = 105345
+deep = 2548473
+tx = 510
+rx = 91487
+cpu = 16539
+lpm = 125325
+deep = 3034984
+tx = 595
+rx = 108950
+cpu = 18839
+lpm = 142778
+deep = 3455634
+tx = 680
+rx = 124046
+cpu = 21283
+lpm = 160897
+deep = 3891527
+tx = 765
+rx = 139691
+cpu = 23590
+lpm = 176974
+deep = 4283728
+tx = 850
+rx = 153763
+cpu = 26001
+lpm = 195627
+deep = 4735178
+tx = 935
+rx = 169959
+cpu = 28225
+lpm = 212103
+deep = 5133944
+tx = 1020
+rx = 184278
+cpu = 30827
+lpm = 230641
+deep = 5587611
+tx = 1105
+rx = 200563
+cpu = 33525
+lpm = 250890
+deep = 6078466
+tx = 1190
+rx = 218194
+cpu = 35809
+lpm = 266772
+deep = 6461708
+tx = 1275
+rx = 231949
+cpu = 38148
+lpm = 283793
+deep = 6871280
+tx = 1360
+rx = 246657
+cpu = 40875
+lpm = 304303
+deep = 7366434
+tx = 1445
+rx = 264439
+cpu = 43248
+lpm = 321298
+deep = 7775998
+tx = 1530
+rx = 279150
[…]

### 2021-01-21 examples/task2/plotting/data/data_16/leaf_4.py

@@ -1,0 +1,540 @@
+Leaf packet sent!
+ticks = 499366
+seconds = 15
+cpu = 8231
+lpm = 489416
+deep = 1858
+tx = 38
+rx = 497041
+Leaf loop start!
+Leaf waiting for association!
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 58505
+Link-layer address: 0012.4b00.1932.e489
+Zolertia RE-Mote revision B platform
+Leaf started with channel hopping sequence size: 4
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 502711
+seconds = 15
+cpu = 8153
+lpm = 492910
+deep = 1787
+tx = 38
+rx = 500461
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 460373
+seconds = 14
+cpu = 7612
+lpm = 451124
+deep = 1776
+tx = 38
+rx = 458133
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 409911
+seconds = 13
+cpu = 6787
+lpm = 401517
+deep = 1746
+tx = 38
+rx = 407702
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 471840
+seconds = 14
+cpu = 7802
+lpm = 462199
+deep = 1978
+tx = 38
+rx = 469434
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 416794
+seconds = 13
+cpu = 6967
+lpm = 407994
+deep = 1972
+tx = 38
+rx = 414387
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 506247
+seconds = 15
+cpu = 8375
+lpm = 496186
+deep = 1825
+tx = 38
+rx = 503954
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 471842
+seconds = 14
+cpu = 7839
+lpm = 462161
+deep = 1981
+tx = 38
+rx = 469433
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
[…]

### 2021-01-21 examples/task2/plotting/data/data_16/root_1.py

@@ -1,0 +1,309 @@
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 57953
+Link-layer address: 0012.4b00.1932.e261
+Zolertia RE-Mote revision B platform
+cpu = 2113
+lpm = 18139
+deep = 443081
+tx = 85
+rx = 15899
+cpu = 4312
+lpm = 34584
+deep = 837313
+tx = 170
+rx = 30055
+cpu = 6469
+lpm = 50798
+deep = 1224937
+tx = 255
+rx = 43972
+cpu = 8988
+lpm = 69038
+deep = 1669827
+tx = 340
+rx = 59941
+cpu = 11192
+lpm = 85478
+deep = 2066337
+tx = 425
+rx = 74181
+cpu = 13476
+lpm = 102950
+deep = 2486983
+tx = 510
+rx = 89289
+cpu = 16162
+lpm = 123706
+deep = 2986519
+tx = 595
+rx = 107230
+cpu = 18520
+lpm = 142112
+deep = 3426802
+tx = 680
+rx = 123040
+cpu = 20833
+lpm = 159683
+deep = 3851905
+tx = 765
+rx = 138292
+cpu = 23165
+lpm = 175957
+deep = 4248471
+tx = 850
+rx = 152523
+cpu = 25472
+lpm = 193476
+deep = 4671339
+tx = 935
+rx = 167694
+cpu = 27832
+lpm = 211578
+deep = 5107337
+tx = 1020
+rx = 183343
+cpu = 30159
+lpm = 227734
+deep = 5501730
+tx = 1105
+rx = 197490
+cpu = 32573
+lpm = 246548
+deep = 5953017
+tx = 1190
+rx = 213701
+cpu = 35404
+lpm = 266566
+deep = 6443971
+tx = 1275
+rx = 231323
+cpu = 37697
+lpm = 283879
+deep = 6860179
+tx = 1360
+rx = 246264
+cpu = 40049
+lpm = 301950
+deep = 7293920
+tx = 1445
+rx = 261838
+cpu = 42602
+lpm = 320851
+deep = 7751861
+tx = 1530
+rx = 278275
+cpu = 45056
+lpm = 338929
+deep = 8187788
+tx = 1615
[…]

### 2021-01-21 examples/task2/plotting/data/data_16/root_16.py

@@ -1,0 +1,530 @@
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 58505
+Link-layer address: 0012.4b00.1932.e489
+Zolertia RE-Mote revision B platform
+Leaf started with channel hopping sequence size: 16
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 440761
+seconds = 13
+cpu = 7493
+lpm = 431614
+deep = 1793
+tx = 38
+rx = 438506
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 412203
+seconds = 13
+cpu = 6809
+lpm = 403800
+deep = 1733
+tx = 38
+rx = 410007
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 407617
+seconds = 12
+cpu = 6798
+lpm = 399203
+deep = 1755
+tx = 38
+rx = 405399
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 432848
+seconds = 13
+cpu = 7223
+lpm = 423866
+deep = 1898
+tx = 38
+rx = 430485
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 485606
+seconds = 15
+cpu = 8016
+lpm = 475809
+deep = 1920
+tx = 38
+rx = 483220
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 421377
+seconds = 13
+cpu = 7048
+lpm = 412521
+deep = 1947
+tx = 38
+rx = 418972
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 503956
+seconds = 15
+cpu = 8306
+lpm = 493951
+deep = 1838
+tx = 38
+rx = 501651
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 508540
+seconds = 16
+cpu = 8409
+lpm = 498454
+deep = 1816
+tx = 38
+rx = 506257
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
[…]

### 2021-01-21 examples/task2/plotting/data/data_16/root_4.py

@@ -1,0 +1,309 @@
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 57953
+Link-layer address: 0012.4b00.1932.e261
+Zolertia RE-Mote revision B platform
+cpu = 2244
+lpm = 18258
+deep = 440537
+tx = 85
+rx = 15794
+cpu = 4529
+lpm = 34453
+deep = 832640
+tx = 170
+rx = 29858
+cpu = 6950
+lpm = 53136
+deep = 1284049
+tx = 255
+rx = 46048
+cpu = 9295
+lpm = 69511
+deep = 1682795
+tx = 340
+rx = 60343
+cpu = 11904
+lpm = 89650
+deep = 2166967
+tx = 425
+rx = 77725
+cpu = 14431
+lpm = 108403
+deep = 2618202
+tx = 510
+rx = 93916
+cpu = 16734
+lpm = 124683
+deep = 3014789
+tx = 595
+rx = 108151
+cpu = 19275
+lpm = 144762
+deep = 3499090
+tx = 680
+rx = 125523
+cpu = 21591
+lpm = 160879
+deep = 3886651
+tx = 765
+rx = 139427
+cpu = 24093
+lpm = 180495
+deep = 4362281
+tx = 850
+rx = 156499
+cpu = 26386
+lpm = 197905
+deep = 4780684
+tx = 935
+rx = 171525
+cpu = 28866
+lpm = 215979
+deep = 5218884
+tx = 1020
+rx = 187267
+cpu = 31408
+lpm = 236169
+deep = 5705366
+tx = 1105
+rx = 204725
+cpu = 33802
+lpm = 253185
+deep = 6117183
+tx = 1190
+rx = 219505
+cpu = 36172
+lpm = 271279
+deep = 6553178
+tx = 1275
+rx = 235159
+cpu = 38920
+lpm = 291261
+deep = 7041955
+tx = 1360
+rx = 252703
+cpu = 41312
+lpm = 309602
+deep = 7486856
+tx = 1445
+rx = 268665
+cpu = 43617
+lpm = 325956
+deep = 7883366
+tx = 1530
+rx = 282896
+cpu = 46262
+lpm = 345946
+deep = 8367653
+tx = 1615
[…]

### 2021-01-21 examples/task2/plotting/data/data_32/leaf_1.py

@@ -1,0 +1,542 @@
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 58505
+Link-layer address: 0012.4b00.1932.e489
+Zolertia RE-Mote revision B platform
+Leaf started with channel hopping sequence size: 1
+Leaf loop start!
+Leaf waiting for association!
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 58505
+Link-layer address: 0012.4b00.1932.e489
+Zolertia RE-Mote revision B platform
+Leaf started with channel hopping sequence size: 1
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 458116
+seconds = 14
+cpu = 7392
+lpm = 449127
+deep = 1736
+tx = 38
+rx = 455919
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 453490
+seconds = 14
+cpu = 7801
+lpm = 444024
+deep = 1804
+tx = 38
+rx = 451220
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 446612
+seconds = 14
+cpu = 7439
+lpm = 437473
+deep = 1839
+tx = 38
+rx = 444308
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 481015
+seconds = 15
+cpu = 7938
+lpm = 471278
+deep = 1938
+tx = 38
+rx = 478610
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 458082
+seconds = 14
+cpu = 7620
+lpm = 448813
+deep = 1788
+tx = 38
+rx = 455828
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 476428
+seconds = 15
+cpu = 7771
+lpm = 466838
+deep = 1958
+tx = 38
+rx = 474021
+Leaf loop start!
[…]

### 2021-01-21 examples/task2/plotting/data/data_32/leaf_16.py

@@ -1,0 +1,540 @@
+Leaf packet sent!
+ticks = 503965
+seconds = 15
+cpu = 8623
+lpm = 493645
+deep = 1836
+tx = 38
+rx = 501663
+Leaf loop start!
+Leaf waiting for association!
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 58505
+Link-layer address: 0012.4b00.1932.e489
+Zolertia RE-Mote revision B platform
+Leaf started with channel hopping sequence size: 16
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 411149
+seconds = 13
+cpu = 6767
+lpm = 402644
+deep = 1877
+tx = 38
+rx = 408811
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 425965
+seconds = 13
+cpu = 7045
+lpm = 417132
+deep = 1927
+tx = 38
+rx = 423574
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 435143
+seconds = 13
+cpu = 7227
+lpm = 426165
+deep = 1890
+tx = 38
+rx = 432788
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 423672
+seconds = 13
+cpu = 7078
+lpm = 414794
+deep = 1939
+tx = 38
+rx = 421268
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 499368
+seconds = 15
+cpu = 8206
+lpm = 489443
+deep = 1858
+tx = 38
+rx = 497043
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 439727
+seconds = 13
+cpu = 7332
+lpm = 430668
+deep = 1866
+tx = 38
+rx = 437394
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 421381
+seconds = 13
+cpu = 7019
+lpm = 412550
+deep = 1951
+tx = 38
+rx = 418973
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
[…]

### 2021-01-21 examples/task2/plotting/data/data_32/leaf_4.py

@@ -1,0 +1,530 @@
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 58505
+Link-layer address: 0012.4b00.1932.e489
+Zolertia RE-Mote revision B platform
+Leaf started with channel hopping sequence size: 4
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 83068
+seconds = 3
+cpu = 1847
+lpm = 79625
+deep = 1730
+tx = 38
+rx = 80880
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 416804
+seconds = 13
+cpu = 7231
+lpm = 407744
+deep = 1968
+tx = 38
+rx = 414396
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 442023
+seconds = 13
+cpu = 6771
+lpm = 433531
+deep = 1860
+tx = 38
+rx = 439696
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 520010
+seconds = 16
+cpu = 8319
+lpm = 510067
+deep = 1763
+tx = 38
+rx = 517780
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 428262
+seconds = 13
+cpu = 7119
+lpm = 419361
+deep = 1921
+tx = 38
+rx = 425876
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 419083
+seconds = 13
+cpu = 7024
+lpm = 410240
+deep = 1958
+tx = 38
+rx = 416676
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 503957
+seconds = 15
+cpu = 8050
+lpm = 494207
+deep = 1839
+tx = 38
+rx = 501653
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 474134
+seconds = 14
+cpu = 7744
+lpm = 464560
+deep = 1969
+tx = 38
+rx = 471727
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
[…]

### 2021-01-21 examples/task2/plotting/data/data_32/root_1.py

@@ -1,0 +1,302 @@
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 57953
+Link-layer address: 0012.4b00.1932.e261
+Zolertia RE-Mote revision B platform
+Root going to sleep![INFO: Main      - Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 57953
+Link-layer address: 0012.4b00.1932.e261
+Zolertia RE-Mote revision B platform
+cpu = 2083
+lpm = 17817
+deep = 434255
+tx = 85
+rx = 15572
+cpu = 4517
+lpm = 35463
+deep = 861460
+tx = 170
+rx = 30899
+cpu = 6946
+lpm = 54598
+deep = 1321584
+tx = 255
+rx = 47412
+cpu = 9445
+lpm = 72694
+deep = 1759743
+tx = 340
+rx = 63125
+cpu = 11892
+lpm = 91615
+deep = 2215476
+tx = 425
+rx = 79477
+cpu = 14221
+lpm = 108491
+deep = 2620617
+tx = 510
+rx = 94024
+cpu = 16671
+lpm = 125745
+deep = 3036726
+tx = 595
+rx = 108976
+cpu = 19255
+lpm = 146571
+deep = 3536294
+tx = 680
+rx = 126903
+cpu = 21629
+lpm = 163295
+deep = 3943835
+tx = 765
+rx = 141533
+cpu = 23947
+lpm = 179806
+deep = 4344764
+tx = 850
+rx = 155919
+cpu = 26131
+lpm = 195856
+deep = 4730231
+tx = 935
+rx = 169759
+cpu = 28398
+lpm = 213066
+deep = 5144276
+tx = 1020
+rx = 184627
+cpu = 30971
+lpm = 232132
+deep = 5608913
+tx = 1105
+rx = 201291
+cpu = 33322
+lpm = 250190
+deep = 6042669
+tx = 1190
+rx = 216868
+cpu = 35776
+lpm = 267812
+deep = 6469875
+tx = 1275
+rx = 232191
+cpu = 38101
[…]

### 2021-01-21 examples/task2/plotting/data/data_32/root_16.py

@@ -1,0 +1,314 @@
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 57953
+Link-layer address: 0012.4b00.1932.e261
+Zolertia RE-Mote revision B platform
+cpu = 1956
+lpm = 16651
+deep = 408023
+tx = 85
+rx = 14633
+cpu = 4538
+lpm = 33826
+deep = 824082
+tx = 170
+rx = 29597
+cpu = 6849
+lpm = 50860
+deep = 1229081
+tx = 255
+rx = 44150
+cpu = 9423
+lpm = 70528
+deep = 1706880
+tx = 340
+rx = 61306
+cpu = 11902
+lpm = 87752
+deep = 2127577
+tx = 425
+rx = 76404
+cpu = 14054
+lpm = 104674
+deep = 2530556
+tx = 510
+rx = 90876
+cpu = 16311
+lpm = 120525
+deep = 2916149
+tx = 595
+rx = 104707
+cpu = 18824
+lpm = 138902
+deep = 3360894
+tx = 680
+rx = 120665
+cpu = 21046
+lpm = 155212
+deep = 3755238
+tx = 765
+rx = 134808
+cpu = 23318
+lpm = 171422
+deep = 4145046
+tx = 850
+rx = 148806
+cpu = 25971
+lpm = 189686
+deep = 4589761
+tx = 935
+rx = 164782
+cpu = 28388
+lpm = 208645
+deep = 5047780
+tx = 1020
+rx = 181224
+cpu = 30624
+lpm = 225592
+deep = 5452944
+tx = 1105
+rx = 195786
+cpu = 33220
+lpm = 244140
+deep = 5902021
+tx = 1190
+rx = 211907
+cpu = 35453
+lpm = 260674
+deep = 6300717
+tx = 1275
+rx = 226206
+cpu = 37657
+lpm = 276748
+deep = 6690729
+tx = 1360
+rx = 240200
+cpu = 40192
+lpm = 293653
+deep = 7102515
+tx = 1445
+rx = 254993
+cpu = 42639
+lpm = 313024
+deep = 7569269
+tx = 1530
+rx = 271762
+cpu = 44950
+lpm = 329624
+deep = 7972409
+tx = 1615
[…]

### 2021-01-21 examples/task2/plotting/data/data_32/root_4.py

@@ -1,0 +1,322 @@
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 57953
+Link-layer address: 0012.4b00.1932.e261
+Zolertia RE-Mote revision B platform
+Root going to sleep![INFO: Main      - Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 57953
+Link-layer address: 0012.4b00.1932.e261
+Zolertia RE-Mote revision B platform
+cpu = 1779
+lpm = 16453
+deep = 399226
+tx = 85
+rx = 14315
+cpu = 4060
+lpm = 33926
+deep = 822168
+tx = 170
+rx = 29508
+cpu = 6798
+lpm = 54409
+deep = 1319629
+tx = 255
+rx = 47366
+cpu = 9117
+lpm = 71325
+deep = 1729329
+tx = 340
+rx = 62074
+cpu = 11401
+lpm = 87777
+deep = 2130349
+tx = 425
+rx = 76474
+cpu = 13998
+lpm = 107762
+deep = 2612396
+tx = 510
+rx = 93809
+cpu = 16473
+lpm = 126459
+deep = 3066031
+tx = 595
+rx = 110099
+cpu = 19208
+lpm = 146721
+deep = 3556836
+tx = 680
+rx = 127730
+cpu = 21590
+lpm = 165330
+deep = 4003772
+tx = 765
+rx = 143790
+cpu = 24211
+lpm = 184299
+deep = 4461578
+tx = 850
+rx = 160245
+cpu = 26729
+lpm = 203784
+deep = 4930439
+tx = 935
+rx = 177101
+cpu = 29067
+lpm = 220431
+deep = 5331213
+tx = 1020
+rx = 191490
+cpu = 31640
+lpm = 240277
+deep = 5811128
+tx = 1105
+rx = 208723
+cpu = 34160
+lpm = 259089
+deep = 6264602
+tx = 1190
+rx = 225007
+cpu = 36613
+lpm = 278121
+deep = 6722515
+tx = 1275
+rx = 241441
+cpu = 39199
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/leaf_1.py

@@ -1,0 +1,508 @@
+Leaf packet sent!
+ticks = 501671
+seconds = 15
+cpu = 8249
+lpm = 491716
+deep = 1845
+tx = 38
+rx = 499360
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 474136
+seconds = 14
+cpu = 7896
+lpm = 464409
+deep = 1970
+tx = 38
+rx = 471727
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 513128
+seconds = 16
+cpu = 8242
+lpm = 503230
+deep = 1795
+tx = 38
+rx = 510866
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 499369
+seconds = 15
+cpu = 8097
+lpm = 489553
+deep = 1858
+tx = 38
+rx = 497044
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 469548
+seconds = 14
+cpu = 7758
+lpm = 460194
+deep = 1735
+tx = 38
+rx = 467346
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 451197
+seconds = 14
+cpu = 7487
+lpm = 442033
+deep = 1816
+tx = 38
+rx = 448915
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 481018
+seconds = 15
+cpu = 7793
+lpm = 471424
+deep = 1940
+tx = 38
+rx = 478613
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 423673
+seconds = 13
+cpu = 7047
+lpm = 414825
+deep = 1940
+tx = 38
+rx = 421268
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 435141
+seconds = 13
+cpu = 7260
+lpm = 426132
+deep = 1888
+tx = 38
+rx = 432787
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 425968
+seconds = 13
+cpu = 7081
+lpm = 417095
+deep = 1931
+tx = 38
+rx = 423571
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 435139
+seconds = 13
+cpu = 7227
+lpm = 426164
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/leaf_16.py

@@ -1,0 +1,540 @@
+Leaf packet sent!
+ticks = 412207
+seconds = 13
+cpu = 6811
+lpm = 403799
+deep = 1736
+tx = 38
+rx = 410008
+Leaf loop start!
+Leaf waiting for association!
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 58505
+Link-layer address: 0012.4b00.1932.e489
+Zolertia RE-Mote revision B platform
+Leaf started with channel hopping sequence size: 16
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 420894
+seconds = 13
+cpu = 7030
+lpm = 412110
+deep = 1893
+tx = 38
+rx = 418540
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 490191
+seconds = 15
+cpu = 8086
+lpm = 480345
+deep = 1899
+tx = 38
+rx = 487826
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 517718
+seconds = 16
+cpu = 8417
+lpm = 507665
+deep = 1775
+tx = 38
+rx = 515478
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 428259
+seconds = 13
+cpu = 7118
+lpm = 419362
+deep = 1918
+tx = 38
+rx = 425877
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 451200
+seconds = 14
+cpu = 7474
+lpm = 442047
+deep = 1818
+tx = 38
+rx = 448918
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 476428
+seconds = 15
+cpu = 7891
+lpm = 466717
+deep = 1959
+tx = 38
+rx = 474021
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 522305
+seconds = 16
+cpu = 8625
+lpm = 512063
+deep = 1756
+tx = 38
+rx = 520081
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/leaf_4.py

@@ -1,0 +1,542 @@
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 58505
+Link-layer address: 0012.4b00.1932.e489
+Zolertia RE-Mote revision B platform
+Leaf started with channel hopping sequence size: 4
+Leaf loop start!
+Leaf waiting for association!
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 58505
+Link-layer address: 0012.4b00.1932.e489
+Zolertia RE-Mote revision B platform
+Leaf started with channel hopping sequence size: 4
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 498105
+seconds = 15
+cpu = 7972
+lpm = 488483
+deep = 1789
+tx = 38
+rx = 495855
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 460372
+seconds = 14
+cpu = 7911
+lpm = 450826
+deep = 1774
+tx = 38
+rx = 458133
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 444318
+seconds = 14
+cpu = 7681
+lpm = 434928
+deep = 1848
+tx = 38
+rx = 442005
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 414496
+seconds = 13
+cpu = 7199
+lpm = 405458
+deep = 1978
+tx = 38
+rx = 412091
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 409911
+seconds = 13
+cpu = 7093
+lpm = 401214
+deep = 1743
+tx = 38
+rx = 407700
+Leaf loop start!
+Leaf waiting for association!
+Leaf packet sent!
+ticks = 497073
+seconds = 15
+cpu = 7589
+lpm = 487754
+deep = 1869
+tx = 38
+rx = 494735
+Leaf loop start!
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/root_1.py

@@ -1,0 +1,285 @@
+cpu = 4534
+lpm = 38669
+deep = 933931
+tx = 170
+rx = 33552
+cpu = 7046
+lpm = 59103
+deep = 1424786
+tx = 255
+rx = 51186
+cpu = 9653
+lpm = 78902
+deep = 1902421
+tx = 340
+rx = 68338
+cpu = 12106
+lpm = 97378
+deep = 2351713
+tx = 425
+rx = 84471
+cpu = 14441
+lpm = 115324
+deep = 2783302
+tx = 510
+rx = 99967
+cpu = 16982
+lpm = 134453
+deep = 3243322
+tx = 595
+rx = 116503
+cpu = 19293
+lpm = 151180
+deep = 3648630
+tx = 680
+rx = 131063
+cpu = 21683
+lpm = 168459
+deep = 4064774
+tx = 765
+rx = 146008
+cpu = 24007
+lpm = 185347
+deep = 4472203
+tx = 850
+rx = 160643
+cpu = 26444
+lpm = 202455
+deep = 4888470
+tx = 935
+rx = 175599
+cpu = 28920
+lpm = 220622
+deep = 5326581
+tx = 1020
+rx = 191328
+cpu = 31462
+lpm = 240816
+deep = 5813060
+tx = 1105
+rx = 208793
+cpu = 34221
+lpm = 258941
+deep = 6257808
+tx = 1190
+rx = 224757
+cpu = 36647
+lpm = 277909
+deep = 6715810
+tx = 1275
+rx = 241208
+cpu = 39409
+lpm = 298575
+deep = 7215360
+tx = 1360
+rx = 259156
+cpu = 41747
+lpm = 315626
+deep = 7624903
+tx = 1445
+rx = 273864
+cpu = 44271
+lpm = 334864
+deep = 8087125
+tx = 1530
+rx = 290472
+cpu = 47045
+lpm = 355132
+deep = 8582473
+tx = 1615
+rx = 308250
+cpu = 49405
+lpm = 372225
+deep = 8994245
+tx = 1700
+rx = 323040
+cpu = 51753
+lpm = 388792
+deep = 9395088
+tx = 1785
+rx = 337421
+cpu = 54165
+lpm = 407442
+deep = 9844247
+tx = 1870
+rx = 353541
+cpu = 56476
+lpm = 423932
+deep = 10242911
+tx = 1955
+rx = 367852
+cpu = 58786
+lpm = 439928
+deep = 10632894
+tx = 2040
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/root_16.py

@@ -1,0 +1,309 @@
+cpu = 13838
+lpm = 109252
+deep = 2631707
+tx = 510
+rx = 94517
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 57953
+Link-layer address: 0012.4b00.1932.e261
+Zolertia RE-Mote revision B platform
+cpu = 2096
+lpm = 19391
+deep = 469370
+tx = 85
+rx = 16845
+cpu = 4753
+lpm = 39968
+deep = 964526
+tx = 170
+rx = 34636
+cpu = 7078
+lpm = 56977
+deep = 1374124
+tx = 255
+rx = 49340
+cpu = 9509
+lpm = 74693
+deep = 1805849
+tx = 340
+rx = 64841
+cpu = 11843
+lpm = 93777
+deep = 2261532
+tx = 425
+rx = 81204
+cpu = 14543
+lpm = 114546
+deep = 2761041
+tx = 510
+rx = 99144
+cpu = 16866
+lpm = 131443
+deep = 3170753
+tx = 595
+rx = 113857
+cpu = 19564
+lpm = 152017
+deep = 3665872
+tx = 680
+rx = 131622
+cpu = 21941
+lpm = 170368
+deep = 4106189
+tx = 765
+rx = 147425
+cpu = 24338
+lpm = 187862
+deep = 4531288
+tx = 850
+rx = 162684
+cpu = 26872
+lpm = 206853
+deep = 4989157
+tx = 935
+rx = 179128
+cpu = 29230
+lpm = 224964
+deep = 5427442
+tx = 1020
+rx = 194869
+cpu = 32018
+lpm = 243571
+deep = 5883147
+tx = 1105
+rx = 211230
+cpu = 34382
+lpm = 261767
+deep = 6319047
+tx = 1190
+rx = 226877
+cpu = 37127
+lpm = 281748
+deep = 6805536
+tx = 1275
+rx = 244343
+cpu = 39708
+lpm = 301377
+deep = 7281071
+tx = 1360
+rx = 261406
+cpu = 41894
+lpm = 317688
+deep = 7668569
+tx = 1445
+rx = 275334
+cpu = 44508
+lpm = 336045
+deep = 8115525
+tx = 1530
+rx = 291365
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/root_4.py

@@ -1,0 +1,287 @@
+Starting Contiki-NG-v1.0-121-g2657a648e-dirty
+- Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 57953
+Link-layer address: 0012.4b00.1932.e261
+Zolertia RE-Mote revision B platform
+Root going to sleep![INFO: Main      - Routing: nullrouting
+- Net: nullnet
+- MAC: TSCH
+- 802.15.4 PANID: 0xabcd
+- 802.15.4 TSCH default hopping sequence length: 1
+Node ID: 57953
+Link-layer address: 0012.4b00.1932.e261
+Zolertia RE-Mote revision B platform
+cpu = 2099
+lpm = 18098
+deep = 440841
+tx = 85
+rx = 15825
+cpu = 4464
+lpm = 35587
+deep = 865977
+tx = 170
+rx = 31090
+cpu = 6647
+lpm = 51974
+deep = 1262576
+tx = 255
+rx = 45333
+cpu = 8896
+lpm = 68193
+deep = 1654691
+tx = 340
+rx = 59425
+cpu = 11556
+lpm = 87721
+deep = 2130249
+tx = 425
+rx = 76507
+cpu = 13732
+lpm = 103836
+deep = 2517953
+tx = 510
+rx = 90425
+cpu = 16574
+lpm = 123235
+deep = 2995753
+tx = 595
+rx = 107585
+cpu = 18749
+lpm = 140627
+deep = 3414294
+tx = 680
+rx = 122634
+cpu = 21426
+lpm = 161319
+deep = 3916195
+tx = 765
+rx = 140660
+cpu = 23578
+lpm = 176984
+deep = 4292905
+tx = 850
+rx = 154182
+cpu = 25716
+lpm = 192563
+deep = 4669714
+tx = 935
+rx = 167712
+cpu = 28067
+lpm = 210674
+deep = 5108006
+tx = 1020
+rx = 183443
+cpu = 30292
+lpm = 228338
+deep = 5530812
+tx = 1105
+rx = 198638
+cpu = 32680
+lpm = 246004
+deep = 5958042
+tx = 1190
+rx = 213992
+cpu = 35337
+lpm = 266435
+deep = 6451050
+tx = 1275
+rx = 231707
+cpu = 37616
[…]

### 2021-01-21 examples/task2/plotting/plot.py

@@ -1,0 +1,20 @@
+import os 
+
+d = 'data/'
+for entry in os.scandir(d):
+	if (entry.is_dir()):
+		for e in os.scandir(entry):
+			# Descend into data_## directories
+			if e.is_file():
+				with open(e.path, 'r') as f:
+					lines = f.readlines()
+				i = 0
+				while i < len(lines):
+					if '[' not in lines[i] or '/dev/ttyUSB' in lines[i] or 'INCOMING PACKET RECEIVED' in lines[i]:
+						del lines[i]
+						continue
+					lines[i] = lines[i].split('] ')[1]
+					i += 1
+				with open(e.path, 'w') as f:
+					f.writelines(lines)
+

### 2021-01-21 examples/task2/root.sh

@@ -1,6 +1,10 @@
 #!/bin/bash
 # Touch the file so Make will definitely pick up changes
 touch root_app.c
+# Also touch tsch files. We change behaviour with command-line defines, so these are important
+touch ../../os/net/mac/tsch/tsch.c
+touch ../../os/net/mac/tsch/tsch.h
+touch ../../os/net/mac/tsch/tsch-conf.h
 
 if [ -e /dev/ttyUSB0 ]; then
 	echo "Installing root onto port 0!"

### 2021-01-21 examples/task2/root_app.c

@@ -33,6 +33,8 @@ PROCESS(root_app, "ROOT_APP");
 PROCESS_THREAD(root_app, ev, data)
 {
 	PROCESS_BEGIN();
+	LOG_INFO("Root started with channel hopping sequence size: %i\n", sizeof(TSCH_DEFAULT_HOPPING_SEQUENCE) / sizeof(TSCH_DEFAULT_HOPPING_SEQUENCE[0]));
+	LOG_INFO("With EB period = %i / 128 seconds\n", TSCH_EB_PERIOD);
 	// Root node in the task2 scenario. 
 	{
 		// Perform interface and energy resets/setup
@@ -66,6 +68,8 @@ void input_callback(const void *data, uint16_t len,
 	// For all other iterations, we should log information
 	// Time is recorded on the leaf side, we only care about energy.
 	logEnergySerial();
+	// Reset after logging
+	resetEnergy();
 	if (buffer == TASK2_ITERATIONCOUNT) {
 		done = true;
 		root_app.needspoll = true;

### 2021-01-21 examples/task3/plotting/data/data100m.py

@@ -35,10 +35,10 @@ def_cpu_deepsleep_time_coordinator = 1763852
 def_radio_rx_time_coordinator = 2419
 def_radio_tx_time_coordinator = 143130
 
-low_cpu_time_coordinator = 55394
-low_cpu_sleep_time_coordinator = 356345
-low_cpu_deepsleep_time_coordinator = 3554156
-low_radio_rx_time_coordinator = 4145
-low_radio_tx_time_coordinator = 286998
+low_cpu_time_coordinator = 30603
+low_cpu_sleep_time_coordinator = 183192
+low_cpu_deepsleep_time_coordinator = 1759362
+low_radio_rx_time_coordinator = 2071
+low_radio_tx_time_coordinator = 143498
 
 

### 2021-01-21 examples/task3/plotting/plot.py

@@ -3,7 +3,10 @@ from data import data1m, data10m, data100m, data50m
 from matplotlib.pyplot import *
 from statistics import mean
 
-ioff()
+def main():
+	#makeFigures()
+	computePowerStates()
+
 
 distances = ["1m", "10m", "50m", "100m"]
 powers = {"low_": "-7 dBm", "def_": "0 dBm", "high_": "7 dBm"}
@@ -12,157 +15,192 @@ prefixes = ["low_", "def_", "high_"]
 
 modules = [data1m, data10m, data50m, data100m]
 
-# Retransmissions Figure
-fig = figure()
-title("Transmission reliability per power level")
-xlabel("Distance (meters)")
-ylabel("Amount of unsuccessful transmissions over 60 packets")
-low_data = []
-high_data = []
-def_data = []
-for module in modules:
-	for prefix in prefixes:
-		numtx = [x - 1 for x in getattr(module, f"{prefix}numtx")]
-		numtx = [x if x != -1 else 8 for x in numtx]
-		eval(f"{prefix}data.append(sum(numtx))")
-plot(distances, high_data, 'ro-', label="TX power 7 dBm")
-plot(distances, def_data, 'go-', label="TX power 0 dBm")
-plot(distances, low_data, 'bo-', label="TX power -7 dBm")
-legend()
-#show()
-savefig("retransmissions.png")
-close(fig)
+def makeFigures():
+	# Retransmissions Figure
+	fig = figure()
+	title("Transmission reliability per power level")
+	xlabel("Distance (meters)")
+	ylabel("Amount of unsuccessful transmissions over 60 packets")
+	low_data = []
+	high_data = []
+	def_data = []
+	for module in modules:
+		for prefix in prefixes:
+			numtx = [x - 1 for x in getattr(module, f"{prefix}numtx")]
+			numtx = [x if x != -1 else 8 for x in numtx]
+			eval(f"{prefix}data.append(sum(numtx))")
+	plot(distances, high_data, 'ro-', label="TX power 7 dBm")
+	plot(distances, def_data, 'go-', label="TX power 0 dBm")
+	plot(distances, low_data, 'bo-', label="TX power -7 dBm")
+	legend()
+	#show()
+	savefig("retransmissions.png")
+	close(fig)
 
-# Latencies figure
-fig = figure()
-title("Latencies per power level")
[…]

### 2021-01-21 examples/task2/conf_my_app.h
Final submission

@@ -15,6 +15,6 @@
 #define TXPREFIX "tx = "
 #define RXPREFIX "rx = "
 #define MYFILENAME "UNIVANTW_SENSORNET_OUTPUT"
-#define TASK2_ITERATIONCOUNT 51
+#define TASK2_ITERATIONCOUNT 25
 
 #endif

### 2021-01-21 examples/task2/plotting/data.bak/data_16/leaf_1.py

@@ -1,533 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB1
-connecting to /dev/ttyUSB1 [OK]
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 58505
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e489
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: SENSORNETS] Leaf started with channel hopping sequence size: 1
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 502910
-[INFO: HELPERS   ] seconds = 15
-[INFO: HELPERS   ] cpu = 8089
-[INFO: HELPERS   ] lpm = 493230
-[INFO: HELPERS   ] deep = 1730
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 500719
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 462667
-[INFO: HELPERS   ] seconds = 14
-[INFO: HELPERS   ] cpu = 7692
-[INFO: HELPERS   ] lpm = 453349
-[INFO: HELPERS   ] deep = 1765
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 460436
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 412204
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_16/leaf_16.py

@@ -1,385 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB0
-connecting to /dev/ttyUSB0 [OK]
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 1864
-[INFO: HELPERS   ] lpm = 17543
-[INFO: HELPERS   ] deep = 425574
-[INFO: HELPERS   ] tx = 85
-[INFO: HELPERS   ] rx = 15262
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 57953
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: MyApp     ] Root going to sleep![INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 1904
-[INFO: HELPERS   ] lpm = 16141
-[INFO: HELPERS   ] deep = 394823
-[INFO: HELPERS   ] tx = 85
-[INFO: HELPERS   ] rx = 14165
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 4065
-[INFO: HELPERS   ] lpm = 32460
-[INFO: HELPERS   ] deep = 784633
-[INFO: HELPERS   ] tx = 170
-[INFO: HELPERS   ] rx = 28173
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 6538
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_16/leaf_4.py

@@ -1,543 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB1
-connecting to /dev/ttyUSB1 [OK]
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 499366
-[INFO: HELPERS   ] seconds = 15
-[INFO: HELPERS   ] cpu = 8231
-[INFO: HELPERS   ] lpm = 489416
-[INFO: HELPERS   ] deep = 1858
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 497041
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 58505
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e489
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: SENSORNETS] Leaf started with channel hopping sequence size: 4
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 502711
-[INFO: HELPERS   ] seconds = 15
-[INFO: HELPERS   ] cpu = 8153
-[INFO: HELPERS   ] lpm = 492910
-[INFO: HELPERS   ] deep = 1787
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 500461
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 460373
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_16/root_1.py

@@ -1,373 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB0
-connecting to /dev/ttyUSB0 [OK]
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 57953
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: MyApp     ] Root going to sleep![INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 2113
-[INFO: HELPERS   ] lpm = 18139
-[INFO: HELPERS   ] deep = 443081
-[INFO: HELPERS   ] tx = 85
-[INFO: HELPERS   ] rx = 15899
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 4312
-[INFO: HELPERS   ] lpm = 34584
-[INFO: HELPERS   ] deep = 837313
-[INFO: HELPERS   ] tx = 170
-[INFO: HELPERS   ] rx = 30055
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 6469
-[INFO: HELPERS   ] lpm = 50798
-[INFO: HELPERS   ] deep = 1224937
-[INFO: HELPERS   ] tx = 255
-[INFO: HELPERS   ] rx = 43972
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 8988
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_16/root_16.py

@@ -1,533 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB1
-connecting to /dev/ttyUSB1 [OK]
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 58505
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e489
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: SENSORNETS] Leaf started with channel hopping sequence size: 16
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 440761
-[INFO: HELPERS   ] seconds = 13
-[INFO: HELPERS   ] cpu = 7493
-[INFO: HELPERS   ] lpm = 431614
-[INFO: HELPERS   ] deep = 1793
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 438506
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 412203
-[INFO: HELPERS   ] seconds = 13
-[INFO: HELPERS   ] cpu = 6809
-[INFO: HELPERS   ] lpm = 403800
-[INFO: HELPERS   ] deep = 1733
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 410007
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 407617
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_16/root_4.py

@@ -1,373 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB0
-connecting to /dev/ttyUSB0 [OK]
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 57953
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: MyApp     ] Root going to sleep![INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 2244
-[INFO: HELPERS   ] lpm = 18258
-[INFO: HELPERS   ] deep = 440537
-[INFO: HELPERS   ] tx = 85
-[INFO: HELPERS   ] rx = 15794
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 4529
-[INFO: HELPERS   ] lpm = 34453
-[INFO: HELPERS   ] deep = 832640
-[INFO: HELPERS   ] tx = 170
-[INFO: HELPERS   ] rx = 29858
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 6950
-[INFO: HELPERS   ] lpm = 53136
-[INFO: HELPERS   ] deep = 1284049
-[INFO: HELPERS   ] tx = 255
-[INFO: HELPERS   ] rx = 46048
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 9295
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_32/leaf_1.py

@@ -1,545 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB1
-connecting to /dev/ttyUSB1 [OK]
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 58505
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e489
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: SENSORNETS] Leaf started with channel hopping sequence size: 1
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 58505
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e489
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: SENSORNETS] Leaf started with channel hopping sequence size: 1
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 458116
-[INFO: HELPERS   ] seconds = 14
-[INFO: HELPERS   ] cpu = 7392
-[INFO: HELPERS   ] lpm = 449127
-[INFO: HELPERS   ] deep = 1736
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_32/leaf_16.py

@@ -1,543 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB1
-connecting to /dev/ttyUSB1 [OK]
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 503965
-[INFO: HELPERS   ] seconds = 15
-[INFO: HELPERS   ] cpu = 8623
-[INFO: HELPERS   ] lpm = 493645
-[INFO: HELPERS   ] deep = 1836
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 501663
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 58505
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e489
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: SENSORNETS] Leaf started with channel hopping sequence size: 16
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 411149
-[INFO: HELPERS   ] seconds = 13
-[INFO: HELPERS   ] cpu = 6767
-[INFO: HELPERS   ] lpm = 402644
-[INFO: HELPERS   ] deep = 1877
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 408811
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 425965
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_32/root_1.py

@@ -1,364 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB0
-connecting to /dev/ttyUSB0 [OK]
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 57953
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: MyApp     ] Root going to sleep![INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 57953
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: MyApp     ] Root going to sleep![INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 2083
-[INFO: HELPERS   ] lpm = 17817
-[INFO: HELPERS   ] deep = 434255
-[INFO: HELPERS   ] tx = 85
-[INFO: HELPERS   ] rx = 15572
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_32/root_16.py

@@ -1,381 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB0
-connecting to /dev/ttyUSB0 [OK]
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 57953
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: MyApp     ] Root going to sleep![INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 1956
-[INFO: HELPERS   ] lpm = 16651
-[INFO: HELPERS   ] deep = 408023
-[INFO: HELPERS   ] tx = 85
-[INFO: HELPERS   ] rx = 14633
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 4538
-[INFO: HELPERS   ] lpm = 33826
-[INFO: HELPERS   ] deep = 824082
-[INFO: HELPERS   ] tx = 170
-[INFO: HELPERS   ] rx = 29597
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 6849
-[INFO: HELPERS   ] lpm = 50860
-[INFO: HELPERS   ] deep = 1229081
-[INFO: HELPERS   ] tx = 255
-[INFO: HELPERS   ] rx = 44150
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 9423
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_32/root_4.py

@@ -1,388 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB0
-connecting to /dev/ttyUSB0 [OK]
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 57953
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: MyApp     ] Root going to sleep![INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 57953
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: MyApp     ] Root going to sleep![INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 1779
-[INFO: HELPERS   ] lpm = 16453
-[INFO: HELPERS   ] deep = 399226
-[INFO: HELPERS   ] tx = 85
-[INFO: HELPERS   ] rx = 14315
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_4/leaf_1.py

@@ -1,511 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB1
-connecting to /dev/ttyUSB1 [OK]
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 501671
-[INFO: HELPERS   ] seconds = 15
-[INFO: HELPERS   ] cpu = 8249
-[INFO: HELPERS   ] lpm = 491716
-[INFO: HELPERS   ] deep = 1845
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 499360
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 474136
-[INFO: HELPERS   ] seconds = 14
-[INFO: HELPERS   ] cpu = 7896
-[INFO: HELPERS   ] lpm = 464409
-[INFO: HELPERS   ] deep = 1970
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 471727
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 513128
-[INFO: HELPERS   ] seconds = 16
-[INFO: HELPERS   ] cpu = 8242
-[INFO: HELPERS   ] lpm = 503230
-[INFO: HELPERS   ] deep = 1795
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 510866
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 499369
-[INFO: HELPERS   ] seconds = 15
-[INFO: HELPERS   ] cpu = 8097
-[INFO: HELPERS   ] lpm = 489553
-[INFO: HELPERS   ] deep = 1858
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 497044
-[INFO: SENSORNETS] Leaf loop start!
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_4/leaf_16.py

@@ -1,543 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB1
-connecting to /dev/ttyUSB1 [OK]
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 412207
-[INFO: HELPERS   ] seconds = 13
-[INFO: HELPERS   ] cpu = 6811
-[INFO: HELPERS   ] lpm = 403799
-[INFO: HELPERS   ] deep = 1736
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 410008
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 58505
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e489
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: SENSORNETS] Leaf started with channel hopping sequence size: 16
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 420894
-[INFO: HELPERS   ] seconds = 13
-[INFO: HELPERS   ] cpu = 7030
-[INFO: HELPERS   ] lpm = 412110
-[INFO: HELPERS   ] deep = 1893
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 418540
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 490191
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_4/root_1.py

@@ -1,345 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB0
-connecting to /dev/ttyUSB0 [OK]
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 4534
-[INFO: HELPERS   ] lpm = 38669
-[INFO: HELPERS   ] deep = 933931
-[INFO: HELPERS   ] tx = 170
-[INFO: HELPERS   ] rx = 33552
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 7046
-[INFO: HELPERS   ] lpm = 59103
-[INFO: HELPERS   ] deep = 1424786
-[INFO: HELPERS   ] tx = 255
-[INFO: HELPERS   ] rx = 51186
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 9653
-[INFO: HELPERS   ] lpm = 78902
-[INFO: HELPERS   ] deep = 1902421
-[INFO: HELPERS   ] tx = 340
-[INFO: HELPERS   ] rx = 68338
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 12106
-[INFO: HELPERS   ] lpm = 97378
-[INFO: HELPERS   ] deep = 2351713
-[INFO: HELPERS   ] tx = 425
-[INFO: HELPERS   ] rx = 84471
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 14441
-[INFO: HELPERS   ] lpm = 115324
-[INFO: HELPERS   ] deep = 2783302
-[INFO: HELPERS   ] tx = 510
-[INFO: HELPERS   ] rx = 99967
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 16982
-[INFO: HELPERS   ] lpm = 134453
-[INFO: HELPERS   ] deep = 3243322
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_4/root_16.py

@@ -1,373 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB0
-connecting to /dev/ttyUSB0 [OK]
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 13838
-[INFO: HELPERS   ] lpm = 109252
-[INFO: HELPERS   ] deep = 2631707
-[INFO: HELPERS   ] tx = 510
-[INFO: HELPERS   ] rx = 94517
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 57953
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: MyApp     ] Root going to sleep![INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 2096
-[INFO: HELPERS   ] lpm = 19391
-[INFO: HELPERS   ] deep = 469370
-[INFO: HELPERS   ] tx = 85
-[INFO: HELPERS   ] rx = 16845
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 4753
-[INFO: HELPERS   ] lpm = 39968
-[INFO: HELPERS   ] deep = 964526
-[INFO: HELPERS   ] tx = 170
-[INFO: HELPERS   ] rx = 34636
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 7078
[…]

### 2021-01-21 examples/task2/plotting/data.bak/data_4/root_4.py

@@ -1,346 +1,0 @@
-using saved target 'zoul'
-rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB0
-connecting to /dev/ttyUSB0 [OK]
-[INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 57953
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: MyApp     ] Root going to sleep![INFO: Main      ] Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-[INFO: Main      ] - Routing: nullrouting
-[INFO: Main      ] - Net: nullnet
-[INFO: Main      ] - MAC: TSCH
-[INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
-[INFO: Main      ] Node ID: 57953
-[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
-[INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: MyApp     ] Root going to sleep![INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
-[INFO: HELPERS   ] cpu = 2099
-[INFO: HELPERS   ] lpm = 18098
-[INFO: HELPERS   ] deep = 440841
-[INFO: HELPERS   ] tx = 85
-[INFO: HELPERS   ] rx = 15825
-[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
[…]

### 2021-01-21 examples/task2/plotting/data/data_1/leaf_1.py

@@ -6,11 +6,11 @@ connecting to /dev/ttyUSB1 [OK]
 [INFO: Main      ] - Net: nullnet
 [INFO: Main      ] - MAC: TSCH
 [INFO: Main      ] - 802.15.4 PANID: 0xabcd
-[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 4
+[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
 [INFO: Main      ] Node ID: 58505
 [INFO: Main      ] Link-layer address: 0012.4b00.1932.e489
 [INFO: Zoul      ] Zolertia RE-Mote revision B platform
-[INFO: SENSORNETS] Leaf started with channel hopping sequence size: 4
+[INFO: SENSORNETS] Leaf started with channel hopping sequence size: 1
 [INFO: SENSORNETS] With EB period = 128 / 128 seconds
 [INFO: SENSORNETS] Leaf loop start!
 [INFO: SENSORNETS] Leaf waiting for association!
@@ -19,250 +19,250 @@ connecting to /dev/ttyUSB1 [OK]
 [INFO: SENSORNETS] Leaf loop start!
 [INFO: SENSORNETS] Leaf waiting for association!
 [INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 123607
-[INFO: HELPERS   ] seconds = 4
-[INFO: HELPERS   ] cpu = 1990
-[INFO: HELPERS   ] lpm = 120011
-[INFO: HELPERS   ] deep = 1744
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 121396
-[INFO: SENSORNETS] Leaf loop start!
-[INFO: SENSORNETS] Leaf waiting for association!
-[INFO: SENSORNETS] Leaf packet sent!
-[INFO: HELPERS   ] ticks = 478725
-[INFO: HELPERS   ] seconds = 15
-[INFO: HELPERS   ] cpu = 7770
-[INFO: HELPERS   ] lpm = 469145
-[INFO: HELPERS   ] deep = 1950
-[INFO: HELPERS   ] tx = 38
-[INFO: HELPERS   ] rx = 476313
-[INFO: SENSORNETS] Leaf loop start!
[…]

### 2021-01-21 examples/task2/plotting/data/data_1/leaf_4.py

@@ -1,0 +1,255 @@
+[INFO: SENSORNETS] Leaf started with channel hopping sequence size: 4
+[INFO: SENSORNETS] With EB period = 128 / 128 seconds
+[INFO: SENSORNETS] Leaf loop start!
+[INFO: SENSORNETS] Leaf waiting for association!
+[INFO: SENSORNETS] Leaf packet sent!
+[INFO: SENSORNETS] First iteration send_callback. Not recording data.
+[INFO: SENSORNETS] Leaf loop start!
+[INFO: SENSORNETS] Leaf waiting for association!
+[INFO: SENSORNETS] Leaf packet sent!
+[INFO: HELPERS   ] ticks = 63970
+[INFO: HELPERS   ] seconds = 2
+[INFO: HELPERS   ] cpu = 1151
+[INFO: HELPERS   ] lpm = 61199
+[INFO: HELPERS   ] deep = 1755
+[INFO: HELPERS   ] tx = 38
+[INFO: HELPERS   ] rx = 61752
+[INFO: SENSORNETS] Leaf loop start!
+[INFO: SENSORNETS] Leaf waiting for association!
+[INFO: SENSORNETS] Leaf packet sent!
+[INFO: HELPERS   ] ticks = 81913
+[INFO: HELPERS   ] seconds = 2
+[INFO: HELPERS   ] cpu = 1365
+[INFO: HELPERS   ] lpm = 78754
+[INFO: HELPERS   ] deep = 1929
+[INFO: HELPERS   ] tx = 38
+[INFO: HELPERS   ] rx = 79522
+[INFO: SENSORNETS] Leaf loop start!
+[INFO: SENSORNETS] Leaf waiting for association!
+[INFO: SENSORNETS] Leaf packet sent!
+[INFO: HELPERS   ] ticks = 118613
+[INFO: HELPERS   ] seconds = 4
+[INFO: HELPERS   ] cpu = 1844
+[INFO: HELPERS   ] lpm = 115143
+[INFO: HELPERS   ] deep = 1764
+[INFO: HELPERS   ] tx = 38
+[INFO: HELPERS   ] rx = 116387
+[INFO: SENSORNETS] Leaf loop start!
+[INFO: SENSORNETS] Leaf waiting for association!
+[INFO: SENSORNETS] Leaf packet sent!
[…]

### 2021-01-21 examples/task2/plotting/data/data_1/leaf_8.py

@@ -1,0 +1,257 @@
+[INFO: Zoul      ] Zolertia RE-Mote revision B platform
+[INFO: SENSORNETS] Leaf started with channel hopping sequence size: 1
+[INFO: SENSORNETS] With EB period = 1024 / 128 seconds
+[INFO: SENSORNETS] Leaf loop start!
+[INFO: SENSORNETS] Leaf waiting for association!
+[INFO: SENSORNETS] Leaf packet sent!
+[INFO: SENSORNETS] First iteration send_callback. Not recording data.
+[INFO: SENSORNETS] Leaf loop start!
+[INFO: SENSORNETS] Leaf waiting for association!
+[INFO: SENSORNETS] Leaf packet sent!
+[INFO: HELPERS   ] ticks = 236001
+[INFO: HELPERS   ] seconds = 7
+[INFO: HELPERS   ] cpu = 3655
+[INFO: HELPERS   ] lpm = 230730
+[INFO: HELPERS   ] deep = 1754
+[INFO: HELPERS   ] tx = 38
+[INFO: HELPERS   ] rx = 233785
+[INFO: SENSORNETS] Leaf loop start!
+[INFO: SENSORNETS] Leaf waiting for association!
+[INFO: SENSORNETS] Leaf packet sent!
+[INFO: HELPERS   ] ticks = 208063
+[INFO: HELPERS   ] seconds = 6
+[INFO: HELPERS   ] cpu = 3255
+[INFO: HELPERS   ] lpm = 203067
+[INFO: HELPERS   ] deep = 1879
+[INFO: HELPERS   ] tx = 38
+[INFO: HELPERS   ] rx = 205721
+[INFO: SENSORNETS] Leaf loop start!
+[INFO: SENSORNETS] Leaf waiting for association!
+[INFO: SENSORNETS] Leaf packet sent!
+[INFO: HELPERS   ] ticks = 237880
+[INFO: HELPERS   ] seconds = 7
+[INFO: HELPERS   ] cpu = 3635
+[INFO: HELPERS   ] lpm = 232638
+[INFO: HELPERS   ] deep = 1745
+[INFO: HELPERS   ] tx = 38
+[INFO: HELPERS   ] rx = 235672
+[INFO: SENSORNETS] Leaf loop start!
+[INFO: SENSORNETS] Leaf waiting for association!
[…]

### 2021-01-21 examples/task2/plotting/data/data_1/root_1.py

@@ -1,0 +1,169 @@
+
+[INFO: Main      ] Starting Contiki-NG-v1.0-131-gfed8f5d5b-dirty
+[INFO: Main      ] - Routing: nullrouting
+[INFO: Main      ] - Net: nullnet
+[INFO: Main      ] - MAC: TSCH
+[INFO: Main      ] - 802.15.4 PANID: 0xabcd
+[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
+[INFO: Main      ] Node ID: 57953
+[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
+[INFO: Zoul      ] Zolertia RE-Mote revision B platform
+[INFO: MyApp     ] Root started with channel hopping sequence size: 1
+[INFO: MyApp     ] With EB period = 128 / 128 seconds
+[INFO: MyApp     ] Root going to sleep![INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: HELPERS   ] cpu = 343
+[INFO: HELPERS   ] lpm = 1124
+[INFO: HELPERS   ] deep = 26049
+[INFO: HELPERS   ] tx = 85
+[INFO: HELPERS   ] rx = 916
+[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: HELPERS   ] cpu = 352
+[INFO: HELPERS   ] lpm = 1293
+[INFO: HELPERS   ] deep = 27760
+[INFO: HELPERS   ] tx = 85
+[INFO: HELPERS   ] rx = 994
+[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: HELPERS   ] cpu = 370
+[INFO: HELPERS   ] lpm = 1618
+[INFO: HELPERS   ] deep = 32001
+[INFO: HELPERS   ] tx = 85
+[INFO: HELPERS   ] rx = 1151
+[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: HELPERS   ] cpu = 352
[…]

### 2021-01-21 examples/task2/plotting/data/data_1/root_8.py

@@ -1,0 +1,165 @@
+using saved target 'zoul'
+rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB0
+connecting to /dev/ttyUSB0 [OK]
+[INFO: Main      ] Starting Contiki-NG-v1.0-131-gfed8f5d5b-dirty
+[INFO: Main      ] - Routing: nullrouting
+[INFO: Main      ] - Net: nullnet
+[INFO: Main      ] - MAC: TSCH
+[INFO: Main      ] - 802.15.4 PANID: 0xabcd
+[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 1
+[INFO: Main      ] Node ID: 57953
+[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
+[INFO: Zoul      ] Zolertia RE-Mote revision B platform
+[INFO: MyApp     ] Root started with channel hopping sequence size: 1
+[INFO: MyApp     ] With EB period = 1024 / 128 seconds
+[INFO: MyApp     ] Root going to sleep![INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: HELPERS   ] cpu = 1045
+[INFO: HELPERS   ] lpm = 9380
+[INFO: HELPERS   ] deep = 225823
+[INFO: HELPERS   ] tx = 85
+[INFO: HELPERS   ] rx = 8079
+[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: HELPERS   ] cpu = 1245
+[INFO: HELPERS   ] lpm = 8214
+[INFO: HELPERS   ] deep = 198849
+[INFO: HELPERS   ] tx = 85
+[INFO: HELPERS   ] rx = 7134
+[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: HELPERS   ] cpu = 1187
+[INFO: HELPERS   ] lpm = 9529
+[INFO: HELPERS   ] deep = 227410
+[INFO: HELPERS   ] tx = 85
[…]

### 2021-01-21 examples/task2/plotting/data/data_16/leaf_1.py

@@ -1,530 +1,0 @@
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 58505
-Link-layer address: 0012.4b00.1932.e489
-Zolertia RE-Mote revision B platform
-Leaf started with channel hopping sequence size: 1
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 502910
-seconds = 15
-cpu = 8089
-lpm = 493230
-deep = 1730
-tx = 38
-rx = 500719
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 462667
-seconds = 14
-cpu = 7692
-lpm = 453349
-deep = 1765
-tx = 38
-rx = 460436
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 412204
-seconds = 13
-cpu = 6870
-lpm = 403738
-deep = 1735
-tx = 38
-rx = 410005
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 405322
-seconds = 12
-cpu = 6763
-lpm = 396934
-deep = 1764
-tx = 38
-rx = 403093
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 464961
-seconds = 14
-cpu = 7696
-lpm = 455647
-deep = 1757
-tx = 38
-rx = 462737
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 414497
-seconds = 13
-cpu = 6924
-lpm = 405733
-deep = 1979
-tx = 38
-rx = 412092
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 439729
-seconds = 13
-cpu = 7266
-lpm = 430733
-deep = 1869
-tx = 38
-rx = 437395
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 522306
-seconds = 16
-cpu = 8591
-lpm = 512099
-deep = 1755
-tx = 38
-rx = 520084
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
[…]

### 2021-01-21 examples/task2/plotting/data/data_16/leaf_16.py

@@ -1,319 +1,0 @@
-cpu = 1864
-lpm = 17543
-deep = 425574
-tx = 85
-rx = 15262
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 57953
-Link-layer address: 0012.4b00.1932.e261
-Zolertia RE-Mote revision B platform
-cpu = 1904
-lpm = 16141
-deep = 394823
-tx = 85
-rx = 14165
-cpu = 4065
-lpm = 32460
-deep = 784633
-tx = 170
-rx = 28173
-cpu = 6538
-lpm = 49541
-deep = 1198599
-tx = 255
-rx = 43036
-cpu = 8969
-lpm = 68730
-deep = 1663258
-tx = 340
-rx = 59717
-cpu = 11305
-lpm = 85429
-deep = 2066272
-tx = 425
-rx = 74187
-cpu = 13817
-lpm = 105345
-deep = 2548473
-tx = 510
-rx = 91487
-cpu = 16539
-lpm = 125325
-deep = 3034984
-tx = 595
-rx = 108950
-cpu = 18839
-lpm = 142778
-deep = 3455634
-tx = 680
-rx = 124046
-cpu = 21283
-lpm = 160897
-deep = 3891527
-tx = 765
-rx = 139691
-cpu = 23590
-lpm = 176974
-deep = 4283728
-tx = 850
-rx = 153763
-cpu = 26001
-lpm = 195627
-deep = 4735178
-tx = 935
-rx = 169959
-cpu = 28225
-lpm = 212103
-deep = 5133944
-tx = 1020
-rx = 184278
-cpu = 30827
-lpm = 230641
-deep = 5587611
-tx = 1105
-rx = 200563
-cpu = 33525
-lpm = 250890
-deep = 6078466
-tx = 1190
-rx = 218194
-cpu = 35809
-lpm = 266772
-deep = 6461708
-tx = 1275
-rx = 231949
-cpu = 38148
-lpm = 283793
-deep = 6871280
-tx = 1360
-rx = 246657
-cpu = 40875
-lpm = 304303
-deep = 7366434
-tx = 1445
-rx = 264439
-cpu = 43248
-lpm = 321298
-deep = 7775998
-tx = 1530
-rx = 279150
[…]

### 2021-01-21 examples/task2/plotting/data/data_16/leaf_4.py

@@ -1,540 +1,0 @@
-Leaf packet sent!
-ticks = 499366
-seconds = 15
-cpu = 8231
-lpm = 489416
-deep = 1858
-tx = 38
-rx = 497041
-Leaf loop start!
-Leaf waiting for association!
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 58505
-Link-layer address: 0012.4b00.1932.e489
-Zolertia RE-Mote revision B platform
-Leaf started with channel hopping sequence size: 4
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 502711
-seconds = 15
-cpu = 8153
-lpm = 492910
-deep = 1787
-tx = 38
-rx = 500461
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 460373
-seconds = 14
-cpu = 7612
-lpm = 451124
-deep = 1776
-tx = 38
-rx = 458133
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 409911
-seconds = 13
-cpu = 6787
-lpm = 401517
-deep = 1746
-tx = 38
-rx = 407702
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 471840
-seconds = 14
-cpu = 7802
-lpm = 462199
-deep = 1978
-tx = 38
-rx = 469434
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 416794
-seconds = 13
-cpu = 6967
-lpm = 407994
-deep = 1972
-tx = 38
-rx = 414387
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 506247
-seconds = 15
-cpu = 8375
-lpm = 496186
-deep = 1825
-tx = 38
-rx = 503954
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 471842
-seconds = 14
-cpu = 7839
-lpm = 462161
-deep = 1981
-tx = 38
-rx = 469433
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
[…]

### 2021-01-21 examples/task2/plotting/data/data_16/root_1.py

@@ -1,309 +1,0 @@
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 57953
-Link-layer address: 0012.4b00.1932.e261
-Zolertia RE-Mote revision B platform
-cpu = 2113
-lpm = 18139
-deep = 443081
-tx = 85
-rx = 15899
-cpu = 4312
-lpm = 34584
-deep = 837313
-tx = 170
-rx = 30055
-cpu = 6469
-lpm = 50798
-deep = 1224937
-tx = 255
-rx = 43972
-cpu = 8988
-lpm = 69038
-deep = 1669827
-tx = 340
-rx = 59941
-cpu = 11192
-lpm = 85478
-deep = 2066337
-tx = 425
-rx = 74181
-cpu = 13476
-lpm = 102950
-deep = 2486983
-tx = 510
-rx = 89289
-cpu = 16162
-lpm = 123706
-deep = 2986519
-tx = 595
-rx = 107230
-cpu = 18520
-lpm = 142112
-deep = 3426802
-tx = 680
-rx = 123040
-cpu = 20833
-lpm = 159683
-deep = 3851905
-tx = 765
-rx = 138292
-cpu = 23165
-lpm = 175957
-deep = 4248471
-tx = 850
-rx = 152523
-cpu = 25472
-lpm = 193476
-deep = 4671339
-tx = 935
-rx = 167694
-cpu = 27832
-lpm = 211578
-deep = 5107337
-tx = 1020
-rx = 183343
-cpu = 30159
-lpm = 227734
-deep = 5501730
-tx = 1105
-rx = 197490
-cpu = 32573
-lpm = 246548
-deep = 5953017
-tx = 1190
-rx = 213701
-cpu = 35404
-lpm = 266566
-deep = 6443971
-tx = 1275
-rx = 231323
-cpu = 37697
-lpm = 283879
-deep = 6860179
-tx = 1360
-rx = 246264
-cpu = 40049
-lpm = 301950
-deep = 7293920
-tx = 1445
-rx = 261838
-cpu = 42602
-lpm = 320851
-deep = 7751861
-tx = 1530
-rx = 278275
-cpu = 45056
-lpm = 338929
-deep = 8187788
-tx = 1615
[…]

### 2021-01-21 examples/task2/plotting/data/data_32/leaf_1.py

@@ -1,542 +1,0 @@
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 58505
-Link-layer address: 0012.4b00.1932.e489
-Zolertia RE-Mote revision B platform
-Leaf started with channel hopping sequence size: 1
-Leaf loop start!
-Leaf waiting for association!
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 58505
-Link-layer address: 0012.4b00.1932.e489
-Zolertia RE-Mote revision B platform
-Leaf started with channel hopping sequence size: 1
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 458116
-seconds = 14
-cpu = 7392
-lpm = 449127
-deep = 1736
-tx = 38
-rx = 455919
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 453490
-seconds = 14
-cpu = 7801
-lpm = 444024
-deep = 1804
-tx = 38
-rx = 451220
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 446612
-seconds = 14
-cpu = 7439
-lpm = 437473
-deep = 1839
-tx = 38
-rx = 444308
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 481015
-seconds = 15
-cpu = 7938
-lpm = 471278
-deep = 1938
-tx = 38
-rx = 478610
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 458082
-seconds = 14
-cpu = 7620
-lpm = 448813
-deep = 1788
-tx = 38
-rx = 455828
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 476428
-seconds = 15
-cpu = 7771
-lpm = 466838
-deep = 1958
-tx = 38
-rx = 474021
-Leaf loop start!
[…]

### 2021-01-21 examples/task2/plotting/data/data_32/leaf_4.py

@@ -1,530 +1,0 @@
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 58505
-Link-layer address: 0012.4b00.1932.e489
-Zolertia RE-Mote revision B platform
-Leaf started with channel hopping sequence size: 4
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 83068
-seconds = 3
-cpu = 1847
-lpm = 79625
-deep = 1730
-tx = 38
-rx = 80880
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 416804
-seconds = 13
-cpu = 7231
-lpm = 407744
-deep = 1968
-tx = 38
-rx = 414396
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 442023
-seconds = 13
-cpu = 6771
-lpm = 433531
-deep = 1860
-tx = 38
-rx = 439696
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 520010
-seconds = 16
-cpu = 8319
-lpm = 510067
-deep = 1763
-tx = 38
-rx = 517780
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 428262
-seconds = 13
-cpu = 7119
-lpm = 419361
-deep = 1921
-tx = 38
-rx = 425876
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 419083
-seconds = 13
-cpu = 7024
-lpm = 410240
-deep = 1958
-tx = 38
-rx = 416676
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 503957
-seconds = 15
-cpu = 8050
-lpm = 494207
-deep = 1839
-tx = 38
-rx = 501653
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 474134
-seconds = 14
-cpu = 7744
-lpm = 464560
-deep = 1969
-tx = 38
-rx = 471727
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
[…]

### 2021-01-21 examples/task2/plotting/data/data_32/root_16.py

@@ -1,314 +1,0 @@
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 57953
-Link-layer address: 0012.4b00.1932.e261
-Zolertia RE-Mote revision B platform
-cpu = 1956
-lpm = 16651
-deep = 408023
-tx = 85
-rx = 14633
-cpu = 4538
-lpm = 33826
-deep = 824082
-tx = 170
-rx = 29597
-cpu = 6849
-lpm = 50860
-deep = 1229081
-tx = 255
-rx = 44150
-cpu = 9423
-lpm = 70528
-deep = 1706880
-tx = 340
-rx = 61306
-cpu = 11902
-lpm = 87752
-deep = 2127577
-tx = 425
-rx = 76404
-cpu = 14054
-lpm = 104674
-deep = 2530556
-tx = 510
-rx = 90876
-cpu = 16311
-lpm = 120525
-deep = 2916149
-tx = 595
-rx = 104707
-cpu = 18824
-lpm = 138902
-deep = 3360894
-tx = 680
-rx = 120665
-cpu = 21046
-lpm = 155212
-deep = 3755238
-tx = 765
-rx = 134808
-cpu = 23318
-lpm = 171422
-deep = 4145046
-tx = 850
-rx = 148806
-cpu = 25971
-lpm = 189686
-deep = 4589761
-tx = 935
-rx = 164782
-cpu = 28388
-lpm = 208645
-deep = 5047780
-tx = 1020
-rx = 181224
-cpu = 30624
-lpm = 225592
-deep = 5452944
-tx = 1105
-rx = 195786
-cpu = 33220
-lpm = 244140
-deep = 5902021
-tx = 1190
-rx = 211907
-cpu = 35453
-lpm = 260674
-deep = 6300717
-tx = 1275
-rx = 226206
-cpu = 37657
-lpm = 276748
-deep = 6690729
-tx = 1360
-rx = 240200
-cpu = 40192
-lpm = 293653
-deep = 7102515
-tx = 1445
-rx = 254993
-cpu = 42639
-lpm = 313024
-deep = 7569269
-tx = 1530
-rx = 271762
-cpu = 44950
-lpm = 329624
-deep = 7972409
-tx = 1615
[…]

### 2021-01-21 examples/task2/plotting/data/data_32/root_4.py

@@ -1,322 +1,0 @@
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 57953
-Link-layer address: 0012.4b00.1932.e261
-Zolertia RE-Mote revision B platform
-Root going to sleep![INFO: Main      - Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 57953
-Link-layer address: 0012.4b00.1932.e261
-Zolertia RE-Mote revision B platform
-cpu = 1779
-lpm = 16453
-deep = 399226
-tx = 85
-rx = 14315
-cpu = 4060
-lpm = 33926
-deep = 822168
-tx = 170
-rx = 29508
-cpu = 6798
-lpm = 54409
-deep = 1319629
-tx = 255
-rx = 47366
-cpu = 9117
-lpm = 71325
-deep = 1729329
-tx = 340
-rx = 62074
-cpu = 11401
-lpm = 87777
-deep = 2130349
-tx = 425
-rx = 76474
-cpu = 13998
-lpm = 107762
-deep = 2612396
-tx = 510
-rx = 93809
-cpu = 16473
-lpm = 126459
-deep = 3066031
-tx = 595
-rx = 110099
-cpu = 19208
-lpm = 146721
-deep = 3556836
-tx = 680
-rx = 127730
-cpu = 21590
-lpm = 165330
-deep = 4003772
-tx = 765
-rx = 143790
-cpu = 24211
-lpm = 184299
-deep = 4461578
-tx = 850
-rx = 160245
-cpu = 26729
-lpm = 203784
-deep = 4930439
-tx = 935
-rx = 177101
-cpu = 29067
-lpm = 220431
-deep = 5331213
-tx = 1020
-rx = 191490
-cpu = 31640
-lpm = 240277
-deep = 5811128
-tx = 1105
-rx = 208723
-cpu = 34160
-lpm = 259089
-deep = 6264602
-tx = 1190
-rx = 225007
-cpu = 36613
-lpm = 278121
-deep = 6722515
-tx = 1275
-rx = 241441
-cpu = 39199
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/leaf_16.py

@@ -1,540 +1,0 @@
-Leaf packet sent!
-ticks = 412207
-seconds = 13
-cpu = 6811
-lpm = 403799
-deep = 1736
-tx = 38
-rx = 410008
-Leaf loop start!
-Leaf waiting for association!
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 58505
-Link-layer address: 0012.4b00.1932.e489
-Zolertia RE-Mote revision B platform
-Leaf started with channel hopping sequence size: 16
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 420894
-seconds = 13
-cpu = 7030
-lpm = 412110
-deep = 1893
-tx = 38
-rx = 418540
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 490191
-seconds = 15
-cpu = 8086
-lpm = 480345
-deep = 1899
-tx = 38
-rx = 487826
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 517718
-seconds = 16
-cpu = 8417
-lpm = 507665
-deep = 1775
-tx = 38
-rx = 515478
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 428259
-seconds = 13
-cpu = 7118
-lpm = 419362
-deep = 1918
-tx = 38
-rx = 425877
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 451200
-seconds = 14
-cpu = 7474
-lpm = 442047
-deep = 1818
-tx = 38
-rx = 448918
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 476428
-seconds = 15
-cpu = 7891
-lpm = 466717
-deep = 1959
-tx = 38
-rx = 474021
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 522305
-seconds = 16
-cpu = 8625
-lpm = 512063
-deep = 1756
-tx = 38
-rx = 520081
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/leaf_4.py

@@ -1,542 +1,268 @@
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 58505
-Link-layer address: 0012.4b00.1932.e489
-Zolertia RE-Mote revision B platform
-Leaf started with channel hopping sequence size: 4
-Leaf loop start!
-Leaf waiting for association!
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 58505
-Link-layer address: 0012.4b00.1932.e489
-Zolertia RE-Mote revision B platform
-Leaf started with channel hopping sequence size: 4
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 498105
-seconds = 15
-cpu = 7972
-lpm = 488483
-deep = 1789
-tx = 38
-rx = 495855
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 460372
-seconds = 14
-cpu = 7911
-lpm = 450826
-deep = 1774
-tx = 38
-rx = 458133
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 444318
-seconds = 14
-cpu = 7681
-lpm = 434928
-deep = 1848
-tx = 38
-rx = 442005
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 414496
-seconds = 13
-cpu = 7199
-lpm = 405458
-deep = 1978
-tx = 38
-rx = 412091
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 409911
-seconds = 13
-cpu = 7093
-lpm = 401214
-deep = 1743
-tx = 38
-rx = 407700
-Leaf loop start!
-Leaf waiting for association!
-Leaf packet sent!
-ticks = 497073
-seconds = 15
-cpu = 7589
-lpm = 487754
-deep = 1869
-tx = 38
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/root_1.py

@@ -1,285 +1,165 @@
-cpu = 4534
-lpm = 38669
-deep = 933931
-tx = 170
-rx = 33552
-cpu = 7046
-lpm = 59103
-deep = 1424786
-tx = 255
-rx = 51186
-cpu = 9653
-lpm = 78902
-deep = 1902421
-tx = 340
-rx = 68338
-cpu = 12106
-lpm = 97378
-deep = 2351713
-tx = 425
-rx = 84471
-cpu = 14441
-lpm = 115324
-deep = 2783302
-tx = 510
-rx = 99967
-cpu = 16982
-lpm = 134453
-deep = 3243322
-tx = 595
-rx = 116503
-cpu = 19293
-lpm = 151180
-deep = 3648630
-tx = 680
-rx = 131063
-cpu = 21683
-lpm = 168459
-deep = 4064774
-tx = 765
-rx = 146008
-cpu = 24007
-lpm = 185347
-deep = 4472203
-tx = 850
-rx = 160643
-cpu = 26444
-lpm = 202455
-deep = 4888470
-tx = 935
-rx = 175599
-cpu = 28920
-lpm = 220622
-deep = 5326581
-tx = 1020
-rx = 191328
-cpu = 31462
-lpm = 240816
-deep = 5813060
-tx = 1105
-rx = 208793
-cpu = 34221
-lpm = 258941
-deep = 6257808
-tx = 1190
-rx = 224757
-cpu = 36647
-lpm = 277909
-deep = 6715810
-tx = 1275
-rx = 241208
-cpu = 39409
-lpm = 298575
-deep = 7215360
-tx = 1360
-rx = 259156
-cpu = 41747
-lpm = 315626
-deep = 7624903
-tx = 1445
-rx = 273864
-cpu = 44271
-lpm = 334864
-deep = 8087125
-tx = 1530
-rx = 290472
-cpu = 47045
-lpm = 355132
-deep = 8582473
-tx = 1615
-rx = 308250
-cpu = 49405
-lpm = 372225
-deep = 8994245
-tx = 1700
-rx = 323040
-cpu = 51753
-lpm = 388792
-deep = 9395088
-tx = 1785
-rx = 337421
-cpu = 54165
-lpm = 407442
-deep = 9844247
-tx = 1870
-rx = 353541
-cpu = 56476
-lpm = 423932
-deep = 10242911
-tx = 1955
-rx = 367852
-cpu = 58786
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/root_16.py

@@ -1,309 +1,0 @@
-cpu = 13838
-lpm = 109252
-deep = 2631707
-tx = 510
-rx = 94517
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 57953
-Link-layer address: 0012.4b00.1932.e261
-Zolertia RE-Mote revision B platform
-cpu = 2096
-lpm = 19391
-deep = 469370
-tx = 85
-rx = 16845
-cpu = 4753
-lpm = 39968
-deep = 964526
-tx = 170
-rx = 34636
-cpu = 7078
-lpm = 56977
-deep = 1374124
-tx = 255
-rx = 49340
-cpu = 9509
-lpm = 74693
-deep = 1805849
-tx = 340
-rx = 64841
-cpu = 11843
-lpm = 93777
-deep = 2261532
-tx = 425
-rx = 81204
-cpu = 14543
-lpm = 114546
-deep = 2761041
-tx = 510
-rx = 99144
-cpu = 16866
-lpm = 131443
-deep = 3170753
-tx = 595
-rx = 113857
-cpu = 19564
-lpm = 152017
-deep = 3665872
-tx = 680
-rx = 131622
-cpu = 21941
-lpm = 170368
-deep = 4106189
-tx = 765
-rx = 147425
-cpu = 24338
-lpm = 187862
-deep = 4531288
-tx = 850
-rx = 162684
-cpu = 26872
-lpm = 206853
-deep = 4989157
-tx = 935
-rx = 179128
-cpu = 29230
-lpm = 224964
-deep = 5427442
-tx = 1020
-rx = 194869
-cpu = 32018
-lpm = 243571
-deep = 5883147
-tx = 1105
-rx = 211230
-cpu = 34382
-lpm = 261767
-deep = 6319047
-tx = 1190
-rx = 226877
-cpu = 37127
-lpm = 281748
-deep = 6805536
-tx = 1275
-rx = 244343
-cpu = 39708
-lpm = 301377
-deep = 7281071
-tx = 1360
-rx = 261406
-cpu = 41894
-lpm = 317688
-deep = 7668569
-tx = 1445
-rx = 275334
-cpu = 44508
-lpm = 336045
-deep = 8115525
-tx = 1530
-rx = 291365
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/root_4.py

@@ -1,287 +1,165 @@
-Starting Contiki-NG-v1.0-121-g2657a648e-dirty
-- Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 57953
-Link-layer address: 0012.4b00.1932.e261
-Zolertia RE-Mote revision B platform
-Root going to sleep![INFO: Main      - Routing: nullrouting
-- Net: nullnet
-- MAC: TSCH
-- 802.15.4 PANID: 0xabcd
-- 802.15.4 TSCH default hopping sequence length: 1
-Node ID: 57953
-Link-layer address: 0012.4b00.1932.e261
-Zolertia RE-Mote revision B platform
-cpu = 2099
-lpm = 18098
-deep = 440841
-tx = 85
-rx = 15825
-cpu = 4464
-lpm = 35587
-deep = 865977
-tx = 170
-rx = 31090
-cpu = 6647
-lpm = 51974
-deep = 1262576
-tx = 255
-rx = 45333
-cpu = 8896
-lpm = 68193
-deep = 1654691
-tx = 340
-rx = 59425
-cpu = 11556
-lpm = 87721
-deep = 2130249
-tx = 425
-rx = 76507
-cpu = 13732
-lpm = 103836
-deep = 2517953
-tx = 510
-rx = 90425
-cpu = 16574
-lpm = 123235
-deep = 2995753
-tx = 595
-rx = 107585
-cpu = 18749
-lpm = 140627
-deep = 3414294
-tx = 680
-rx = 122634
-cpu = 21426
-lpm = 161319
-deep = 3916195
-tx = 765
-rx = 140660
-cpu = 23578
-lpm = 176984
-deep = 4292905
-tx = 850
-rx = 154182
-cpu = 25716
-lpm = 192563
-deep = 4669714
-tx = 935
-rx = 167712
-cpu = 28067
-lpm = 210674
-deep = 5108006
-tx = 1020
-rx = 183443
-cpu = 30292
-lpm = 228338
-deep = 5530812
-tx = 1105
-rx = 198638
-cpu = 32680
-lpm = 246004
-deep = 5958042
-tx = 1190
-rx = 213992
-cpu = 35337
-lpm = 266435
[…]

### 2021-01-21 examples/task2/plotting/data/data_4/root_8.py

@@ -1,0 +1,167 @@
+using saved target 'zoul'
+rlwrap ../../tools/serial-io/serialdump -b115200 /dev/ttyUSB0
+connecting to /dev/ttyUSB0 [OK]
+[INFO: Main      ] Starting Contiki-NG-v1.0-131-gfed8f5d5b-dirty
+[INFO: Main      ] - Routing: nullrouting
+[INFO: Main      ] - Net: nullnet
+[INFO: Main      ] - MAC: TSCH
+[INFO: Main      ] - 802.15.4 PANID: 0xabcd
+[INFO: Main      ] - 802.15.4 TSCH default hopping sequence length: 4
+[INFO: Main      ] Node ID: 57953
+[INFO: Main      ] Link-layer address: 0012.4b00.1932.e261
+[INFO: Zoul      ] Zolertia RE-Mote revision B platform
+[INFO: MyApp     ] Root started with channel hopping sequence size: 4
+[INFO: MyApp     ] With EB period = 1024 / 128 seconds
+[INFO: MyApp     ] Root going to sleep![INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: HELPERS   ] cpu = 2823
+[INFO: HELPERS   ] lpm = 23537
+[INFO: HELPERS   ] deep = 576889
+[INFO: HELPERS   ] tx = 189
+[INFO: HELPERS   ] rx = 20660
+[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: HELPERS   ] cpu = 2118
+[INFO: HELPERS   ] lpm = 18308
+[INFO: HELPERS   ] deep = 444775
+[INFO: HELPERS   ] tx = 137
+[INFO: HELPERS   ] rx = 16016
+[INFO: MyApp     ] INCOMING PACKET RECEIVED FROM 0012.4b00.1932.e489
+[INFO: HELPERS   ] cpu = 7187
+[INFO: HELPERS   ] lpm = 62602
+[INFO: HELPERS   ] deep = 1537703
+[INFO: HELPERS   ] tx = 397
[…]

### 2021-01-21 examples/task2/plotting/plot.py

@@ -1,6 +1,37 @@
 import os 
 
+
+class Measurement:
+	def __init__(self, cpu, lpm, deep, tx, rx):
+		self.cpu = cpu
+		self.lpm = lpm
+		self.deep = deep
+		self.tx = tx
+		self.rx = rx
+	def __str__(self):
+		return f"CPU: {self.cpu}\nLPM: {self.lpm}\nDeepSleep: {self.deep}\nRX: {self.rx}\nTX: {self.tx}"
+
+class LeafMeasurement(Measurement):
+	def __init__(self, seconds, ticks, cpu, lpm, deep, tx, rx):
+		super().__init__(cpu, lpm, deep, tx, rx)
+		self.seconds = seconds
+		self.ticks = ticks
+	def __str__(self):
+		return f"{super().__str__()}\nseconds: {self.seconds}\nticks: {self.ticks}"
+
+
+
+dataPrefixes = ["ticks =",
+"seconds =",
+"cpu =",
+"lpm =",
+"deep =",
+"tx =",
+"rx ="]
+sqBrPrefix = "[INFO: HELPERS   ] "
 d = 'data/'
+
+data = {}
 for entry in os.scandir(d):
 	if (entry.is_dir()):
 		for e in os.scandir(entry):
@@ -10,11 +41,108 @@ for entry in os.scandir(d):
 					lines = f.readlines()
 				i = 0
 				while i < len(lines):
-					if '[' not in lines[i] or '/dev/ttyUSB' in lines[i] or 'INCOMING PACKET RECEIVED' in lines[i]:
+					if (not any([x in lines[i] for x in dataPrefixes])):
 						del lines[i]
 						continue
-					lines[i] = lines[i].split('] ')[1]
+					lines[i] = lines[i][len(sqBrPrefix):-1] # Cut the prefix and the newline
 					i += 1
-				with open(e.path, 'w') as f:
-					f.writelines(lines)
+				if "_1" in entry.name: # 
+					hopSeqLen = 1
+				elif "_4" in entry.name:
+					hopSeqLen = 4
+				
+				if "_1" in e.name:
+					ebPeriod = 1
+				elif "_4" in e.name:
+					ebPeriod = 4
+				elif "_8" in e.name:
+					ebPeriod = 8
+				if (hopSeqLen, ebPeriod) not in data:
+					data[(hopSeqLen, ebPeriod)] = []
[…]

### 2021-01-21 Paper/Paper.tex
Fixed abstract
Final submission paper

@@
 These boards are part of the IoT hardware family, and they allow for the creation of a network minimizing energy consumption.\\
-We perform different experiments aiming to evaluate various parameters such as energy consumption or latency of the boards in a two nodes network.\\
-Different measurements are performed on the boards under different conditions such as only the MAC layer enabled compared full-stack, during the joining process, and at various distances.
+We perform different experiments aiming to evaluate various parameters such as energy consumption or latency between the boards in a two node network.\\
+We consider three different analyses in this paper.
+First, we compare the energy use when using a full network stack to the energy use when only having the TSCH MAC layer enabled.
+Second, we look at the TSCH association process and analyze the time and energy required for each node.
+Finally, we consider the impact distancing the nodes from each other has on network reliability and energy consumption.
+\cite{TODO: FIX ABSTRACT}
 For each experiment, we report and explain how the introduced variations in the network affect the measured values.
@@
 
+\subsection{Introduction}
+
+A TSCH network advertises through the broadcast of Enhanced Beacons (EB).
+These are frames that contain the TSCH network properties and reception of such a frame allows a node to attempt to join the TSCH network.
+In this section, we analyze how long it takes for a node to join an existing TSCH network.
+We also consider the energy used by the joining node as well as the advertising node.
+
+D.
+De Guglielmo et al have already done similar work\cite{JoinProcess}.
+They show that the channel hopping sequence length is the most important factor with regards to the association time.
+This analysis intends to verify that conclusion (as well as consider the impact of the EB period) and additionally consider the energy used by each node during this association process.
+
 \subsection{Disclaimer}
-
+\label{sec:t2_discl}
 An oversight during the initial experiments for this section caused all the data to be invalid.
@@
 During our initial experiment set, these were the only changes made in between runs of the software.
+This was unfortunately uncovered too close to the submission deadline to fully correct.
 
-Initial dataset considered
+Initial (incorrect) dataset considered EB periods between 1 and 16 seconds as well as channel hopping sequences between 1 and 16 channels.
+In order to limit the amount of time needed to perform the experiments, we limit ourselves to EB periods between 1 and 8 seconds and channel hopping sequences between 1 and 4 channels.
+We further limit the amount of measurements per parameter set to 25 rather than the original 50.
+
+\subsection{Configuration}
+
+The Contiki-NG operating system offers many options for configuring the TSCH joining process.
+We briefly discuss the most significant ones below.
+Any parameters that are changed for our analysis are mentioned in their respective subsections, all others are left as their default value for all performed experiments.
+
+\subsubsection{TSCH\_CONF\_MAX\_JOIN\_PRIORITY}
+This parameter sets the maximal allowed depth for a new node attempting to join the network.
+The TSCH coordinator is at depth 0.
+For any other node, the depth is defined as 1 + the depth of the node it is trying to connect through (i.e.
+the advertising node).
+In our study, we only consider two-node networks, so this parameter is essentially not relevant to our case.
+
+\subsubsection{TSCH\_CONF\_JOIN\_SECURED\_ONLY}
+This parameter sets the TSCH layer such that it only allows joining secured TSCH networks.
+For our experiments, this has been set to disabled.
+We want to minimize all non-TSCH noise on our measurements.
+Security layers require additional processing and thus might obscure some of the results we obtain.
+
+\subsubsection{TSCH\_CONF\_JOIN\_MY\_PANID\_ONLY}
+This parameter sets the TSCH layer such that nodes will only join TSCH networks that are advertising the same PAN ID as they were configured with.
+Any other received EBs (i.e., those with a different PAN ID) are ignored.
+
+\subsubsection{TSCH\_CONF\_ASSOCIATION\_POLL\_FREQUENCY}
+The association poll frequency set by this parameter sets the frequency with which the radio is polled during the association process.
+This has implications for the energy used by the system, as a higher polling rate would result in higher energy use.
+However, a higher polling rate might also be able to associate faster.
+This parameter is left as default in this analysis, but might be interesting to consider in future work.
+
+\subsubsection{TSCH\_CONF\_CHECK\_TIME\_AT\_ASSOCIATION}
+Defining this constant enables the functionality that time should be compared to local uptime at association.
+It will compare the ASN from the EB to the node's own uptime.
+This can be used to allow nodes to be configured such that they will only connect to networks that were created close to their own boot time.
+
+\subsubsection{TSCH\_CONF\_INIT\_SCHEDULE\_FROM\_EB} 
+\label{t2_initsched}
+An EB frame can contain information elements specifying slotframe and link information. This parameter controls whether the node should initialize itself using those information elements.
+
+\subsubsection{TSCH\_CONF\_CHANNEL\_SCAN\_DURATION}
+
+\subsubsection{TSCH\_PACKET\_CONF\_EB\_WITH\_TIMESLOT\_TIMING}
+Controls whether the EB frame contains an information element specifying the network's timeslot timings.
+
+\subsubsection{TSCH\_PACKET\_CONF\_EB\_WITH\_HOPPING\_SEQUENCE} 
+Controls whether the EB frame contains an information element specifying the network's hopping sequence.
+
+\subsubsection{TSCH\_PACKET\_CONF\_EB\_WITH\_SLOTFRAME\_AND\_LINK}
+
+Controls whether the EB frame contains an information element for the slotframe and link information.
+This element would be used by the parameter mentioned in \secref{t2_initsched} if that parameter is set.
+
+\subsubsection{TSCH\_CONF\_EB\_PERIOD}
+How long the time between EB broadcasts should be. Defaults to 16 seconds. This parameter is varied over our experiments, between 1 and 16 seconds.
+
+\subsubsection{TSCH\_CONF\_MAX\_EB\_PERIOD}
+
+The maximal allowed period between EB broadcasts. Defaults to 16 seconds. It imposes an upper limit on the variable mentioned in the previous point.
+
+\subsubsection{TSCH\_CONF\_DEFAULT\_HOPPING\_SEQUENCE}
+The default hopping sequence that is configured for the network. This sequence may have duplicate channels and so can have arbitrary length. It is limited by another variable, see \secref{t2_maxlen}.
+
+\subsubsection{TSCH\_CONF\_JOIN\_HOPPING\_SEQUENCE}
+This constant determines the hopping sequence a node attempting to join a network will use.
+By default, this will be the same as the default hopping sequence for the network.
+It is possible to configure them differently, but our analyses do not use this option.
+
+\subsubsection{TSCH\_CONF\_HOPPING\_SEQUENCE\_MAX\_LEN}
+\label{t2_maxlen}
+This sets the maximal allowed length for a hopping sequence in the TSCH network.
+By default it is set to the length of the default hopping sequence.
+This value is 4 in the standard configuration, but is automatically changed along with the configuration of a different default hopping sequence.
+
+\subsection{Experiment setup}
+
+In this section, we consider two nodes placed 20 cm apart, with nothing between them impeding communication, as in \figref{fig:exp1Topology}.
+The leaf node will repeatedly associate and disassociate from the TSCH network.
+The root node will simply wait and output its energy statistics whenever the node associates.
+The leaf, similarly, will output its time taken and the energy used when association is complete.
+After the data has been output, the leaf node disassociates from the network and starts over.
+
+We consider the case only where the node disassociates from the network, then immediately reassociates itself.
+Introducing additional variance by waiting the leaf node for an arbitrary amount of time simply introduces additional noise into the measurements.
+It is an option that was considered, but discarded.
+While the effect this has on the measurements simulates a more realistic scenario (node starts listening at a random time), it simply introduces noise into our measurements that were not influenced by the variables we're attempting to isolate.
+In order to correctly gauge the effect each of the variables we consider has, this additional source of noise was not added.
+
+\subsection{Results}
+
+We see clearly that, regardless of configuration, the leaf node always spends a large amount of time in the RX state.
+This makes sense as it has to be listening for an EB constantly in order to connect to a network.
+We also see that, while this happening, it is very rare for the CPU to enter a deep sleep state.
+Presumably, because of the constant channel switching, the CPU has to perform some computation regularly enough to prevent long deep sleeps.
+This contrasts heavily with the behaviour observed when the node is connected, where the deep sleep state dominates.
+This is clear from all data obtained in \secref{section:task3}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/times}
+	\caption{The average connection times per configuration. X axis is the configuration (hopping sequence length, EB period), Y axis in seconds}
+	\label{fig:t2leaf}
+\end{figure}
+
+Per \figref{fig:t2leaf}, it is clear that most of the time is spent by the leaf in the Low power mode CPU state, while listening to the channel.
+This is true regardless of configuration, but some configurations show higher peaks because of the longer experiment durations.
+It is trivially true that a longer on-time for the node leads to higher energy use and thus a distinctly higher peak in this graph.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/leaf_powerstates}
+	\caption{The average connection times per configuration. X axis is the configuration (hopping sequence length, EB period), Y axis in seconds}
+	\label{fig:t2root}
+\end{figure}
+
+\figref{fig:t2root} shows the root power states, for each configuration.
+Again, we see roughly identical power state distribution for each configuration.
+It is notably different from the leaf power states graph in that the root node spends most of its time in the sleep state.
+This is to be expected as it already has all the required information to operate efficiently.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.48\textwidth,keepaspectratio]{figures/root_powerstates}
+	\caption{Seconds needed to successfully connect, on average, per configuration}
+	\label{fig:t2times}
+\end{figure}
+\figref{fig:t2times} shows the required connection times for each configuration.
+It clearly indicates that the length of the hopping sequence is a dominating factor in the estimation of TSCH association times.
+
+\subsection{Conclusion}
+We have shown that the hopping sequence does indeed impact the association time more than the EB period does, supporting previous research \cite{JoinProcess}.
+
+\subsection{Future Work}
+\subsubsection{Full measurements} 
+As discussed in \secref{sec:t2_discl}, we have severely limited the scope of this analysis because of an oversight on our part.
+This oversight must be corrected in future work in order to confirm the tentative results we've presented here.
+\subsubsection{Additional parameters}
+Considering other variables, for example, TSCH\_CONF\_ASSOCIATION\_POLL\_FREQUENCY would be interesting.
+There are many variables that have an impact on the TSCH association process and our analyses do not offer thorough coverage.
 

### 2021-01-21 Paper/Paper.tex
Final polish

@@
 Finally, we consider the impact distancing the nodes from each other has on network reliability and energy consumption.
-\cite{TODO: FIX ABSTRACT}
-For each experiment, we report and explain how the introduced variations in the network affect the measured values.
+Comparing the energy usage we found that in a MAC only configuration the leaf and root node have the same energy consumption, such value diminishes for both of them if the full stack is enabled. 
+The join process is mostly impacted by the length of the hopping sequence, though the EB period also has significant impact.
+Distance between the nodes starts impacting performance noticeably (from our tested distances) at 50m, leading to completely unacceptable performance at low TX powers when reaching 100m.
 \end{abstract}
